### 2016-05-02 ms.tex
I added everything relevant for the paper to git version control.

%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%\documentclass{article}
%\documentclass[manuscript]{aastex}
\documentclass{emulateapj}

%% preprint2 produces a double-column, single-spaced document:
%\documentclass[preprint2]{aastex}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

%Packages
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}

\usepackage{natbib}
\bibliographystyle{astroads}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\DHSres}{3000 ?}

%% You can insert a short comment on the title page using the command below.

%\slugcomment{DHS White Paper}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

\shorttitle{JWST NIRCam SW and LW}
\shortauthors{Schlawin et al.}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short Wavelength Dispersed Hartmann Sensor}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{E. Schlawin \and M. Rieke? \and J. Leisenring \and J. Fraine? \and D. Kelly \and L. M. Walker? \and K. Misselt}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

\author{T. Greene}
\affil{NASA Ames Research Center, Moffett Field, CA 94035}

\author{M. Line?\altaffilmark{1,2,3,4}}
\affil{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 95064}

\author{N. Lewis? \and J. Stansberry}
\affil{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

\altaffiltext{1}{Hubble Postdoctoral Fellow}
\altaffiltext{2}{NASA Ames Research Center, Moffett Field, CA 94035}
\altaffiltext{3}{Bay Area Environmental Research Institute, Petaluma, CA}
\altaffiltext{4}{School of Earth and Space Exploration, Arizona State University, Tempe, AZ}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
James Webb Space Telescope (JWST) offers unprecedented sensitivity, stability and wavelength coverage for transiting exoplanet studies, opening up new avenues for measuring atmospheric abundances, structure and temperature profiles. Taking full advantage of JWST spectroscopy of planets from 0.6 $\mu$m to 28$\mu$m, however, will require many observations with a combination of the NIRISS, NIRCam, NIRSpec and MIRI instruments. In this white paper, we discuss a new NIRCam mode (not yet approved and implemented) that can reduce the number of observations needed for observations in the 1.0$\mu$m to 5.0$\mu$m wavelength range. The NIRCam instrument was primarily designed as an imager, but includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments. NIRCam's long wavelength arm includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R \sim 1770$ and it has already been approved for wide field slitless spectroscopy. We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short wavelength arm. This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spectra for every source at $R \sim \DHSres$. The DHS can observe the brightest host stars of any JWST mode. We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres. The DHS essentially comes for free with any NIRCam long wavelength grism observation, but the readout has to be selected to ensure that the long wavelength grisms observations do not saturate and that the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{telescopes, planets and satellites: atmospheres, instrumentation: spectrographs}

%% From the front matter, we move on to the body of the paper.
%% In the first two sections, notice the use of the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below. We have
%% chosen the first three characters of the first author's name plus
%% the last two numeral of the year of publication as our KEY for
%% each reference.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so by tagging
%% their objects with \objectname{} or \object{}.  Each macro takes the
%% object name as its required argument. The optional, square-bracket 
%% argument should be used in cases where the data center identification
%% differs from what is to be printed in the paper.  The text appearing 
%% in curly braces is what will appear in print in the published paper. 
%% If the object name is recognized by the data centers, it will be linked
%% in the electronic edition to the object data available at the data centers  
%%
%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
%% the brackets must be escaped with backslashes when used in the first
%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
%%  Otherwise, LaTeX will issue an error.

\section{Introduction}

The James Webb Space Telescope (JWST) \citep[e.g.][]{gardner2006SSRv} has the potential to profoundly expand and deepen the science of transiting exoplanets \citep[e.g.][]{greene2016jwst_trans}. The wavelength coverage from 0.6$\mu$m to 28$\mu$m ads significantly to the wavelengths covered by the Hubble Space Telescope (currently 0.09$\mu$m to 1.7$\mu$m). Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent observatory for characterizing the atmospheres of planets that transit their host stars with time series observations. Ground-based observatories and the Hubble Space Telescope (HST) have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}. JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to it host star. Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes at longer wavelengths.

No single JWST instrument may measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum over these wavelengths. The largest bandwidths possible are NIRSpec's low resolution prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m. Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments. For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7 $\mu$m to 12 $\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7 to 2.5$\mu$m), two with NIRCam's Long Wavelength Arm (2.44$\mu$m to 4.98 $\mu$m) \footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m). With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours. This was calculated with the Astronomer's Proposal Tools software\footnote{http://www.stsci.edu/hst/proposing/apt} with the NIRISS SOSS mode, NIRCam's F322W2 and F444W grism time series and the MIRI Low Resolution spectrograph (LRS).

The NIRCam instrument was originally designed as an imager, but it includes several spectroscopic modes originally designed for wavefront sensing. These include the grisms installed in its long wavelength arm as well as the Dispersed Hartmann Sensors (DHSs) installed in its short wavelength arm. The long wavelength grisms are used in concert with broadband filters. The F322W2 filter encompasses 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter encompasses 3.88$\mu$ to 4.98$\mu$m at half maximum throughput. These filters and grism are enabled and supported JWST science modes. The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput. The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the first order of the spectrum begins to overlap at at 2.0$\mu$m.

The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5 $\mu$m. This is because the instrument has a dichroic that splits the incoming beam into a short wavelength arm and long wavelength arm, so simultaneous imaging and spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths. In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter. Thus, the DHS data comes ``for free'' with any long wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}. For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0 to 2.4$\mu$m and higher Signal to Noise ratios from NIRISS are not required. The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long wavelength NIRCam grism transit.

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
\caption{Model spectra divided up by molecule for HD209458b. The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either of NIRCam's F322W2 or F444W slitless grism observations in its long wavelength arm. The error bars are for two DHS grism spectra taken simultaneously with each of the long wavelength grism observations. The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:DHSmolecules}
\end{figure}

Since the DHS was not originally designed for science observations, it is not yet an approved mode for the James Webb Space Telescope. In this white paper, we argue for the inclusion of the DHS mode to fully take advantage of two NIRCam arms to maximize JWST's science potential for transiting planets. In section \ref{sec:implementation}, we discuss how the DHS would work in for time series observations and the implications of reading out several detectors simultaneously at a high frame rate. In section \ref{sec:addedScience} we discuss the added science that can be achieved with the DHS, including the brightness limits and improved precision in retrieved parameters for a representative system.

\section{DHS Implementation}\label{sec:implementation}

A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short wavelength arm and one spectrum on the long wavelength arm -- see Figure \ref{fig:DHSimage}. The 10 separate DHS spectra are spread across two of NIRCam's short wavelength detectors. Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source. Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on whether they lie in comparison to the secondary mirror strut supports seen in Figure \ref{fig:DHSvsPupilOverlay}. Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum. For sub-array sizes encompassing 1 DHS spectra, the large unobscured DHS grisms should be used like numbers 2, 4, 7 or 9.

%The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs. The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m. If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
\caption{Example images of the same source observed with the DHS on the short wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long wavelength arm (right). These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard. Only 3 detectors will be needed for transit observations.}\label{fig:DHSimage}
\end{figure}

\begin{table}
\centering
\begin{tabular}{cc}
DHS  Resolution &  R $\sim$ \DHSres \\
Dispersion & 0.29 nm / px \\
Wavelength Range & 1$\mu$m to 2$\mu$m, 0.05$\mu$m gap \\
Plate Scale & 32 mas/px \\
\hline \hline
Grism Resolution & R $\sim$ 1770 \\
Dispersion & 1.0 nm / px  \\
Wavelength Range F322W2 & 2.44$\mu$m to 4.02$\mu$m \\
Wavelength Range F444W & 3.88$\mu$m to 4.98 $\mu$m \\
Plate Scale & 65 mas/px \\
\end{tabular}
\caption{Properties of DHS and simultaneous long wavelength grism spectra.}\label{tab:DHSgprop}
\end{table}

\begin{table}
\centering
\begin{tabular}{cc}
DHS \# & Pupil Fraction \\
\hline \hline
1 & 0.033 \\
2 & 0.047 \\
3 & 0.036 \\
4 & 0.043 \\
5 & 0.030 \\
6 & 0.032 \\
7 & 0.042 \\
8 & 0.045 \\
9 & 0.040 \\
10 & 0.033 \\
\end{tabular}
\caption{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area. \textbf{Needs updating after correcting for the OSIM circles.}}\label{tab:pupfrac}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{dhs_pupil_overlay.png}
\caption{DHS pupil coverage by each of the 10 DHS grisms, with the fractional throughput given in Table \ref{tab:pupfrac}. The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (black lines). The circles in the image are products of the OSIM (optical telescope element simulator) test source used in Cryogenic Vacuum testing of the instrument suite, and will not be present in flight.}\label{fig:DHSvsPupilOverlay}

\end{figure}
\subsection{Readout Considerations}\label{sec:readout}
JWST's NIRCam has many different possible readout patterns per pixel and array that all factor in to the Signal to Noise Ratios (SNRs) and saturation limits for for an observation. We adopt the following naming convention for the readout: An observation may consist of one of more exposures which are typically combined into a single \texttt{FITS} file per exposure. Within an exposure, there 1 or more integrations, which consist of a reset frame followed by 1 or more groups of non-destructive reads up a ramp. This is illustrated in Fig \ref{fig:readout} for three example readout modes.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{readout_schematic.pdf}
\caption{Schematic of example readout modes for an exposure that is 12 frame times in duration. A single FITS file is saved for the exposure, consisting of 1-2 groups (read 1 or both read 1 and read 2) per integration. No reset frames or dropped frames are saved.``1 Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable. The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but will saturate more easily. }\label{fig:readout}
\end{figure}

Each NIRCam array must be read out with identical window sizes and exposure times (due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}). This means that some balance must be made between saturating grism spectra (which has much higher throughput) in the long wavelength and getting the most flux in the short wave DHS spectrum (which has lower throughput and also spreads the light over more pixels).

The balance between saturating the long wavelength grism and getting enough signal to noise in the DHS is listed in Table \ref{tab:SatSNRsubA}. The table shows the brightest observable G2V star  for a given array size in the long wavelength grism and the signal to noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration. We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} is used and we consider 80\% well depth in the second read as saturation.

\begin{table}
\centering
\begin{tabular}{llll}
Sub-Array Size &  LW Saturation & \# of DHS & DHS Noise\\
                         &  K Magnitude    &                               & ppm \\
\hline \hline
1600$\times$ 64 & 4.03 & 1 &  ?? \\
1600$\times$ 200 & 5.25 & 2 &  ?? \\
1600$\times$ 500 & 6.23 & 4 &  ?? \\
1600$\times$ 1240 & 7.22 & 10 & ??
\end{tabular}
\caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes. The size affects the number of DHS that can be included, so the Signal To Noise at 1.5$\mu$m in the DHS spectrum at the given saturation limit for a 1 hour transit is shown in column 4.}\label{tab:SatSNRsubA}
\end{table}

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{example_ap_sizes.png}
\caption{Example sub-array size options for one of the short wavelength detectors for the DHS.}\label{fig:DHSaps}
\end{figure}

\subsubsection{Data Volume}
For most transiting planet science, the targets are bright and so the pixels will continuously be read out and saved without any pauses or skips in the stream of data at $\sim$1.6 Mbits per second per amplifier per detector. The amount of data streaming from the detectors can overload the Solid State Recorder (SSR), which has a capacity of 540 Gbits \citep{johns2008L2comm} (\textbf{compressed data?}). This overload can happen in as few as 10 hours if three NIRCam detectors are used simultaneously and all are read out with four amplifiers in RAPID mode (meaning no samples are co-added or dropped).

In normal operations, up to 232 Gbits of compressed science and telemetry data from James Webb Space Telescope are downlinked once per day over the 4 hour contact time with an antenna in the Deep Space Network (SDN)  \citep{dashevsky2008groundflight}. Science operations can continue during the 4 hour contact time, but re-pointing the high gain antenna can cause $<$0.07 \arcsec\ disturbances \citep{beichman2014pasp}. To satisfy these normal operations, the data volume must be reduced for observations longer than \textbf{How many do you think? 6 hours to allow for telemetry and other science?} when using 3 detectors and 4 amplifiers simultaneously.

There are a few ways to reduce the data volume streaming from the detectors. One way is to read each detector with a single amplifier (WINDOW mode). This reduces the frame rate by a factor of four (for the four amplifiers), thus allowing $\sim$40 hours before filling JWST's solid state recorders. The lower frame rate, however, means that the detector saturates at 1/4 the flux as four amplifiers. Second, the detector can be read out in BRIGHT1 mode, seen in Figure \ref{fig:readout}. This is where each a frame is dropped between read 2 and read 1 to increase the integration time while reducing data volume. This only works for sources faint enough that the long wavelength grisms do not saturate. Reducing the size of the sub-array does not affect the data volume because it just increases the number of frames so that approximately the same amount of data in pixels is saved to JWST's solid state recorder.

\section{Science Benefits with the DHS}\label{sec:addedScience}

\subsection{Brightness limits}\label{sec:brightness}

The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST. Figure \ref{fig:DHSaps} shows the saturation limits for the DHS mode along with NIRCam's long wavelength grisms. Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4. The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS).

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
\caption{Saturation limits of the DHS mode (blue), and long wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star. The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.}\label{fig:DHSaps}
\end{figure}

\subsection{CHIMERA Simulations}\label{sec:simulations}

We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to show the scientific value of using the DHS simultaneously with NIRCam's long wavelength grisms. We first simulate a forward model of a transmission spectrum for a planet (in this case HD 209458b). We then add Gaussian noise using the signal to noise estimated on the target to create a simulated spectrum. Finally, we run an Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}. We combine the individual gases' posterior distributions for the C/O ratio and metallicity.

For the initial model, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the settling out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}. The atomic abundances are converted to molecular mixing ratios using the Chemical Equilibrium code with Applications (CEA) \footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} to calculate the fractions of molecules at the given pressure and temperature. For HD209458b, this is at a reference pressure of 0.01 bars and a reference temperature of 1440K. We assume that the abundances and temperature are constant with altitude. We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$,H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as sources of opacity, but only H$_2$O, CO, and CO$_2$ contribute significantly to the opacity, as seen in Figure \ref{fig:DHSmolecules}.
% if we run the simulations later, also mention emission spectra

For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m. We assume that each of these was accompanied by a DHS spectrum for the 1.01$\mu$ to 2.0$\mu$m wavelength range, which benefits in signal to noise by $\sqrt(2)$ for the two separate observations. This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra. The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the detector noise floor (35 ppm) for the long wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short wavelength DHS observations. The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher signal to noise and full wavelength coverage from 0.7 to 2.4$\mu$m can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours. Similar wavelength coverage can be achieved in just 3 different transits or $\sim$ 33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
\end{figure}

We use CHIMERA and a Markov Chain Monte Carlo (MCMC) retrieval to recover the individual atmospheric abundances of the simulated spectrum. The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile 2) the altitude of the 10-bar pressure surface where the model begins 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths 4-11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively 12) an amplitude of a Raleigh-like haze and 13) a power law index for the Raleigh-type haze. We assume flat priors in log space for all abundances from volume mixing ratios of 10$^{-12}$ to 1. The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 to allow for burn-in.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_DHS.pdf}
\caption{Posterior distributions of the retrieved abundances, showing improvements of the constraints on temperature, cloud pressure upper limit and H$_2$O, CO$_2$ and CO abundances with the DHS. Vertical dashed bars show the input abundances for the initial forward model that was used to generate the simulated spectru.}\label{fig:DHSadded}
\end{figure}

%The DHS improves constraints on HD209458b's temperature (assumed isothermal in this model), abundances and cloud pressure layer, as visible in Figure \ref{fig:cornerRun}. The improvements in abundances are

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_nc_only_subset.png}
\caption{Posterior distributions an MCMC run of HD209458b without the DHS. The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.}\label{fig:cornerRun}
\end{figure*}

One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances. A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor. However, the retrieval for the spectrum with only NIRCam's long wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}. Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.

\section{Conclusions}

The James Webb Space Telescope will provide unprecedented measurements of transiting exoplanets, especially for carbon-bearing gases in their atmospheres. The time needed to observe in JWST's full range of wavelengths from 0.6$\mu$m to 28$\mu$m, however, can add up quickly since many transits are needed with different instrument modes to cover all wavelengths. We introduced a new science mode using the Dispersed Hartmann Sensor's on the NIRCam instrument which enable simultaneous measurements of spectra at R $\sim$ \DHSres\ from 1.0 to 2.0$\mu$m while using the NIRCam long wavelength grisms covering either 2.4$\mu$m to 4.0$\mu$m or 3.9$\mu$m to 5.0$\mu$m. The readout mode and subarray size much be chosen carefully on the DHS so as to not saturate the long wavelength grisms.

The DHS mode enables more science because it has the brightest saturation limits of any JWST spectroscopic mode and can increase the wavelength coverage of a single observation. The brightest known systems and similarly bright future TESS targets will be accessible with NIRCam's DHS mode. We present example usage of the DHS mode on HD 209458b and show that the temperature, cloud pressure level and water vapor constraints are improved with the DHS. Furthermore, the improved water vapor constraints also improve CO and CO$_2$ abundances because of the correlation of these derived parameters. We encourage the implementation and approval of the DHS mode to enable this additional science.

\section{Acknowledgements}

CHIMERA retrieval makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}. For use of the El Gato computing system, this material is based upon work supported by the National Science Foundation under Grant No. 1228509. Thanks to Michael Bruck at the High Performance Computing center at the University of Arizona for assisting with setting up the CHIMERA runs to utilize the HPC hardware.
%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

%% In a manner similar to \objectname authors can provide links to dataset
%% hosted at participating data centers via the \dataset{} command.  The
%% second curly bracket argument is printed in the text while the first
%% parentheses argument serves as the valid data set identifier.  Large
%% lists of data set are best provided in a table (see Table 3 for an example).
%% Valid data set identifiers should be obtained from the data center that
%% is currently hosting the data.
%%
%% Note that AASTeX interprets everything between the curly braces in the 
%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
%% compile your manuscript.  Special characters do not 
%% need to be escaped in the optional, square-bracket argument.

%% In this section, we use  the \subsection command to set off
%% a subsection.  \footnote is used to insert a footnote to the text.

%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% This section also includes several of the displayed math environments
%% mentioned in the Author Guide.

%% The equation environment wil produce a numbered display equation.

%% The \notetoeditor{TEXT} command allows the author to communicate
%% information to the copy editor.  This information will appear as a
%% footnote on the printed copy for the manuscript style file.  Nothing will
%% appear on the printed copy if the preprint or
%% preprint2 style files are used.

%% The eqnarray environment produces multi-line display math. The end of
%% each line is marked with a \\. Lines will be numbered unless the \\
%% is preceded by a \nonumber command.
%% Alignment points are marked by ampersands (&). There should be two
%% ampersands (&) per line.

%% Putting eqnarrays or equations inside the mathletters environment groups
%% the enclosed equations by letter. For instance, the eqnarray below, instead
%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%% LaTeX the paper and look at the output to see the results.

%% This section contains more display math examples, including unnumbered
%% equations (displaymath environment). The last paragraph includes some
%% examples of in-line math featuring a couple of the AASTeX symbol macros.

%% The displaymath environment will produce the same sort of equation as
%% the equation environment, except that the equation will not be numbered
%% by LaTeX.
%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.

%% Included in this acknowledgments section are examples of the
%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
%% argument when you want to print the url directly in the text. Otherwise,
%% use either \url or \anchor, with the HREF as the first argument and the
%% text to be printed in the second.

\acknowledgments

%% To help institutions obtain information on the effectiveness of their
%% telescopes, the AAS Journals has created a group of keywords for telescope
%% facilities. A common set of keywords will make these types of searches
%% significantly easier and more accurate. In addition, they will also be
%% useful in linking papers together which utilize the same telescopes
%% within the framework of the National Virtual Observatory.
%% See the AASTeX Web site at http://aastex.aas.org/
%% for information on obtaining the facility keywords.

%% After the acknowledgments section, use the following syntax and the
%% \facility{} macro to list the keywords of facilities used in the research
%% for the paper.  Each keyword will be checked against the master list during
%% copy editing.  Individual instruments or configurations can be provided 
%% in parentheses, after the keyword, but they will not be verified.

%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc.

\appendix

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\bibliographystyle{apj}
\bibliography{/Users/everettschlawin/evmemo_folder/pdfs/master_bib_file/master_biblio.bib}
%\bibliography{master_biblio.bib}

%\clearpage

%% Use the figure environment and \plotone or \plottwo to include
%% figures and captions in your electronic submission.
%% To embed the sample graphics in
%% the file, uncomment the \plotone, \plottwo, and
%% \includegraphics commands
%%
%% If you need a layout that cannot be achieved with \plotone or
%% \plottwo, you can invoke the graphicx package directly with the
%% \includegraphics command or use \plotfiddle. For more information,
%% please see the tutorial on "Using Electronic Art with AASTeX" in the
%% documentation section at the AASTeX Web site, http://aastex.aas.org/
%%
%% The examples below also include sample markup for submission of
%% supplemental electronic materials. As always, be sure to check
%% the instructions to authors for the journal you are submitting to
%% for specific submissions guidelines as they vary from
%% journal to journal.

%% This example uses \plotone to include an EPS file scaled to
%% 80% of its natural size with \epsscale. Its caption
%% has been written to indicate that additional figure parts will be
%% available in the electronic journal.

%\begin{figure}
%\epsscale{.80}
%\plotone{f1.eps}
%\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
%in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
%\end{figure}

%\clearpage

%% Here we use \plottwo to present two versions of the same figure,
%% one in black and white for print the other in RGB color
%% for online presentation. Note that the caption indicates
%% that a color version of the figure will be available online.
%%

%\begin{figure}
%\plottwo{f2.eps}{f2_color.eps}
%\caption{A panel taken from Figure 2 of \citet{rudnick03}. 
%See the electronic edition of the Journal for a color version 
%of this figure.\label{fig2}}
%\end{figure}

%% This figure uses \includegraphics to scale and rotate the still frame
%% for an mpeg animation.

%\begin{figure}
%\includegraphics[angle=90,scale=.50]{f3.eps}
%\caption{Animation still frame taken from \citet{kim03}.
%This figure is also available as an mpeg
%animation in the electronic edition of the
%{\it Astrophysical Journal}.}
%\end{figure}

%% If you are not including electonic art with your submission, you may
%% mark up your captions using the \figcaption command. See the
%% User Guide for details.
%%
%% No more than seven \figcaption commands are allowed per page,
%% so if you have more than seven captions, insert a \clearpage
%% after every seventh one.

%% Tables should be submitted one per page, so put a \clearpage before
%% each one.

%% Two options are available to the author for producing tables:  the
%% deluxetable environment provided by the AASTeX package or the LaTeX
%% table environment.  Use of deluxetable is preferred.
%%

%% Three table samples follow, two marked up in the deluxetable environment,
%% one marked up as a LaTeX table.

%% In this first example, note that the \tabletypesize{}
%% command has been used to reduce the font size of the table.
%% We also use the \rotate command to rotate the table to
%% landscape orientation since it is very wide even at the
%% reduced font size.
%%
%% Note also that the \label command needs to be placed
%% inside the \tablecaption.

%% This table also includes a table comment indicating that the full
%% version will be available in machine-readable format in the electronic
%% edition.

%% If you use the table environment, please indicate horizontal rules using
%% \tableline, not \hline.
%% Do not put multiple tabular environments within a single table.
%% The optional \label should appear inside the \caption command.

%% If the table is more than one page long, the width of the table can vary
%% from page to page when the default \tablewidth is used, as below.  The
%% individual table widths for each page will be written to the log file; a
%% maximum tablewidth for the table can be computed from these values.
%% The \tablewidth argument can then be reset and the file reprocessed, so
%% that the table is of uniform width throughout. Try getting the widths
%% from the log file and changing the \tablewidth parameter to see how
%% adjusting this value affects table formatting.

%% The \dataset{} macro has also been applied to a few of the objects to
%% show how many observations can be tagged in a table.

%% Tables may also be prepared as separate files. See the accompanying
%% sample file table.tex for an example of an external table file.
%% To include an external file in your main document, use the \input
%% command. Uncomment the line below to include table.tex in this
%% sample file. (Note that you will need to comment out the \documentclass,
%% \begin{document}, and \end{document} commands from table.tex if you want
%% to include it in this document.)

%% \input{table}

%% The following command ends your manuscript. LaTeX will ignore any text
%% that appears after it.

\end{document}

%%
%% End of file `sample.tex'.

### 2016-05-03 ms.tex
I did some word changes such as long to short wavelength and other clarifications on the first few pages suggested by Lisa May.

@@
 
-\title{Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short Wavelength Dispersed Hartmann Sensor}
+\title{Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor}
 
@@
 
-\author{E. Schlawin \and M. Rieke? \and J. Leisenring \and J. Fraine? \and D. Kelly \and L. M. Walker? \and K. Misselt}
+\author{E. Schlawin \and M. Rieke? \and J. Leisenring \and  L. M. Walker  \and J. Fraine? \and D. Kelly \and K. Misselt}
 \affil{Steward Observatory, Tucson AZ 85721}
@@
 The NIRCam instrument was primarily designed as an imager, but includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments.
-NIRCam's long wavelength arm includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R \sim 1770$ and it has already been approved for wide field slitless spectroscopy.
-We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short wavelength arm.
+NIRCam's long-wavelength arm includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R \sim 1770$ and it has already been approved for wide field slitless spectroscopy.
+We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength arm.
 This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spectra for every source at $R \sim \DHSres$.
@@
 We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres.
-The DHS essentially comes for free with any NIRCam long wavelength grism observation, but the readout has to be selected to ensure that the long wavelength grisms observations do not saturate and that the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
+The DHS essentially comes for free with any NIRCam long-wavelength grism observation, but the readout has to be selected to ensure that the long-wavelength grism observations do not saturate and that the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
+Combining both of NIRCam's arms will maximize the science potential of JWST, which is a limited life observatory.
 \end{abstract}
@@
 The James Webb Space Telescope (JWST) \citep[e.g.][]{gardner2006SSRv} has the potential to profoundly expand and deepen the science of transiting exoplanets \citep[e.g.][]{greene2016jwst_trans}.
-The wavelength coverage from 0.6$\mu$m to 28$\mu$m ads significantly to the wavelengths covered by the Hubble Space Telescope (currently 0.09$\mu$m to 1.7$\mu$m).
+The wavelength coverage from 0.6$\mu$m to 28$\mu$m adds significantly to the wavelengths covered by the Hubble Space Telescope (HST) (currently 0.09$\mu$m to 1.7$\mu$m).
 Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent observatory for characterizing the atmospheres of planets that transit their host stars with time series observations.
-Ground-based observatories and the Hubble Space Telescope (HST) have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
+Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
 JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to it host star.
-Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes at longer wavelengths.
+Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes.
 
-No single JWST instrument may measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum over these wavelengths.
+No single JWST instrument may measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum.
 The largest bandwidths possible are NIRSpec's low resolution prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m.
 Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
-For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7 $\mu$m to 12 $\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7 to 2.5$\mu$m), two with NIRCam's Long Wavelength Arm (2.44$\mu$m to 4.98 $\mu$m) \footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
+For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7 $\mu$m to 12 $\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7 to 2.5$\mu$m), two with NIRCam's long-wavelength arm (2.44$\mu$m to 4.98 $\mu$m) \footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
 With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours.
@@
 
-The NIRCam instrument was originally designed as an imager, but it includes several spectroscopic modes originally designed for wavefront sensing.
-These include the grisms installed in its long wavelength arm as well as the Dispersed Hartmann Sensors (DHSs) installed in its short wavelength arm.
-The long wavelength grisms are used in concert with broadband filters.
+The NIRCam instrument is primarily an imager, but it includes several spectroscopic modes originally designed for wavefront sensing.
+These include the grisms installed in its long-wavelength arm as well as the Dispersed Hartmann Sensors (DHSs) installed in its short-wavelength arm.
+The long-wavelength grisms are used in concert with broadband filters.
 The F322W2 filter encompasses 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter encompasses 3.88$\mu$ to 4.98$\mu$m at half maximum throughput.
@@
 The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5 $\mu$m.
-This is because the instrument has a dichroic that splits the incoming beam into a short wavelength arm and long wavelength arm, so simultaneous imaging and spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
-In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
-Thus, the DHS data comes ``for free'' with any long wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
-For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0 to 2.4$\mu$m and higher Signal to Noise ratios from NIRISS are not required.
-The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long wavelength NIRCam grism transit.
+This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength arm and long-wavelength arm, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
+In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
+Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
+For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0 to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
+The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.
 
@@
 \caption{Model spectra divided up by molecule for HD209458b.
-The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either of NIRCam's F322W2 or F444W slitless grism observations in its long wavelength arm.
-The error bars are for two DHS grism spectra taken simultaneously with each of the long wavelength grism observations.
+The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength arm.
+The simulated data are for one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
 The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:DHSmolecules}
@@
 In this white paper, we argue for the inclusion of the DHS mode to fully take advantage of two NIRCam arms to maximize JWST's science potential for transiting planets.
-In section \ref{sec:implementation}, we discuss how the DHS would work in for time series observations and the implications of reading out several detectors simultaneously at a high frame rate.
+In section \ref{sec:implementation}, we discuss how the DHS would work for time-series observations and the implications of reading out several detectors simultaneously at a high frame rate.
 In section \ref{sec:addedScience} we discuss the added science that can be achieved with the DHS, including the brightness limits and improved precision in retrieved parameters for a representative system.
@@
 
-A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short wavelength arm and one spectrum on the long wavelength arm -- see Figure \ref{fig:DHSimage}.
-The 10 separate DHS spectra are spread across two of NIRCam's short wavelength detectors.
+A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength arm and one spectrum on the long-wavelength arm -- see Figure \ref{fig:DHSimage}.
+The DHS mode is only well suited for one source at a time because of the large number of spectra that would overlap in a crowded field.
+The 10 separate DHS spectra are spread across two of NIRCam's short-wavelength detectors.
 Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
-Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on whether they lie in comparison to the secondary mirror strut supports seen in Figure \ref{fig:DHSvsPupilOverlay}.
+Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports seen in Figure \ref{fig:DHSvsPupilOverlay}.
 Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum.
-For sub-array sizes encompassing 1 DHS spectra, the large unobscured DHS grisms should be used like numbers 2, 4, 7 or 9.
+For sub-array sizes encompassing 1 DHS spectra, the large unobscured DHS grisms should be used like numbers 3, 7 or 9.
 
@@
 \includegraphics[width=0.5\textwidth]{dhs_image_example.png}
-\caption{Example images of the same source observed with the DHS on the short wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long wavelength arm (right).
+\caption{Example images of the same source observed with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right).
 These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard.
@@
 \centering
-\begin{tabular}{cc}
-DHS  Resolution &  R $\sim$ \DHSres \\
+\begin{tabular}{ccc}
+ &  R $\sim$ \DHSres \\
+ \hline \hline
 Dispersion & 0.29 nm / px \\
@@
 \end{tabular}
-\caption{Properties of DHS and simultaneous long wavelength grism spectra.}\label{tab:DHSgprop}
+\caption{Properties of DHS and simultaneous long-wavelength grism spectra.}\label{tab:DHSgprop}
 \end{table}
@@
 Each NIRCam array must be read out with identical window sizes and exposure times (due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}).
-This means that some balance must be made between saturating grism spectra (which has much higher throughput) in the long wavelength and getting the most flux in the short wave DHS spectrum (which has lower throughput and also spreads the light over more pixels).
+This means that some balance must be made between saturating grism spectra (which has much higher throughput) in the long-wavelength and getting the most flux in the short wave DHS spectrum (which has lower throughput and also spreads the light over more pixels).
 
-The balance between saturating the long wavelength grism and getting enough signal to noise in the DHS is listed in Table \ref{tab:SatSNRsubA}.
-The table shows the brightest observable G2V star  for a given array size in the long wavelength grism and the signal to noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration.
+The balance between saturating the long-wavelength grism and getting enough signal to noise in the DHS is listed in Table \ref{tab:SatSNRsubA}.
+The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the signal to noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration.
 We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} is used and we consider 80\% well depth in the second read as saturation.
@@
 \includegraphics[width=0.5\textwidth]{example_ap_sizes.png}
-\caption{Example sub-array size options for one of the short wavelength detectors for the DHS.}\label{fig:DHSaps}
+\caption{Example sub-array size options for one of the short-wavelength detectors for the DHS.
+Each element is labeled corresponding to the DHS apertures shown in Figure \ref{fig:DHSvsPupilOverlay}}\label{fig:DHSaps}
 \end{figure}
@@
 This is where each a frame is dropped between read 2 and read 1 to increase the integration time while reducing data volume.
-This only works for sources faint enough that the long wavelength grisms do not saturate.
+This only works for sources faint enough that the long-wavelength grisms do not saturate.
 Reducing the size of the sub-array does not affect the data volume because it just increases the number of frames so that approximately the same amount of data in pixels is saved to JWST's solid state recorder.
@@
 The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST.
-Figure \ref{fig:DHSaps} shows the saturation limits for the DHS mode along with NIRCam's long wavelength grisms.
-Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
+Figure \ref{fig:DHSaps} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
+Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
 The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS).
@@
 \includegraphics[width=0.5\textwidth]{sat_limits.jpg}
-\caption{Saturation limits of the DHS mode (blue), and long wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
+\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
 The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.}\label{fig:DHSaps}
@@
 
-We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to show the scientific value of using the DHS simultaneously with NIRCam's long wavelength grisms.
+We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to show the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
 We first simulate a forward model of a transmission spectrum for a planet (in this case HD 209458b).
@@
 This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra.
-The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the detector noise floor (35 ppm) for the long wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short wavelength DHS observations.
+The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the detector noise floor (35 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
 The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher signal to noise and full wavelength coverage from 0.7 to 2.4$\mu$m can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
@@
 A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor.
-However, the retrieval for the spectrum with only NIRCam's long wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}.
+However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}.
 Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.
@@
 The time needed to observe in JWST's full range of wavelengths from 0.6$\mu$m to 28$\mu$m, however, can add up quickly since many transits are needed with different instrument modes to cover all wavelengths.
-We introduced a new science mode using the Dispersed Hartmann Sensor's on the NIRCam instrument which enable simultaneous measurements of spectra at R $\sim$ \DHSres\ from 1.0 to 2.0$\mu$m while using the NIRCam long wavelength grisms covering either 2.4$\mu$m to 4.0$\mu$m or 3.9$\mu$m to 5.0$\mu$m.
-The readout mode and subarray size much be chosen carefully on the DHS so as to not saturate the long wavelength grisms.
+We introduced a new science mode using the Dispersed Hartmann Sensor's on the NIRCam instrument which enable simultaneous measurements of spectra at R $\sim$ \DHSres\ from 1.0 to 2.0$\mu$m while using the NIRCam long-wavelength grisms covering either 2.4$\mu$m to 4.0$\mu$m or 3.9$\mu$m to 5.0$\mu$m.
+The readout mode and subarray size much be chosen carefully on the DHS so as to not saturate the long-wavelength grisms.
 

### 2016-05-06 ms.tex
I added Lisa May's specific comments and corrections to the text.

@@
 %\documentclass[manuscript]{aastex}
-\documentclass{emulateapj}
+\documentclass[iop]{emulateapj}
 
@@
 
-\author{E. Schlawin \and M. Rieke? \and J. Leisenring \and  L. M. Walker  \and J. Fraine? \and D. Kelly \and K. Misselt}
+\author{E. Schlawin \and M. Rieke \and J. Leisenring \and  L. M. Walker  \and J. Fraine? \and D. Kelly \and K. Misselt}
 \affil{Steward Observatory, Tucson AZ 85721}
@@
 \includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
-\caption{Model spectra divided up by molecule for HD209458b.
+\caption{Model spectra separated by molecule for HD209458b.
 The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength arm.
@@
 
+\subsection{DHS properties}
+The DHS expands the wavelength range that NIRCam can achieve on a single observation by simultaneously obtaining spectroscopy with NIRCam's short wavelength arm and long wavelength arm.
+The wavelength range for the F150W2 filter in the short wavelength arm is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
+There will be about a 0.04$\mu$m gap in the spectrum due to the gap between short wavelength detectors.
+The center of this gap depends on source position.
+The DHS can be used in tandem with either the F322W2 or F444W filter for the long wavelength grism observations.
+The The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
+If the region from 2-2.2 is highly desirable, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength arms.
+
+\begin{table}
+%\centering
+\begin{tabular}{ccr}
+		& DHS	& Grism \\
+ \hline \hline		
+Resolution &  \DHSres & 1770 \\
+Dispersion & 0.29 nm / px & 1.0 nm / px \\
+Wavelengths & 1.01 - 2.02$\mu$m (F150W2)\footnote{There is a 0.05$\mu$m gap between detectors that depends on field position} & 2.44 - 4.02$\mu$m (F322W2)\\
+				& 								& 3.88 - 4.98$\mu$m (F444W) \\
+Plate Scale & 32 mas/px  &  65 mas / px\\
+\hline
+\end{tabular}
+\caption{Properties of DHS and simultaneous long-wavelength grism spectra.}\label{tab:DHSgprop}
+\vspace{0.1in}
+\end{table}
+
+\subsection{DHS Layout}
+
 A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength arm and one spectrum on the long-wavelength arm -- see Figure \ref{fig:DHSimage}.
-The DHS mode is only well suited for one source at a time because of the large number of spectra that would overlap in a crowded field.
-The 10 separate DHS spectra are spread across two of NIRCam's short-wavelength detectors.
+The DHS spectra span two of NIRCam's short-wavelength detectors covering 1-2$\mu$m with a 0.05$\mu$m due to the separation between detectors.
+The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but would be ill-suited for a crowded field, where the spectra would overlap.
 Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
-Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports seen in Figure \ref{fig:DHSvsPupilOverlay}.
+Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure \ref{fig:DHSvsPupilOverlay}.
 Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum.
-For sub-array sizes encompassing 1 DHS spectra, the large unobscured DHS grisms should be used like numbers 3, 7 or 9.
+For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure \ref{fig:DHSvsPupilOverlay}.
 
@@
 \includegraphics[width=0.5\textwidth]{dhs_image_example.png}
-\caption{Example images of the same source observed with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right).
+\caption{Example images of the same source observed simultaneously with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right).
 These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard.
-Only 3 detectors will be needed for transit observations.}\label{fig:DHSimage}
+Only 3 detectors will be needed for transit observations \textbf{Update w/ Mod A image and w/ C grism estimate}.}\label{fig:DHSimage}
 \end{figure}
-
-\begin{table}
-\centering
-\begin{tabular}{ccc}
- &  R $\sim$ \DHSres \\
- \hline \hline
-Dispersion & 0.29 nm / px \\
-Wavelength Range & 1$\mu$m to 2$\mu$m, 0.05$\mu$m gap \\
-Plate Scale & 32 mas/px \\
-\hline \hline
-Grism Resolution & R $\sim$ 1770 \\
-Dispersion & 1.0 nm / px  \\
-Wavelength Range F322W2 & 2.44$\mu$m to 4.02$\mu$m \\
-Wavelength Range F444W & 3.88$\mu$m to 4.98 $\mu$m \\
-Plate Scale & 65 mas/px \\
-\end{tabular}
-\caption{Properties of DHS and simultaneous long-wavelength grism spectra.}\label{tab:DHSgprop}
-\end{table}
 
@@
 \hline \hline
-1 & 0.033 \\
-2 & 0.047 \\
-3 & 0.036 \\
-4 & 0.043 \\
-5 & 0.030 \\
-6 & 0.032 \\
-7 & 0.042 \\
-8 & 0.045 \\
-9 & 0.040 \\
-10 & 0.033 \\
+1 & ?? \\
+2 & ?? \\
+3 & ?? \\
+4 & ?? \\
+5 & ?? \\
+6 & ?? \\
+7 & ?? \\
+8 & ?? \\
+9 & ?? \\
+10 &??  \\
 \end{tabular}
-\caption{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area. \textbf{Needs updating after correcting for the OSIM circles.}}\label{tab:pupfrac}
+\caption{Pupil Coverage}\label{tab:pupfrac}
+\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.
+\textbf{Needs updating after correcting for the OSIM circles and for clocking.}}\label{tab:pupfrac}
 \end{table}
@@
 \includegraphics[width=0.4\textwidth]{dhs_pupil_overlay.png}
-\caption{DHS pupil coverage by each of the 10 DHS grisms, with the fractional throughput given in Table \ref{tab:pupfrac}.
+\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}.
+.
 The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (black lines).
-The circles in the image are products of the OSIM (optical telescope element simulator) test source used in Cryogenic Vacuum testing of the instrument suite, and will not be present in flight.}\label{fig:DHSvsPupilOverlay}
+The circles in the image are products of the OSIM (optical telescope element simulator) test source used in Cryogenic Vacuum testing of the instrument suite, and will not be present in flight.
+The pupil wheel is clocked to make the DHS spectra straight along rows, but moves the DHS elements off-center from JWST's pupil and masks.
+\textbf{Remove circles and secondary struts from Orange}}\label{fig:DHSvsPupilOverlay}
+\end{figure}
 
-\end{figure}
 \subsection{Readout Considerations}\label{sec:readout}
-JWST's NIRCam has many different possible readout patterns per pixel and array that all factor in to the Signal to Noise Ratios (SNRs) and saturation limits for for an observation.
+JWST's NIRCam has many different possible readout patterns per pixel and array that all factor in to the SNRs and saturation limits for an observation.
 We adopt the following naming convention for the readout: An observation may consist of one of more exposures which are typically combined into a single \texttt{FITS} file per exposure.
-Within an exposure, there 1 or more integrations, which consist of a reset frame followed by 1 or more groups of non-destructive reads up a ramp.
+Within an exposure, there are 1 or more integrations, which consist of a reset frame followed by 1 or more groups of non-destructive reads up a ramp.
 This is illustrated in Fig \ref{fig:readout} for three example readout modes.
@@
 
-Each NIRCam array must be read out with identical window sizes and exposure times (due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}).
-This means that some balance must be made between saturating grism spectra (which has much higher throughput) in the long-wavelength and getting the most flux in the short wave DHS spectrum (which has lower throughput and also spreads the light over more pixels).
+Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}).
+This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
 
-The balance between saturating the long-wavelength grism and getting enough signal to noise in the DHS is listed in Table \ref{tab:SatSNRsubA}.
-The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the signal to noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration.
-We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} is used and we consider 80\% well depth in the second read as saturation.
+The balance between saturating the long-wavelength grism and getting enough SNR in the DHS is listed in Table \ref{tab:SatSNRsubA}.
+The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the DHS noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration and binned to a resolution of 100.
+We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} and we consider 80\% well depth in the second read as saturation.
+The sub-array sizes and order of DHS elements is shown in Figure \ref{fig:DHSaps}.
 
@@
 \hline \hline
-1600$\times$ 64 & 4.03 & 1 &  ?? \\
-1600$\times$ 200 & 5.25 & 2 &  ?? \\
-1600$\times$ 500 & 6.23 & 4 &  ?? \\
-1600$\times$ 1240 & 7.22 & 10 & ??
+2048$\times$ 64 & 4.03 & 1 &  ?? \\
+2048$\times$ 200 & 5.25 & 2 &  ?? \\
+2048$\times$ 500 & 6.23 & 4 &  ?? \\
+2048$\times$ 1240 & 7.22 & 10 & ??
 \end{tabular}
 \caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes.
-The size affects the number of DHS that can be included, so the Signal To Noise at 1.5$\mu$m in the DHS spectrum at the given saturation limit for a 1 hour transit is shown in column 4.}\label{tab:SatSNRsubA}
+The size affects the number of DHS that can be included, so the SNR at 1.5$\mu$m in the DHS spectrum at the given saturation limit for a 1 hour transit is shown in column 4.}\label{tab:SatSNRsubA}
 \end{table}
@@
 Second, the detector can be read out in BRIGHT1 mode, seen in Figure \ref{fig:readout}.
-This is where each a frame is dropped between read 2 and read 1 to increase the integration time while reducing data volume.
+This is where a frame is dropped between read 2 and read 1 to increase the integration time and efficiency while reducing data volume.
 This only works for sources faint enough that the long-wavelength grisms do not saturate.
@@
 We first simulate a forward model of a transmission spectrum for a planet (in this case HD 209458b).
-We then add Gaussian noise using the signal to noise estimated on the target to create a simulated spectrum.
-Finally, we run an Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
+We then add Gaussian noise using the SNR estimated on the target to create a simulated spectrum.
+Finally, we run a Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
 We combine the individual gases' posterior distributions for the C/O ratio and metallicity.
@@
 For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
-We assume that each of these was accompanied by a DHS spectrum for the 1.01$\mu$ to 2.0$\mu$m wavelength range, which benefits in signal to noise by $\sqrt(2)$ for the two separate observations.
+We assume that each of these was accompanied by a DHS observation for the 1.01$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt(2)$ for the two separate observations.
 This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra.
 The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the detector noise floor (35 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
-The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher signal to noise and full wavelength coverage from 0.7 to 2.4$\mu$m can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
+The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from 0.7 to 2.4$\mu$m can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
 
@@
 \caption{Posterior distributions of the retrieved abundances, showing improvements of the constraints on temperature, cloud pressure upper limit and H$_2$O, CO$_2$ and CO abundances with the DHS.
-Vertical dashed bars show the input abundances for the initial forward model that was used to generate the simulated spectru.}\label{fig:DHSadded}
+Vertical dashed bars show the input abundances for the initial forward model that was used to generate the simulated spectru.}\label{fig:DHSposterios}
 \end{figure}
@@
 
-One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances.
+One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:DHSposterios}.
 A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor.
@@
 The time needed to observe in JWST's full range of wavelengths from 0.6$\mu$m to 28$\mu$m, however, can add up quickly since many transits are needed with different instrument modes to cover all wavelengths.
-We introduced a new science mode using the Dispersed Hartmann Sensor's on the NIRCam instrument which enable simultaneous measurements of spectra at R $\sim$ \DHSres\ from 1.0 to 2.0$\mu$m while using the NIRCam long-wavelength grisms covering either 2.4$\mu$m to 4.0$\mu$m or 3.9$\mu$m to 5.0$\mu$m.
-The readout mode and subarray size much be chosen carefully on the DHS so as to not saturate the long-wavelength grisms.
+We introduced a new science mode using the Dispersed Hartmann Sensors on the NIRCam instrument which enable simultaneous measurements of spectra at R $\sim$ \DHSres\ from 1.0 to 2.0$\mu$m while using the NIRCam long-wavelength grisms covering either 2.4$\mu$m to 4.0$\mu$m or 3.9$\mu$m to 5.0$\mu$m.
+The readout mode and subarray size must be chosen carefully on the DHS so as to not saturate the long-wavelength grisms.
 
@@
 Furthermore, the improved water vapor constraints also improve CO and CO$_2$ abundances because of the correlation of these derived parameters.
-We encourage the implementation and approval of the DHS mode to enable this additional science.
+We encourage the implementation and approval of the DHS mode to enable this additional science in less time for this limited life observatory.
 

### 2016-05-06 ms.tex
I use the included bibliography file instead of the master one on my computer.
I added some points about the cost of only getting one DHS spectrum and also explained that the subarray sizes could theoretically be different between long wavelength and short wavelengths.

@@
 Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}).
+The window sizes could theoretically be different between the long-wavelength and short-wavelength detectors with only software changes, but would require large changes to the existing software.
 This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
@@
 The sub-array sizes and order of DHS elements is shown in Figure \ref{fig:DHSaps}.
+For the brightest sources, which require the 2048 $\times$ 64 pixel subarray, the DHS throughput loss is significant, because only 1 DHS spectrum out of 10 is used, meaning only about 4\% of JWST's 25 m$^2$ collecting area is used.
 
@@
 \bibliographystyle{apj}
-\bibliography{/Users/everettschlawin/evmemo_folder/pdfs/master_bib_file/master_biblio.bib}
-%\bibliography{master_biblio.bib}
+\bibliography{dhs_biblio}
 

### 2016-05-06 ms.tex
I made the tex file one sentence per line to make it work better with version control.
I added aastex6.cls as an optional manuscript style.
I explained the colors in the saturation limits plot.

@@
 %\documentclass{article}
-%\documentclass[manuscript]{aastex}
+%\documentclass[twocolumn]{aastex6}
 \documentclass[iop]{emulateapj}
@@
 \begin{table}
-%\centering
+\centering
 \begin{tabular}{ccr}
@@
 %The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs.
-The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m.
-If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
+%The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m.
+%If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
 \begin{figure}[!ht]
@@
 \caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}. 
-.
 The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (black lines).
@@
 No reset frames or dropped frames are saved.``1 Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
-The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but will saturate more easily.
-}\label{fig:readout}
+The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but will saturate more easily.}\label{fig:readout}
 \end{figure}
@@
 \caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
-The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.}\label{fig:DHSaps}
+The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
+The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:DHSaps}
 \end{figure}
@@
 
-%The DHS improves constraints on HD209458b's temperature (assumed isothermal in this model), abundances and cloud pressure layer, as visible in Figure \ref{fig:cornerRun}.
-The improvements in abundances are
-
 \begin{figure*}
@@
 CHIMERA retrieval makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
-For use of the El Gato computing system, this material is based upon work supported by the National Science Foundation under Grant No.
-1228509.
+For use of the El Gato computing system, this material is based upon work supported by the National Science Foundation under Grant No. 1228509.
 Thanks to Michael Bruck at the High Performance Computing center at the University of Arizona for assisting with setting up the CHIMERA runs to utilize the HPC hardware.

### 2016-06-24 ms.tex
Added commas between authors.
I put in the pupil fractions and also some notes about clocking the pupil wheel.

@@
 
-\author{E. Schlawin \and M. Rieke \and J. Leisenring \and  L. M. Walker  \and J. Fraine? \and D. Kelly \and K. Misselt}
+\author{E. Schlawin, M. Rieke, J. Leisenring, L. M. Walker, J. Fraine?, D. Kelly, K. Misselt}
 \affil{Steward Observatory, Tucson AZ 85721}
@@
 
-\author{N. Lewis? \and J. Stansberry}
+\author{N. Lewis?, J. Stansberry}
 \affil{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
@@
 Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure \ref{fig:DHSvsPupilOverlay}.
-Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum.
+We elected to clock the pupil wheel by 1.9$^\circ$ in order to align the spectra with rows on the short wavelength detector.
+Aligning spectra along the rows enables small stripe mode readouts (such as 2048 $\times$ 64) to read one DHS spectra simultaneously with long wavelength grism spectra.
+This is needed for bright targets that will saturate the long wavelength detector with longer frame times, as shown in Section \ref{sec:readout}.
+There is a price for clocking the DHS pupil wheel to align spectra with rows: all DHS grisms are partially obscured, save element 7.
+Fortunately, the relative obscuration for all 10 DHS spectra is small, going from 32\% when the pupil wheel is centered (which produces tilted spectra), versus 29\% if the pupil wheel is clocked to align the spectra along rows.
+Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum where 1.00 would use the entire pupil and JWST collecting area.
 For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure \ref{fig:DHSvsPupilOverlay}.
@@
 \hline \hline
-1 & ?? \\
-2 & ?? \\
-3 & ?? \\
-4 & ?? \\
-5 & ?? \\
-6 & ?? \\
-7 & ?? \\
-8 & ?? \\
-9 & ?? \\
-10 &??  \\
+1 & 0.012 \\
+2 & 0.032 \\
+3 &  0.032 \\
+4 & 0.040 \\
+5 & 0.021 \\
+6 & 0.015 \\
+7 & 0.042 \\
+8 & 0.040 \\
+9 & 0.036 \\
+10 & 0.022 \\
+\hline
+Total & 0.292
 \end{tabular}
 \caption{Pupil Coverage}\label{tab:pupfrac}
-\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.
-\textbf{Needs updating after correcting for the OSIM circles and for clocking.}}\label{tab:pupfrac}
+\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}\label{tab:pupfrac}
 \end{table}
@@
 The circles in the image are products of the OSIM (optical telescope element simulator) test source used in Cryogenic Vacuum testing of the instrument suite, and will not be present in flight.
-The pupil wheel is clocked to make the DHS spectra straight along rows, but moves the DHS elements off-center from JWST's pupil and masks.
+The pupil wheel is clocked to make the DHS spectra straight along rows, but this moves the DHS elements off-center from JWST's pupil and masks.
 \textbf{Remove circles and secondary struts from Orange}}\label{fig:DHSvsPupilOverlay}
@@
 
-Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}).
+Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS).
 The window sizes could theoretically be different between the long-wavelength and short-wavelength detectors with only software changes, but would require large changes to the existing software.
 This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
+The current software requires that the sub-array locations must be identical for NIRCam's short wavelength arrays and long wavelength arrays.
+We recommend  the sub-array locations to be adjustable so that the short wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long wavelength array can be centered on a single grism spectrum.
+The software also is limited subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra.
 

### 2016-07-03 ms.tex
I updated the DHS and grism resolutions.

@@
 \newcommand{\vdag}{(v)^\dagger}
-\newcommand{\DHSres}{3000 ?}
+\newcommand{\DHSres}{272 - 304}
 
@@
 The wavelength range for the F150W2 filter in the short wavelength arm is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
+The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width in the dispersion direction.
+Figure \ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from the spatial PSF and the aspect ratio of dispersion and spatial directions.
 There will be about a 0.04$\mu$m gap in the spectrum due to the gap between short wavelength detectors.
@@
 
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.4\textwidth]{dhs_res.pdf}
+\caption{Resolution as a function of wavelength for the DHS.}\label{fig:DHSRes}
+\end{figure}
+
 \begin{table}
@@
  \hline \hline		
-Resolution &  \DHSres & 1770 \\
+Resolution &  \DHSres & 1200 - 1550 \\
 Dispersion & 0.29 nm / px & 1.0 nm / px \\
@@
 These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard.
-Only 3 detectors will be needed for transit observations \textbf{Update w/ Mod A image and w/ C grism estimate}.}\label{fig:DHSimage}
+Only 3 detectors will be needed for transit observations \textbf{Update w/ Mod A image and w/ R grism estimate}.}\label{fig:DHSimage}
 \end{figure}

### 2016-07-03 ms.tex
I updated the figure with contours for HD 209458b retrievals both with and without the DHS.

@@
 \centering
-\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_nc_only_subset.png}
-\caption{Posterior distributions an MCMC run of HD209458b without the DHS.
+\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
+\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) laid on top of that for the NIRCam girsms only without the DHS (gray).
 The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.}\label{fig:cornerRun}

### 2016-07-07 ms.tex
I simplified the description of the contours with and without the DHS.
I moved the science benefits section first since it's the main argument of the paper.

@@
 The NIRCam instrument was primarily designed as an imager, but includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments.
-NIRCam's long-wavelength arm includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R \sim 1770$ and it has already been approved for wide field slitless spectroscopy.
+NIRCam's long-wavelength arm includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R = 1200 - 1550$ and it has already been approved for wide field slitless spectroscopy.
 We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength arm.
-This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spectra for every source at $R \sim \DHSres$.
+This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spatially separated spectra per source source at $R \sim \DHSres$.
 The DHS can observe the brightest host stars of any JWST mode.
@@
 In this white paper, we argue for the inclusion of the DHS mode to fully take advantage of two NIRCam arms to maximize JWST's science potential for transiting planets.
+In section \ref{sec:addedScience} we discuss the added science that can be achieved with the DHS, including the brightness limits and improved precision in retrieved parameters for a representative system.
 In section \ref{sec:implementation}, we discuss how the DHS would work for time-series observations and the implications of reading out several detectors simultaneously at a high frame rate.
-In section \ref{sec:addedScience} we discuss the added science that can be achieved with the DHS, including the brightness limits and improved precision in retrieved parameters for a representative system.
+
+\section{Science Benefits with the DHS}\label{sec:addedScience}
+
+\subsection{Brightness limits}\label{sec:brightness}
+
+The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST.
+Figure \ref{fig:DHSaps} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
+Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
+The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS).
+
+\begin{figure}[!ht]
+\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
+\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
+The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
+The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:DHSaps}
+\end{figure}
+
+\subsection{CHIMERA Simulations}\label{sec:simulations}
+
+We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to show the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
+We first simulate a forward model of a transmission spectrum for a planet (in this case HD 209458b).
+We then add Gaussian noise using the SNR estimated on the target to create a simulated spectrum.
+Finally, we run a Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
+We combine the individual gases' posterior distributions for the C/O ratio and metallicity.
+
+For the initial model, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the settling out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}.
+The atomic abundances are converted to molecular mixing ratios using the Chemical Equilibrium code with Applications (CEA) \footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} to calculate the fractions of molecules at the given pressure and temperature.
+For HD209458b, this is at a reference pressure of 0.01 bars and a reference temperature of 1440K.
+We assume that the abundances and temperature are constant with altitude.
+We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$,H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as sources of opacity, but only H$_2$O, CO, and CO$_2$ contribute significantly to the opacity, as seen in Figure \ref{fig:DHSmolecules}.
+% if we run the simulations later, also mention emission spectra
+
+For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
+We assume that each of these was accompanied by a DHS observation for the 1.01$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt(2)$ for the two separate observations.
+This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra.
+The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the detector noise floor (35 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
+The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from 0.7 to 2.4$\mu$m can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
+\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
+Similar wavelength coverage can be achieved in just 3 different transits or $\sim$ 33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
+\end{figure}
+
+We use CHIMERA and a Markov Chain Monte Carlo (MCMC) retrieval to recover the individual atmospheric abundances of the simulated spectrum.
+The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile 2) the altitude of the 10-bar pressure surface where the model begins 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths 4-11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively 12) an amplitude of a Raleigh-like haze and 13) a power law index for the Raleigh-type haze.
+We assume flat priors in log space for all abundances from volume mixing ratios of 10$^{-12}$ to 1.
+The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 to allow for burn-in.
+
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_DHS.pdf}
+%\caption{Posterior distributions of the retrieved abundances, showing improvements of the constraints on temperature, cloud pressure upper limit and H$_2$O, CO$_2$ and CO abundances with the DHS.
+%Vertical dashed bars show the input abundances for the initial forward model that was used to generate the simulated spectru.}\label{fig:DHSposterios}
+%\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
+\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) and without the DHS (gray).
+The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.}\label{fig:cornerRun}
+\end{figure*}
+
+One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:DHSposterios}.
+A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor.
+However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}.
+Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.
 
@@
 Reducing the size of the sub-array does not affect the data volume because it just increases the number of frames so that approximately the same amount of data in pixels is saved to JWST's solid state recorder.
-
-\section{Science Benefits with the DHS}\label{sec:addedScience}
-
-\subsection{Brightness limits}\label{sec:brightness}
-
-The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST.
-Figure \ref{fig:DHSaps} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
-Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
-The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS).
-
-\begin{figure}[!ht]
-\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
-\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
-The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
-The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:DHSaps}
-\end{figure}
-
-\subsection{CHIMERA Simulations}\label{sec:simulations}
-
-We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to show the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
-We first simulate a forward model of a transmission spectrum for a planet (in this case HD 209458b).
-We then add Gaussian noise using the SNR estimated on the target to create a simulated spectrum.
-Finally, we run a Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
-We combine the individual gases' posterior distributions for the C/O ratio and metallicity.
-
-For the initial model, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the settling out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}.
-The atomic abundances are converted to molecular mixing ratios using the Chemical Equilibrium code with Applications (CEA) \footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} to calculate the fractions of molecules at the given pressure and temperature.
-For HD209458b, this is at a reference pressure of 0.01 bars and a reference temperature of 1440K.
-We assume that the abundances and temperature are constant with altitude.
-We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$,H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as sources of opacity, but only H$_2$O, CO, and CO$_2$ contribute significantly to the opacity, as seen in Figure \ref{fig:DHSmolecules}.
-% if we run the simulations later, also mention emission spectra
-
-For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
-We assume that each of these was accompanied by a DHS observation for the 1.01$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt(2)$ for the two separate observations.
-This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra.
-The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the detector noise floor (35 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
-The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from 0.7 to 2.4$\mu$m can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
-\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
-Similar wavelength coverage can be achieved in just 3 different transits or $\sim$ 33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
-\end{figure}
-
-We use CHIMERA and a Markov Chain Monte Carlo (MCMC) retrieval to recover the individual atmospheric abundances of the simulated spectrum.
-The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile 2) the altitude of the 10-bar pressure surface where the model begins 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths 4-11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively 12) an amplitude of a Raleigh-like haze and 13) a power law index for the Raleigh-type haze.
-We assume flat priors in log space for all abundances from volume mixing ratios of 10$^{-12}$ to 1.
-The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 to allow for burn-in.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_DHS.pdf}
-\caption{Posterior distributions of the retrieved abundances, showing improvements of the constraints on temperature, cloud pressure upper limit and H$_2$O, CO$_2$ and CO abundances with the DHS.
-Vertical dashed bars show the input abundances for the initial forward model that was used to generate the simulated spectru.}\label{fig:DHSposterios}
-\end{figure}
-
-\begin{figure*}
-\centering
-\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
-\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) laid on top of that for the NIRCam girsms only without the DHS (gray).
-The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.}\label{fig:cornerRun}
-\end{figure*}
-
-One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:DHSposterios}.
-A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor.
-However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}.
-Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.
 

### 2016-07-07 ms.tex
I got rid of multiply defined references to the pupil fraction table.
I changed the reference for the DHS versus no DHS posteriors from the histograms to now the corner plot since they're updated.

@@
 
-One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:DHSposterios}.
+One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:cornerRun}.
 A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor.
@@
 \caption{Pupil Coverage}\label{tab:pupfrac}
-\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}\label{tab:pupfrac}
+\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}
 \end{table}

### 2016-07-08 ms.tex
I added figures for HAT-P-12b's clear atmosphere model.

@@
 \includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
-\caption{Model spectra separated by molecule for HD209458b.
+\caption{Model spectra separated by molecule for HD 209458b.
 The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength arm.
@@
 We combine the individual gases' posterior distributions for the C/O ratio and metallicity.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_clear_DHS_nc.pdf}
+\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b.
+Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.}\label{fig:DHSvsNIRISS209}
+\end{figure}
 

### 2016-07-20 ms.tex
I added retrieval corner plots and the spectrum plot for the HAT-P-12b cloudy model.

--- 2016-07-07 ms.tex
@@
 
-\shorttitle{JWST NIRCam SW and LW}
+\shorttitle{NIRCam's DHS Mode}
 \shortauthors{Schlawin et al.}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
+\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
+Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
+A metallicity of 22 $\times$ solar from the relation in \citet{kreidberg2014wasp43}.}\label{fig:DHSvsNIRISS209}
+\end{figure}
+
 For the initial model, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the settling out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}.
@@
 For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
-We assume that each of these was accompanied by a DHS observation for the 1.01$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt(2)$ for the two separate observations.
+We assume that each of these was accompanied by a DHS observation for the 1.01$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
 This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra.
@@
 
-One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:cornerRun}.
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
+\caption{Posterior distributions an MCMC retrieval of parameters for HAT-P-12b with the DHS (blue) and without the DHS (gray).}\label{fig:cornerHATp12}
+\end{figure*}
+
+One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:cornerRun} and Figure \ref{fig:cornerHATp12}.
 A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor.
@@
 Plate Scale & 32 mas/px  &  65 mas / px\\
+Undeviated \\Wavelength & 1.36 $\mu$m & 4.00 $\mu$m   \\
 \hline
@@
 
-In normal operations, up to 232 Gbits of compressed science and telemetry data from James Webb Space Telescope are downlinked once per day over the 4 hour contact time with an antenna in the Deep Space Network (SDN)  \citep{dashevsky2008groundflight}.
+In normal operations, up to 232 Gbits of compressed science and telemetry data from James Webb Space Telescope are downlinked in a  4 hour contact time with an antenna in the Deep Space Network (SDN)  \citep{dashevsky2008groundflight}.
+There will be two downlinks per day so on average the total data rate can be about 540 Gbits per 12 hours.
 Science operations can continue during the 4 hour contact time, but re-pointing the high gain antenna can cause $<$0.07 \arcsec\ disturbances \citep{beichman2014pasp}.

### 2016-07-25 ms.tex
I updated the DHS resolution using the peak in the supercontinuum source.

@@
 \newcommand{\vdag}{(v)^\dagger}
-\newcommand{\DHSres}{272 - 304}
+\newcommand{\DHSres}{299 - 334}
+\newcommand{\DHSresApprox}{300}
 
@@
 We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength arm.
-This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spatially separated spectra per source source at $R \sim \DHSres$.
+This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spatially separated spectra per source source at $R \sim \DHSresApprox$.
 The DHS can observe the brightest host stars of any JWST mode.

### 2016-07-29 ms.tex
I removed some question marks from the DHS white paper.
I added a figure to show the simultaneous max wavelength coverage, updated the bibliography with a TESS example, and fixed up some wording.

@@
 
-\author{E. Schlawin, M. Rieke, J. Leisenring, L. M. Walker, J. Fraine?, D. Kelly, K. Misselt}
+\author{E. Schlawin, M. Rieke, J. Leisenring, L. M. Walker, J. Fraine, D. Kelly, K. Misselt}
 \affil{Steward Observatory, Tucson AZ 85721}
@@
 
-\author{M. Line?\altaffilmark{1,2,3,4}}
+\author{M. Line\altaffilmark{1,2,3,4}}
 \affil{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 95064}
 
-\author{N. Lewis?, J. Stansberry}
+\author{N. Lewis, J. Stansberry}
 \affil{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
@@
 The long-wavelength grisms are used in concert with broadband filters.
-The F322W2 filter encompasses 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter encompasses 3.88$\mu$ to 4.98$\mu$m at half maximum throughput.
+The F322W2 filter encompasses 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter encompasses 3.88$\mu$m to 4.98$\mu$m at half maximum throughput.
 These filters and grism are enabled and supported JWST science modes.
 The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput.
-The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the first order of the spectrum begins to overlap at at 2.0$\mu$m.
+The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the first order of the spectrum begins to overlap at at 2.0$\mu$m.\footnote{The prism that spatially separate the 10 DHS spectra separate the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
 
@@
 Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
-The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS).
+The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
 
@@
 Dispersion & 0.29 nm / px & 1.0 nm / px \\
-Wavelengths & 1.01 - 2.02$\mu$m (F150W2)\footnote{There is a 0.05$\mu$m gap between detectors that depends on field position} & 2.44 - 4.02$\mu$m (F322W2)\\
-				& 								& 3.88 - 4.98$\mu$m (F444W) \\
+Wavelengths & 1.08 - 2.02$\mu$m \footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
+			& 	1.01 - 1.98$\mu$m \footnote{For a field point matched to the F444W filter and long wavelength grism.
+There is a 0.05$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
 Plate Scale & 32 mas/px  &  65 mas / px\\
@@
 \textbf{Remove circles and secondary struts from Orange}}\label{fig:DHSvsPupilOverlay}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.49\textwidth]{grism_pos_for_max_wcoverage.pdf}
+\caption{DHS Wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source.
+The V2/V3 axes show the JWST observatory axes and the detectors are labeled for the A channel.}\label{fig:DHSwaveWGrism}
 \end{figure}

### 2016-07-29 ms.tex
I added further clarifications on the CHIMERA models for HAT-P-12b.

@@
 We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to show the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
-We first simulate a forward model of a transmission spectrum for a planet (in this case HD 209458b).
+We first simulate a forward model of a transmission spectrum for two planets, HD 209458b and HAT-P-12b.
 We then add Gaussian noise using the SNR estimated on the target to create a simulated spectrum.
@@
 
-For the initial model, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the settling out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}.
-The atomic abundances are converted to molecular mixing ratios using the Chemical Equilibrium code with Applications (CEA) \footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} to calculate the fractions of molecules at the given pressure and temperature.
-For HD209458b, this is at a reference pressure of 0.01 bars and a reference temperature of 1440K.
+For the initial model of HD 209458b, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the settling out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}.
+For HAT-P-12b, we scale the atomic abundances of all elements except Hydrogen and Helium by a factor of 22 using the mass-metallicity relation of \citep{kreidberg2014wasp43} and \citep{line2016hd209wfc3}.
+The atomic abundances are converted to molecular mixing ratios using the Chemical Equilibrium code with Applications (CEA)\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} to calculate the fractions of molecules at the given pressure and temperature.
+For HD209458b and HAT-P-12b, this is at a reference pressure of 0.01 bars and a reference temperature of 1440K and 960 K respectively.
 We assume that the abundances and temperature are constant with altitude.
 We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$,H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as sources of opacity, but only H$_2$O, CO, and CO$_2$ contribute significantly to the opacity, as seen in Figure \ref{fig:DHSmolecules}.
+For the HAT-P-12b model, we include an opaque cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
 % if we run the simulations later, also mention emission spectra
@@
 We use CHIMERA and a Markov Chain Monte Carlo (MCMC) retrieval to recover the individual atmospheric abundances of the simulated spectrum.
-The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile 2) the altitude of the 10-bar pressure surface where the model begins 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths 4-11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively 12) an amplitude of a Raleigh-like haze and 13) a power law index for the Raleigh-type haze.
+The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile 2) the altitude of the 10-bar pressure surface where the model begins 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths 4) through 11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively 12) an amplitude of a Raleigh-like haze and 13) a power law index for the Raleigh-type haze.
 We assume flat priors in log space for all abundances from volume mixing ratios of 10$^{-12}$ to 1.
@@
 \caption{DHS Wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source.
-The V2/V3 axes show the JWST observatory axes and the detectors are labeled for the A channel.}\label{fig:DHSwaveWGrism}
+The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.}\label{fig:DHSwaveWGrism}
 \end{figure}

### 2016-07-29 ms.tex
I fixed some multiply defined labels.

@@
 The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST.
-Figure \ref{fig:DHSaps} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
+Figure \ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
 Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
@@
 The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
-The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:DHSaps}
+The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:saturationLim}
 \end{figure}
@@
 Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
-A metallicity of 22 $\times$ solar from the relation in \citet{kreidberg2014wasp43}.}\label{fig:DHSvsNIRISS209}
+A metallicity of 22 $\times$ solar from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
 \end{figure}

### 2016-07-31 ms.tex
I updated the wavelength coverage, HD209458b corner plot and some other details."

@@
 The simulated data are for one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
-The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:DHSmolecules}
+The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:209spec}
 \end{figure}
@@
 
-\subsection{CHIMERA Simulations}\label{sec:simulations}
+\subsection{CHIMERA Models}\label{sec:models}
 
@@
 Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
-A metallicity of 22 $\times$ solar from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
+A planet metallicity of 22 $\times$ solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
 \end{figure}
@@
 We assume that the abundances and temperature are constant with altitude.
-We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$,H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as sources of opacity, but only H$_2$O, CO, and CO$_2$ contribute significantly to the opacity, as seen in Figure \ref{fig:DHSmolecules}.
+We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$,H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as sources of opacity, but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
 For the HAT-P-12b model, we include an opaque cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
+For HD 209458b, this cloud deck is placed at a pressure level of 1 bar which is too low in altitude to affect the spectrum, as shown in Figure \ref{fig:209spec}.
 % if we run the simulations later, also mention emission spectra
@@
 
+\subsection{CHIMERA Retreivals}\label{sec:retrievals}
+
+The posterior distributions for retrieved parameters for the most important abundances are shown in Figures \ref{fig:corner209} and \ref{fig:cornerHATp12}.
+We show the posterior distributions for two cases:
+\begin{enumerate}
+\item \label{it:DHSgr} An observation with the long wavelength grisms alone (2.4$\mu$m to 5.0$\mu$m), shown in green.
+\item \label{it:grAlone} An observation with the long wavelength grisms (2.44$\mu$m to 5.0$\mu$m) with simultaneous DHS spectra (1.0-2.0$\mu$m), shown in blue
+\end{enumerate}
+For the spectral data they have in common (2.4$\mu$m to 5.0$\mu$m), we use the same noise instance to make direct comparison easier.
+
+The posterior distributions for HD 209458b in Figure \ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used with the long wavelength grisms (Case \ref{it:DHSgr}) as compared to the long wavelength grisms alone (Case \ref{it:grAlone}).
+These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.
+
 \begin{figure*}
@@
 \includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
-\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) and without the DHS (gray).
-The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.}\label{fig:cornerRun}
+\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) and without the DHS (green).
+The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.
+Abundances are given in Log$_{10}$(ppm).
+Cloud pressure is in Log$_{10}$(bar).}\label{fig:corner209}
 \end{figure*}
+
+The warm Saturn HAT-P-12b model shows improvements to the temperature constraints, but the cloud pressure measurements have similar uncertainties with and without the DHS.
+This is because the 1mbar cloud layer begins to affect the opacity near 4.0$\mu$m, which is measured by the long wavelength grisms.
+As with HD 209458b, the DHS improves constraints on the H$_2$O and CO$_2$ abundances, but since the planet is at a cooler temperatures, chemical equilibrium favors CH$_4$ over CO, so the constraints are much better on CH$_4$.
 
@@
 
-One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:cornerRun} and Figure \ref{fig:cornerHATp12}.
-A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor.
-However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}.
+One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:corner209} and Figure \ref{fig:cornerHATp12}.
+A quick glance at the contributions of individual molecules to the spectrum shown in Figures \ref{fig:209spec} and \ref{fig:HATp12spec} would indicate that the DHS is mainly important for water vapor.
+However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:corner209}.
 Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.
@@
 The DHS expands the wavelength range that NIRCam can achieve on a single observation by simultaneously obtaining spectroscopy with NIRCam's short wavelength arm and long wavelength arm.
-The wavelength range for the F150W2 filter in the short wavelength arm is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
+The maximum wavelength range for the F150W2 filter in the short wavelength arm is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
 The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width in the dispersion direction.
-Figure \ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from the spatial PSF and the aspect ratio of dispersion and spatial directions.
+Figure \ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
 There will be about a 0.04$\mu$m gap in the spectrum due to the gap between short wavelength detectors.
@@
 The DHS can be used in tandem with either the F322W2 or F444W filter for the long wavelength grism observations.
-The The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
-If the region from 2-2.2 is highly desirable, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength arms.
+The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
+If the region from 2-2.23 $\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength arms.
 
@@
 Dispersion & 0.29 nm / px & 1.0 nm / px \\
-Wavelengths & 1.08 - 2.02$\mu$m \footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
-			& 	1.01 - 1.98$\mu$m \footnote{For a field point matched to the F444W filter and long wavelength grism.
-There is a 0.05$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
+Wavelengths & 1.05 - 2.00$\mu$m (F150W2)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
+			 & 1.75 - 2.23$\mu$m (F200W)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
+			& 	1.01 - 1.94$\mu$m (F150W2) \footnote{For a field point matched to the F444W filter and long wavelength grism.
+There is a 0.04$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
 Plate Scale & 32 mas/px  &  65 mas / px\\
-Undeviated \\Wavelength & 1.36 $\mu$m & 4.00 $\mu$m   \\
+Undeviated \\Wavelength & 1.36 $\mu$m & 3.94 $\mu$m   \\
 \hline
 \end{tabular}
-\caption{Properties of DHS and simultaneous long-wavelength grism spectra.}\label{tab:DHSgprop}
+\caption{Properties of DHS and simultaneous long-wavelength grism spectra. The parameters are for the A-side grism in the direction aligned with detector rows (R).}\label{tab:DHSgprop}
 \vspace{0.1in}
@@
 \caption{DHS Wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source.
-The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.}\label{fig:DHSwaveWGrism}
+The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.
+The circles plotted for each grism are the shortest usable wavelength, undispersed wavelength and longest usable wavelength.}\label{fig:DHSwaveWGrism}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{readout_schematic.pdf}
+\includegraphics[width=0.49\textwidth]{readout_schematic.pdf}
 \caption{Schematic of example readout modes for an exposure that is 12 frame times in duration.
@@
 \begin{figure}[!ht]
-\includegraphics[width=0.5\textwidth]{example_ap_sizes.png}
+\includegraphics[width=0.49\textwidth]{example_ap_sizes.png}
 \caption{Example sub-array size options for one of the short-wavelength detectors for the DHS.
-Each element is labeled corresponding to the DHS apertures shown in Figure \ref{fig:DHSvsPupilOverlay}}\label{fig:DHSaps}
+Each element is labeled corresponding to the DHS apertures shown in Figure \ref{fig:DHSvsPupilOverlay}.\vspace{0.2in}}\label{fig:DHSaps}
 \end{figure}
@@
 The brightest known systems and similarly bright future TESS targets will be accessible with NIRCam's DHS mode.
-We present example usage of the DHS mode on HD 209458b and show that the temperature, cloud pressure level and water vapor constraints are improved with the DHS.
-Furthermore, the improved water vapor constraints also improve CO and CO$_2$ abundances because of the correlation of these derived parameters.
+We present example usage of the DHS mode on real example systems and show that the temperature, cloud pressure level and water vapor constraints are improved with the DHS.
+Furthermore, the improved water vapor constraints also feed back to higher precision CO and CO$_2$ abundances because of the correlation of these derived parameters.
 We encourage the implementation and approval of the DHS mode to enable this additional science in less time for this limited life observatory.

### 2016-07-31 ms.tex
I re-arranted the example DHS image and also replaced the pupil image with a simpler one.

@@
 \newcommand{\DHSresApprox}{300}
+\newcommand{\DHSgap}{0.04}
 
@@
 Figure \ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
-There will be about a 0.04$\mu$m gap in the spectrum due to the gap between short wavelength detectors.
+There will be about a \DHSgap$\mu$m gap in the spectrum due to the gap between short wavelength detectors.
 The center of this gap depends on source position.
@@
 			& 	1.01 - 1.94$\mu$m (F150W2) \footnote{For a field point matched to the F444W filter and long wavelength grism.
-There is a 0.04$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
+There is a \DHSgap$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
 Plate Scale & 32 mas/px  &  65 mas / px\\
@@
 
-A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength arm and one spectrum on the long-wavelength arm -- see Figure \ref{fig:DHSimage}.
-The DHS spectra span two of NIRCam's short-wavelength detectors covering 1-2$\mu$m with a 0.05$\mu$m due to the separation between detectors.
-The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but would be ill-suited for a crowded field, where the spectra would overlap.
+A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength arm and one spectrum on the long-wavelength arm -- see Figure \ref{fig:DHSwaveWGrism}.
+The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
+The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
 Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.49\textwidth]{grism_pos_for_max_wcoverage.pdf}
+\caption{DHS Wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source.
+The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.
+The circles plotted for each grism are the shortest usable wavelength, undispersed wavelength and longest usable wavelength.}\label{fig:DHSwaveWGrism}
+\end{figure}
+
 %The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs.
@@
 %If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
-\begin{figure}[!ht]
-\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
-\caption{Example images of the same source observed simultaneously with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right).
-These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard.
-Only 3 detectors will be needed for transit observations \textbf{Update w/ Mod A image and w/ R grism estimate}.}\label{fig:DHSimage}
-\end{figure}
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{dhs_pupil_overlay.png}
+\includegraphics[width=0.49\textwidth]{dhs_pupil_labels_modA.pdf}
 \caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}. 
-The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (black lines).
-The circles in the image are products of the OSIM (optical telescope element simulator) test source used in Cryogenic Vacuum testing of the instrument suite, and will not be present in flight.
-The pupil wheel is clocked to make the DHS spectra straight along rows, but this moves the DHS elements off-center from JWST's pupil and masks.
-\textbf{Remove circles and secondary struts from Orange}}\label{fig:DHSvsPupilOverlay}
+The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted "Y" shaped feature).
+The pupil wheel is clocked to make the DHS spectra straight along rows, but this moves the DHS elements off-center from JWST's pupil and masks and thus decreases throughput to elements 1 and 6 significantly.}\label{fig:DHSvsPupilOverlay}
 \end{figure}
 
-\begin{figure}
-\centering
-\includegraphics[width=0.49\textwidth]{grism_pos_for_max_wcoverage.pdf}
-\caption{DHS Wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source.
-The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.
-The circles plotted for each grism are the shortest usable wavelength, undispersed wavelength and longest usable wavelength.}\label{fig:DHSwaveWGrism}
+\begin{figure}[!ht]
+\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
+\caption{Example images of the same source observed simultaneously with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right).
+These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard.
+Only 3 detectors will be needed for transit observations \textbf{Update w/ Mod A image and w/ R grism estimate}.}\label{fig:DHSimage}
 \end{figure}

### 2016-08-02 ms.tex
I added some re-wording and better descriptions of the data volume limits.

@@
 For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
-We assume that each of these was accompanied by a DHS observation for the 1.01$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
+We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
 This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra.
@@
 Aligning spectra along the rows enables small stripe mode readouts (such as 2048 $\times$ 64) to read one DHS spectra simultaneously with long wavelength grism spectra.
-This is needed for bright targets that will saturate the long wavelength detector with longer frame times, as shown in Section \ref{sec:readout}.
-There is a price for clocking the DHS pupil wheel to align spectra with rows: all DHS grisms are partially obscured, save element 7.
-Fortunately, the relative obscuration for all 10 DHS spectra is small, going from 32\% when the pupil wheel is centered (which produces tilted spectra), versus 29\% if the pupil wheel is clocked to align the spectra along rows.
-Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum where 1.00 would use the entire pupil and JWST collecting area.
+This is needed for bright targets that will saturate the long wavelength detector with longer frame times, as discussed in Section \ref{sec:readout}.
+There is a price for clocking the DHS pupil wheel to align spectra with rows: all DHS grisms are partially obscured by either the secondary supports or the outer edges of the primary, save element 7.
+Fortunately, the relative obscuration for all 10 DHS spectra is small, going from 32\% total throughput when the pupil wheel is centered (which produces tilted spectra), versus 29\% if the pupil wheel is clocked to align the spectra along rows.
+Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum where 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
 For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure \ref{fig:DHSvsPupilOverlay}.
@@
 The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted "Y" shaped feature).
-The pupil wheel is clocked to make the DHS spectra straight along rows, but this moves the DHS elements off-center from JWST's pupil and masks and thus decreases throughput to elements 1 and 6 significantly.}\label{fig:DHSvsPupilOverlay}
+The pupil wheel is clocked to make the DHS spectra straight along rows.
+This moves the DHS elements off-center from JWST's pupil and thus decreases the throughput for elements 1 and 6, but the overall combined throughput for all 10 elements is only reduced from 32\% to 29\%.}\label{fig:DHSvsPupilOverlay}
 \end{figure}
 
-\begin{figure}[!ht]
-\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
-\caption{Example images of the same source observed simultaneously with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right).
-These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard.
-Only 3 detectors will be needed for transit observations \textbf{Update w/ Mod A image and w/ R grism estimate}.}\label{fig:DHSimage}
-\end{figure}
+%\begin{figure}[!ht]
+%\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
+%\caption{Example images of the same source observed simultaneously with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right).
+%These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard.
+%Only 3 detectors will be needed for transit observations \textbf{Update w/ Mod A image and w/ R grism estimate}.}\label{fig:DHSimage}
+%\end{figure}
 
@@
 JWST's NIRCam has many different possible readout patterns per pixel and array that all factor in to the SNRs and saturation limits for an observation.
-We adopt the following naming convention for the readout: An observation may consist of one of more exposures which are typically combined into a single \texttt{FITS} file per exposure.
+We adopt the following naming convention for the readout: an observation may consist of one of more exposures which are typically combined into a single \texttt{FITS} file per exposure.
 Within an exposure, there are 1 or more integrations, which consist of a reset frame followed by 1 or more groups of non-destructive reads up a ramp.
@@
 \caption{Schematic of example readout modes for an exposure that is 12 frame times in duration.
-A single FITS file is saved for the exposure, consisting of 1-2 groups (read 1 or both read 1 and read 2) per integration.
+A single FITS file is saved for the exposure, consisting of 1 or more groups per integration.
 No reset frames or dropped frames are saved.``1 Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
@@
 Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS).
-The window sizes could theoretically be different between the long-wavelength and short-wavelength detectors with only software changes, but would require large changes to the existing software.
+%The window sizes could theoretically be different between the long-wavelength and short-wavelength detectors with only software changes, but would require large changes to the existing software.
 This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
@@
 We recommend  the sub-array locations to be adjustable so that the short wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long wavelength array can be centered on a single grism spectrum.
-The software also is limited subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra.
+The current time series observing templates is limited subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure \ref{fig:DHSaps}.
+
+\begin{figure}[!ht]
+\includegraphics[width=0.49\textwidth]{example_ap_sizes.pdf}
+\caption{Example DHS image on the A1 short wavelength detector taken during cryogenic vacuum testing of the flight hardware -- see Figure \ref{fig:DHSwaveWGrism} for the detector's position.
+Each element is labeled corresponding to the DHS apertures shown in Figure \ref{fig:DHSvsPupilOverlay} and pupil fraction in Table \ref{tab:pupfrac}.
+The sub-array size options currently available (all 2048 pixels wide) are shown with selections for the brightest spectra available - elements 7 and 8.}\label{fig:DHSaps}
+\end{figure}
 
@@
 We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} and we consider 80\% well depth in the second read as saturation.
+If the bias level after each reset remains stable over the course of observations, it may be possible to use ``1 Group Readout'', illustrated in Figure \ref{fig:readout}.
+The 1 Group Readout method can push the brightness limits by a factor of 2 over CDS because it reduces the integration time by a factor of 2.
 The sub-array sizes and order of DHS elements is shown in Figure \ref{fig:DHSaps}.
-For the brightest sources, which require the 2048 $\times$ 64 pixel subarray, the DHS throughput loss is significant, because only 1 DHS spectrum out of 10 is used, meaning only about 4\% of JWST's 25 m$^2$ collecting area is used.
+For the brightest sources, which require the 2048 $\times$ 64 pixel subarray, the DHS throughput loss is significant, because only 1 DHS spectrum out of 10 is used, meaning only 4.2\% of JWST's 25 m$^2$ collecting area is used.
 
@@
 
+\subsubsection{Data Volume}
+For most transiting planet science, the targets are bright and so the pixels will continuously be read out quickly without any co-added reads.
+The amount of data streaming from the detectors can overload the Solid State Recorder (SSR), which has a capacity of 540 Gbits \citep{johns2008L2comm}.
+We consider the use of 458 Gbits of space for science data as the maximum the SSR can handle at once.
+This overload can happen in as few as 10.3 hours if three NIRCam detectors are used simultaneously and all are read out with four amplifiers in CDS mode (meaning no samples are co-added or dropped) -- see Figure \ref{fig:DataVolume}.
+
 \begin{figure}[!ht]
-\includegraphics[width=0.49\textwidth]{example_ap_sizes.png}
-\caption{Example sub-array size options for one of the short-wavelength detectors for the DHS.
-Each element is labeled corresponding to the DHS apertures shown in Figure \ref{fig:DHSvsPupilOverlay}.\vspace{0.2in}}\label{fig:DHSaps}
+\includegraphics[width=0.49\textwidth]{NIRCam_grism_max_exp.pdf}
+\caption{The maximum time JWST NIRCam can expose three detectors (e.g.
+A1, A3 and A5 in Figure \ref{fig:DHSwaveWGrism}) before filling up JWST's Solid State Recorder (SSR).
+The readout modes shown are for Rapid readouts (no skipped frames as in CDS) and Bright1 for both 1 amplifier and 4 amplifiers.
+The number of pixels read out affects the integration time and thus the data rate.
+The time needed for a phase curve of the planet HD 189733b and a transit of the system are shown for reference.}\label{fig:DataVolume}
 \end{figure}
 
-\subsubsection{Data Volume}
-For most transiting planet science, the targets are bright and so the pixels will continuously be read out and saved without any pauses or skips in the stream of data at $\sim$1.6 Mbits per second per amplifier per detector.
-The amount of data streaming from the detectors can overload the Solid State Recorder (SSR), which has a capacity of 540 Gbits \citep{johns2008L2comm} (\textbf{compressed data?}).
-This overload can happen in as few as 10 hours if three NIRCam detectors are used simultaneously and all are read out with four amplifiers in RAPID mode (meaning no samples are co-added or dropped).
-
-In normal operations, up to 232 Gbits of compressed science and telemetry data from James Webb Space Telescope are downlinked in a  4 hour contact time with an antenna in the Deep Space Network (SDN)  \citep{dashevsky2008groundflight}.
-There will be two downlinks per day so on average the total data rate can be about 540 Gbits per 12 hours.
+In normal operations, science and telemetry data from James Webb Space Telescope are downlinked in a 4 hour contact time with an antenna in the Deep Space Network (SDN)  \citep{dashevsky2008groundflight}.
+There will be two downlinks per day so on average the total data rate can no more than $\sim$458 Gbits per 12 hours.
 Science operations can continue during the 4 hour contact time, but re-pointing the high gain antenna can cause $<$0.07 \arcsec\ disturbances \citep{beichman2014pasp}.
-To satisfy these normal operations, the data volume must be reduced for observations longer than \textbf{How many do you think?
-6 hours to allow for telemetry and other science?} when using 3 detectors and 4 amplifiers simultaneously.
+To satisfy these normal operations, the data volume is a concern for bright objects requiring longer than $\sim$10 hours of continuous spectroscopy when using 3 detectors and 4 amplifiers simultaneously.
 
 There are a few ways to reduce the data volume streaming from the detectors.
-One way is to read each detector with a single amplifier (WINDOW mode).
+One way is to read each detector with a single amplifier.
 This reduces the frame rate by a factor of four (for the four amplifiers), thus allowing $\sim$40 hours before filling JWST's solid state recorders.
@@
 This only works for sources faint enough that the long-wavelength grisms do not saturate.
-Reducing the size of the sub-array does not affect the data volume because it just increases the number of frames so that approximately the same amount of data in pixels is saved to JWST's solid state recorder.
 
@@
 
-The James Webb Space Telescope will provide unprecedented measurements of transiting exoplanets, especially for carbon-bearing gases in their atmospheres.
+The James Webb Space Telescope will provide unprecedented measurements of transiting exoplanets, especially for carbon-bearing and nitrogen-bearing gases in their atmospheres.
 The time needed to observe in JWST's full range of wavelengths from 0.6$\mu$m to 28$\mu$m, however, can add up quickly since many transits are needed with different instrument modes to cover all wavelengths.
@@
 The brightest known systems and similarly bright future TESS targets will be accessible with NIRCam's DHS mode.
-We present example usage of the DHS mode on real example systems and show that the temperature, cloud pressure level and water vapor constraints are improved with the DHS.
+We present example usage of the DHS mode on example systems and show that the temperature, cloud pressure level and water vapor constraints are improved with the DHS.
 Furthermore, the improved water vapor constraints also feed back to higher precision CO and CO$_2$ abundances because of the correlation of these derived parameters.

### 2016-08-04 ms.tex
I updated the sub-array sizes, saturation magnitudes and number of DHSs for the saturation/noise table.
I got rid of an incorrect comma in C2H2.

@@
 We assume that the abundances and temperature are constant with altitude.
-We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$,H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as sources of opacity, but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
+We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as sources of opacity, but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
 For the HAT-P-12b model, we include an opaque cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
@@
 \hline \hline
-2048$\times$ 64 & 4.03 & 1 &  ?? \\
-2048$\times$ 200 & 5.25 & 2 &  ?? \\
-2048$\times$ 500 & 6.23 & 4 &  ?? \\
-2048$\times$ 1240 & 7.22 & 10 & ??
+2048$\times$ 64 & 4.52 & 1 &  ?? \\
+2048$\times$ 128 & 5.26 & 1 &  ?? \\
+2048$\times$ 256 & 6.01 & 2 &  ?? \\
+2048$\times$ 2048 & 8.26 & 10 & ??
 \end{tabular}

### 2016-08-05 ms.tex
Jarron rearranged the figures to make them better aligned with the text.

@@
 \usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
+\usepackage{graphicx}
+%\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-The James Webb Space Telescope (JWST) \citep[e.g.][]{gardner2006SSRv} has the potential to profoundly expand and deepen the science of transiting exoplanets \citep[e.g.][]{greene2016jwst_trans}.
+The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} has the potential to profoundly expand and deepen the science of transiting exoplanets \citep[e.g.][]{greene2016jwst_trans}.
 The wavelength coverage from 0.6$\mu$m to 28$\mu$m adds significantly to the wavelengths covered by the Hubble Space Telescope (HST) (currently 0.09$\mu$m to 1.7$\mu$m).
@@
 Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
-For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7 $\mu$m to 12 $\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7 to 2.5$\mu$m), two with NIRCam's long-wavelength arm (2.44$\mu$m to 4.98 $\mu$m) \footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
+For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7$\mu$m to 2.5$\mu$m), two with NIRCam's long-wavelength arm (2.44$\mu$m to 4.98$\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7~$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
 With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours.
@@
 
-The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5 $\mu$m.
-This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength arm and long-wavelength arm, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
-In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
-Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
-For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0 to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
-The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.
-
-\begin{figure}[!ht]
-\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
+\begin{figure}[t]
+\centering
+\includegraphics[width=1.0\columnwidth]{molecules_DHS_HD209.pdf}
 \caption{Model spectra separated by molecule for HD 209458b.
@@
 
+The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5$\mu$m.
+This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength arm and long-wavelength arm, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
+In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
+Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
+For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0$\mu$m to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
+The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.
+
 Since the DHS was not originally designed for science observations, it is not yet an approved mode for the James Webb Space Telescope.
@@
 In section \ref{sec:implementation}, we discuss how the DHS would work for time-series observations and the implications of reading out several detectors simultaneously at a high frame rate.
+
+\begin{figure}[!b]
+\includegraphics[width=1.0\columnwidth]{sat_limits.jpg}
+\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
+The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
+The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:saturationLim}
+\end{figure}
 
@@
 
-\begin{figure}[!ht]
-\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
-\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
-The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
-The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:saturationLim}
-\end{figure}
-
 \subsection{CHIMERA Models}\label{sec:models}
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
-\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
+\includegraphics[width=1.0\columnwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
 \caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
 Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
-A planet metallicity of 22 $\times$ solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
+A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
 \end{figure}
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
-\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
+\includegraphics[width=1.0\columnwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
 \caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
-Similar wavelength coverage can be achieved in just 3 different transits or $\sim$ 33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
+Similar wavelength coverage can be achieved in just 3 different transits or $\sim$33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
 \end{figure}
 
+\begin{figure*}[t]
+\centering
+\begin{subfigure}{0.48\textwidth}
+	\includegraphics[width=1\textwidth]{HD209458b_solar_clear_1trans_corner.png}
+	\caption{HD209458b}
+	\label{fig:corner209}
+\end{subfigure}
+\begin{subfigure}{0.48\textwidth}
+	\includegraphics[width=1\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
+	\caption{HAT-P-12b}
+	\label{fig:cornerHATp12}
+\end{subfigure}
+	\caption{Posterior distributions for MCMC runs of HD209458b and HAT-P-12b with the DHS (blue) and without the DHS (green).
+The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.
+Abundances are given in $\log_{10}$~(ppm).
+Cloud pressure is in $\log_{10}$~(bar).}
+	\label{fig:corner}
+\end{figure*}
+
 We use CHIMERA and a Markov Chain Monte Carlo (MCMC) retrieval to recover the individual atmospheric abundances of the simulated spectrum.
-The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile 2) the altitude of the 10-bar pressure surface where the model begins 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths 4) through 11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively 12) an amplitude of a Raleigh-like haze and 13) a power law index for the Raleigh-type haze.
+The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile; 2) the altitude of the 10-bar pressure surface where the model begins; 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths; 4) through 11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively; 12) an amplitude of a Raleigh-like haze; and 13) a power law index for the Raleigh-type haze.
 We assume flat priors in log space for all abundances from volume mixing ratios of 10$^{-12}$ to 1.
@@
 
-The posterior distributions for retrieved parameters for the most important abundances are shown in Figures \ref{fig:corner209} and \ref{fig:cornerHATp12}.
+The posterior distributions for retrieved parameters for the most important abundances are shown in Figure~\ref{fig:corner}.
 We show the posterior distributions for two cases:
 \begin{enumerate}
-\item \label{it:DHSgr} An observation with the long wavelength grisms alone (2.4$\mu$m to 5.0$\mu$m), shown in green.
-\item \label{it:grAlone} An observation with the long wavelength grisms (2.44$\mu$m to 5.0$\mu$m) with simultaneous DHS spectra (1.0-2.0$\mu$m), shown in blue
+\item \label{it:DHSgr} An observation with the long wavelength grisms alone (2.4-5.0$\mu$m), shown in green.
+\item \label{it:grAlone} An observation with the long wavelength grisms (2.4-5.0$\mu$m) with simultaneous DHS spectra (1.0-2.0$\mu$m), shown in blue.
 \end{enumerate}
@@
 
-The posterior distributions for HD 209458b in Figure \ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used with the long wavelength grisms (Case \ref{it:DHSgr}) as compared to the long wavelength grisms alone (Case \ref{it:grAlone}).
+The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used with the long wavelength grisms (Case~\ref{it:DHSgr}) as compared to the long wavelength grisms alone (Case~\ref{it:grAlone}).
 These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.
 
-\begin{figure*}
-\centering
-\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
-\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) and without the DHS (green).
-The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.
+%\begin{figure*}
+%\centering
+%\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
+%\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) and without the DHS (green).
+%The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.
 Abundances are given in Log$_{10}$(ppm).
 Cloud pressure is in Log$_{10}$(bar).}\label{fig:corner209}
-\end{figure*}
+%\end{figure*}
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=1.0\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
-\caption{Posterior distributions an MCMC retrieval of parameters for HAT-P-12b with the DHS (blue) and without the DHS (gray).}\label{fig:cornerHATp12}
-\end{figure*}
+%\begin{figure*}
+%\centering
+%\includegraphics[width=1.0\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
+%\caption{Posterior distributions an MCMC retrieval of parameters for HAT-P-12b with the DHS (blue) and without the DHS (gray).}\label{fig:cornerHATp12}
+%\end{figure*}
 
@@
 Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.
+
+\begin{table*}[!t]
+\centering
+\begin{tabular}{lcc}
+\hline \hline
+ & DHS & Grism \\
+\hline \hline		
+Resolution: &  \DHSres & 1200 - 1550 \\
+Dispersion: & 0.29 nm / px & 1.0 nm / px \\
+Wavelengths: & 1.05 - 2.00$\mu$m (F150W2)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
+			 & 1.75 - 2.23$\mu$m (F200W)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
+			& 	1.01 - 1.94$\mu$m (F150W2) \footnote{For a field point matched to the F444W filter and long wavelength grism.
+There is a \DHSgap$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
+Plate Scale: & 32 mas / px  &  65 mas / px\\
+Undeviated Wavelength: & 1.36$\mu$m & 3.94$\mu$m   \\
+\hline
+\end{tabular}
+\caption{Properties of DHS and simultaneous long-wavelength grism spectra. The parameters are for the A-side grism in the direction aligned with detector rows (R).}\label{tab:DHSgprop}
+\vspace{0.1in}
+\end{table*}
 
@@
 The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
-If the region from 2-2.23 $\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength arms.
+If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength arms.
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{dhs_res.pdf}
+\includegraphics[width=1.0\columnwidth]{dhs_res.pdf}
 \caption{Resolution as a function of wavelength for the DHS.}\label{fig:DHSRes}
@@
 
-\begin{table}
+\subsection{DHS Layout}
+
+\begin{figure}[b]
 \centering
-\begin{tabular}{ccr}
-		& DHS	& Grism \\
- \hline \hline		
-Resolution &  \DHSres & 1200 - 1550 \\
-Dispersion & 0.29 nm / px & 1.0 nm / px \\
-Wavelengths & 1.05 - 2.00$\mu$m (F150W2)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
-			 & 1.75 - 2.23$\mu$m (F200W)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
-			& 	1.01 - 1.94$\mu$m (F150W2) \footnote{For a field point matched to the F444W filter and long wavelength grism.
-There is a \DHSgap$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
-Plate Scale & 32 mas/px  &  65 mas / px\\
-Undeviated \\Wavelength & 1.36 $\mu$m & 3.94 $\mu$m   \\
-\hline
-\end{tabular}
-\caption{Properties of DHS and simultaneous long-wavelength grism spectra. The parameters are for the A-side grism in the direction aligned with detector rows (R).}\label{tab:DHSgprop}
-\vspace{0.1in}
-\end{table}
+\includegraphics[width=1.0\columnwidth]{dhs_pupil_labels_modA.pdf}
+\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}. 
+The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted "Y" shaped feature).
+The pupil wheel is clocked to make the DHS spectra straight along rows.
+This moves the DHS elements off-center from JWST's pupil and thus decreases the throughput for elements 1 and 6, but the overall combined throughput for all 10 elements is only reduced from 32\% to 29\%.}\label{fig:DHSvsPupilOverlay}
+\end{figure}
 
-\subsection{DHS Layout}
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{grism_pos_for_max_wcoverage.pdf}
+\caption{DHS wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source.
+The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.
+The circles plotted for each grism are the shortest usable wavelength, undispersed wavelength and longest usable wavelength.}\label{fig:DHSwaveWGrism}
+\end{figure*}
 
@@
 Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum where 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
-For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure \ref{fig:DHSvsPupilOverlay}.
+For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure~\ref{fig:DHSvsPupilOverlay}.
 
-\begin{figure}
-\centering
-\includegraphics[width=0.49\textwidth]{grism_pos_for_max_wcoverage.pdf}
-\caption{DHS Wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source.
-The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.
-The circles plotted for each grism are the shortest usable wavelength, undispersed wavelength and longest usable wavelength.}\label{fig:DHSwaveWGrism}
-\end{figure}
-
-%The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs.
-%The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m.
-%If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
-
-\begin{table}
+\begin{table}[!ht]
 \centering
 \begin{tabular}{cc}
+\hline \hline
 DHS \# & Pupil Fraction \\
@@
 \hline
-Total & 0.292
+Total & 0.292\\
+\hline
 \end{tabular}
-\caption{Pupil Coverage}\label{tab:pupfrac}
-\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}
+\caption{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area}
+\label{tab:pupfrac}
+%\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}
 \end{table}
 
-\begin{figure}
-\centering
-\includegraphics[width=0.49\textwidth]{dhs_pupil_labels_modA.pdf}
-\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}. 
-The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted "Y" shaped feature).
-The pupil wheel is clocked to make the DHS spectra straight along rows.
-This moves the DHS elements off-center from JWST's pupil and thus decreases the throughput for elements 1 and 6, but the overall combined throughput for all 10 elements is only reduced from 32\% to 29\%.}\label{fig:DHSvsPupilOverlay}
-\end{figure}
+%The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs.
+%The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m.
+%If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
 
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
-\includegraphics[width=0.49\textwidth]{readout_schematic.pdf}
+\includegraphics[width=1.0\columnwidth]{readout_schematic.pdf}
 \caption{Schematic of example readout modes for an exposure that is 12 frame times in duration.
@@
 
-\begin{figure}[!ht]
-\includegraphics[width=0.49\textwidth]{example_ap_sizes.pdf}
+\begin{figure}[!t]
+\includegraphics[width=1.0\columnwidth]{example_ap_sizes.pdf}
 \caption{Example DHS image on the A1 short wavelength detector taken during cryogenic vacuum testing of the flight hardware -- see Figure \ref{fig:DHSwaveWGrism} for the detector's position.
@@
 
-\begin{table}
+\begin{table}[!hb]
 \centering
 \begin{tabular}{llll}
+\hline \hline
 Sub-Array Size &  LW Saturation & \# of DHS & DHS Noise\\
@@
 2048$\times$ 256 & 6.01 & 2 &  ?? \\
-2048$\times$ 2048 & 8.26 & 10 & ??
+2048$\times$ 2048 & 8.26 & 10 & ?? \\
+\hline
 \end{tabular}
@@
 
-\begin{figure}[!ht]
-\includegraphics[width=0.49\textwidth]{NIRCam_grism_max_exp.pdf}
+\begin{figure}[!t]
+\includegraphics[width=1.0\columnwidth]{NIRCam_grism_max_exp.pdf}
 \caption{The maximum time JWST NIRCam can expose three detectors (e.g.
@@
 
-\section{Acknowledgements}
+\section*{Acknowledgements}
+%\acknowledgments
 
@@
 
-\acknowledgments
+%\acknowledgments
 

### 2016-08-07 ms.tex
I tried to do a subfloat to do the same thing as subfigure but it didn't work very well.
I changed from the subfigure method of showing the corner plots (which generated compilation issues) to subfloat.
I added info on the efficiency and throughput of the DHS.

@@
 \usepackage{graphicx}
+\usepackage{float}
 %\usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{subcaption}
+\usepackage[caption=false]{subfig}
 
@@
 \centering
-\begin{subfigure}{0.48\textwidth}
-	\includegraphics[width=1\textwidth]{HD209458b_solar_clear_1trans_corner.png}
-	\caption{HD209458b}
+\subfloat[HD 209458b]{
+	\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_1trans_corner.png}
+	%\caption{HD209458b}
 	\label{fig:corner209}
-\end{subfigure}
-\begin{subfigure}{0.48\textwidth}
-	\includegraphics[width=1\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
-	\caption{HAT-P-12b}
+	}
+\subfloat[HAT-P-12b]{
+	\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
+	%\caption{HAT-P-12b}
 	\label{fig:cornerHATp12}
-\end{subfigure}
+	}
 	\caption{Posterior distributions for MCMC runs of HD209458b and HAT-P-12b with the DHS (blue) and without the DHS (green).
@@
 \centering
-\includegraphics[width=1.0\textwidth]{grism_pos_for_max_wcoverage.pdf}
+\includegraphics[width=0.7\textwidth]{grism_pos_for_max_wcoverage.pdf}
 \caption{DHS wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source.
@@
 Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
+
 Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure \ref{fig:DHSvsPupilOverlay}.
@@
 Fortunately, the relative obscuration for all 10 DHS spectra is small, going from 32\% total throughput when the pupil wheel is centered (which produces tilted spectra), versus 29\% if the pupil wheel is clocked to align the spectra along rows.
-Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum where 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
+
+The throughput for DHS spectroscopy is the multiple of the DHS grating efficiency, telescope and instrument throughput for a given filter (both shown in Figure \ref{fig:DHSthrough}) and the pupil coverage by the DHS elements listed in Table \ref{tab:pupfrac}.
+A fractional pupil 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
 For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure~\ref{fig:DHSvsPupilOverlay}.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
+\caption{Throughput as a function of wavelength for the DHS grism and F150W2 filter that includes the telescope and instrument transmission.
+The total throughput is the multiple of the filter curve, ``DHS'' grism and the pupil area fraction from Table \ref{tab:pupfrac}..}\label{fig:DHSthrough}
+\end{figure}
 

### 2016-08-15 ms.tex
Tom updated the table of sensitivities with tradeoffs.

@@
 \centering
-\begin{tabular}{llll}
+\begin{tabular}{llrr}
 \hline \hline
@@
 \hline \hline
-2048$\times$ 64 & 4.52 & 1 &  ?? \\
-2048$\times$ 128 & 5.26 & 1 &  ?? \\
-2048$\times$ 256 & 6.01 & 2 &  ?? \\
-2048$\times$ 2048 & 8.26 & 10 & ?? \\
+2048$\times$ 64 & 4.52 & 1 &  72 -- 110 \\
+2048$\times$ 128 & 5.26 & 1 &  100 -- 160 \\
+2048$\times$ 256 & 6.01 & 2 &  100 -- 160 \\
+2048$\times$ 2048 & 8.26 & 10 & 160 -- 270 \\
 \hline
@@
 \caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes.
-The size affects the number of DHS that can be included, so the SNR at 1.5$\mu$m in the DHS spectrum at the given saturation limit for a 1 hour transit is shown in column 4.}\label{tab:SatSNRsubA}
+The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4.}\label{tab:SatSNRsubA}
 \end{table}

### 2016-08-16 ms.tex
I replaced NIRCam arms with NIRCam channels and a short list of specific recommendations.

@@
 
-\title{Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor}
+\title{Two NIRCam channels are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor}
 
@@
 The NIRCam instrument was primarily designed as an imager, but includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments.
-NIRCam's long-wavelength arm includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R = 1200 - 1550$ and it has already been approved for wide field slitless spectroscopy.
-We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength arm.
+NIRCam's long-wavelength channel includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R = 1200 - 1550$ and it has already been approved for wide field slitless spectroscopy.
+We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength channel.
 This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spatially separated spectra per source source at $R \sim \DHSresApprox$.
@@
 The DHS essentially comes for free with any NIRCam long-wavelength grism observation, but the readout has to be selected to ensure that the long-wavelength grism observations do not saturate and that the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
-Combining both of NIRCam's arms will maximize the science potential of JWST, which is a limited life observatory.
+Combining both of NIRCam's channels will maximize the science potential of JWST, which is a limited life observatory.
 \end{abstract}
@@
 Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
-For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7$\mu$m to 2.5$\mu$m), two with NIRCam's long-wavelength arm (2.44$\mu$m to 4.98$\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7~$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
+For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7$\mu$m to 2.5$\mu$m), two with NIRCam's long-wavelength channel (2.44$\mu$m to 4.98$\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7~$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
 With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours.
@@
 The NIRCam instrument is primarily an imager, but it includes several spectroscopic modes originally designed for wavefront sensing.
-These include the grisms installed in its long-wavelength arm as well as the Dispersed Hartmann Sensors (DHSs) installed in its short-wavelength arm.
+These include the grisms installed in its long-wavelength channel as well as the Dispersed Hartmann Sensors (DHSs) installed in its short-wavelength channel.
 The long-wavelength grisms are used in concert with broadband filters.
@@
 \caption{Model spectra separated by molecule for HD 209458b.
-The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength arm.
+The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel.
 The simulated data are for one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
@@
 The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5$\mu$m.
-This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength arm and long-wavelength arm, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
+This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength channel and long-wavelength channel, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
 In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
@@
 Since the DHS was not originally designed for science observations, it is not yet an approved mode for the James Webb Space Telescope.
-In this white paper, we argue for the inclusion of the DHS mode to fully take advantage of two NIRCam arms to maximize JWST's science potential for transiting planets.
+In this white paper, we argue for the inclusion of the DHS mode to fully take advantage of two NIRCam channels to maximize JWST's science potential for transiting planets.
 In section \ref{sec:addedScience} we discuss the added science that can be achieved with the DHS, including the brightness limits and improved precision in retrieved parameters for a representative system.
@@
 \subsection{DHS properties}
-The DHS expands the wavelength range that NIRCam can achieve on a single observation by simultaneously obtaining spectroscopy with NIRCam's short wavelength arm and long wavelength arm.
-The maximum wavelength range for the F150W2 filter in the short wavelength arm is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
+The DHS expands the wavelength range that NIRCam can achieve on a single observation by simultaneously obtaining spectroscopy with NIRCam's short wavelength channel and long wavelength channel.
+The maximum wavelength range for the F150W2 filter in the short wavelength channel is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
 The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width in the dispersion direction.
@@
 The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
-If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength arms.
+If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels.
 
@@
 \includegraphics[width=0.7\textwidth]{grism_pos_for_max_wcoverage.pdf}
-\caption{DHS wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source.
+\caption{DHS wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength channel for the same input source.
 The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.
@@
 
-A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength arm and one spectrum on the long-wavelength arm -- see Figure \ref{fig:DHSwaveWGrism}.
+A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure \ref{fig:DHSwaveWGrism}.
 The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
@@
 %\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
-%\caption{Example images of the same source observed simultaneously with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right).
+%\caption{Example images of the same source observed simultaneously with the DHS on the short-wavelength channel (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength channel (right).
 %These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard.
@@
 We encourage the implementation and approval of the DHS mode to enable this additional science in less time for this limited life observatory.
+
+\subsubsection{Specific Changes Needed for Implementation}
+We summarize the specific changes to the existing operations needed for the DHS here:
+\begin{enumerate}
+\item Allow the NIRCam pupil wheel to be used for science at the DHS element position with spectra parallel with detector rows
+\item Allow subarray locations to be different for the short wavelength arrays and the long wavelength arrays in order to capture the spectrum for Element numbers 7 and 8 for subarrays
+\item Choose field points from NIRCam's long wavelength grism to allow simultaneous DHS spectroscopy with all 10 DHS elements
+\item Change the OSS software and timing so that large subarrays may used with the DHS simultaneously with small 2048$\times$64 subarrays with the long wavelength grisms
+\end{enumerate}
 

### 2016-08-16 ms.tex
I added Tom's suggestions for sections 1 and 2.

@@
 \newcommand{\DHSgap}{0.04}
+
+\newcommand{\SOSSrange}{0.6 to 2.5 $\mu$m}
 
@@
 The NIRCam instrument was primarily designed as an imager, but includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments.
-NIRCam's long-wavelength channel includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R = 1200 - 1550$ and it has already been approved for wide field slitless spectroscopy.
+NIRCam's long-wavelength channel includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R = 1200 - 1550$ and it has already been approved for wide field and single object (time series) slitless spectroscopy.
 We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength channel.
@@
 We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres.
-The DHS essentially comes for free with any NIRCam long-wavelength grism observation, but the readout has to be selected to ensure that the long-wavelength grism observations do not saturate and that the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
+The DHS essentially comes for free with any NIRCam long-wavelength grism observation, but the detector integration parameters have to be selected to ensure that the long-wavelength grism observations do not saturate and that the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
 Combining both of NIRCam's channels will maximize the science potential of JWST, which is a limited life observatory.
@@
 No single JWST instrument may measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum.
-The largest bandwidths possible are NIRSpec's low resolution prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m.
+The largest bandwidths possible are NIRSpec's low resolution double prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m.
 Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
-For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7$\mu$m to 2.5$\mu$m), two with NIRCam's long-wavelength channel (2.44$\mu$m to 4.98$\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7~$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
+For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (\SOSSrange), two with NIRCam's long-wavelength channel (2.44$\mu$m to 4.98$\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7~$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
 With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours.
@@
 
-The NIRCam instrument is primarily an imager, but it includes several spectroscopic modes originally designed for wavefront sensing.
+The NIRCam instrument is primarily an imager, but it includes several spectroscopic modes originally designed for observatory wavefront sensing.
 These include the grisms installed in its long-wavelength channel as well as the Dispersed Hartmann Sensors (DHSs) installed in its short-wavelength channel.
@@
 This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength channel and long-wavelength channel, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
-In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
+In principle, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
 Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
 For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0$\mu$m to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
-The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.
+The DHS is expected to collect similar photon levels as HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.
 
 Since the DHS was not originally designed for science observations, it is not yet an approved mode for the James Webb Space Telescope.
-In this white paper, we argue for the inclusion of the DHS mode to fully take advantage of two NIRCam channels to maximize JWST's science potential for transiting planets.
+In this white paper, we explain the value of the DHS mode to fully take advantage of two NIRCam channels to maximize JWST's science potential for transiting planets as well as discuss the specifics of its implementation.
 In section \ref{sec:addedScience} we discuss the added science that can be achieved with the DHS, including the brightness limits and improved precision in retrieved parameters for a representative system.
@@
 
+\subsubsection{Simulated Observations and Retrieval Methods}
 For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
 We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
+In other words, there is one DHS measurement per grism filter (F444W and F322W2).
 This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra.
-The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the detector noise floor (35 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
-The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from 0.7 to 2.4$\mu$m can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
+The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
+The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrange\ can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
 

### 2016-08-16 ms.tex
I incorporated Tom's Section 3 suggestions.

@@
 The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
-If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels.
+If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels, though the grism blaze function drops off above 2.0$\mu$m, shown in Section \ref{sec:layout}.
 
@@
 
-\subsection{DHS Layout}
+\subsection{DHS Layout}\label{sec:layout}
 
@@
 \includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
-\caption{Throughput as a function of wavelength for the DHS grism and F150W2 filter that includes the telescope and instrument transmission.
+\caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission.
 The total throughput is the multiple of the filter curve, ``DHS'' grism and the pupil area fraction from Table \ref{tab:pupfrac}..}\label{fig:DHSthrough}
@@
 \hline
+\\
+\multicolumn{2}{c}{\textbf{DHS Pupil Coverage} }
 \end{tabular}
-\caption{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area}
+\caption{The pupil coverage of the 10 DHS grisms compared to the total primary collecting area for the pupil wheel position that aligns DHS spectra with detector rows.}
 \label{tab:pupfrac}
@@
 No reset frames or dropped frames are saved.``1 Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
-The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but will saturate more easily.}\label{fig:readout}
+The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but has a longer minimum integration time, resulting in fainter saturation limits.}\label{fig:readout}
 \end{figure}
@@
 The balance between saturating the long-wavelength grism and getting enough SNR in the DHS is listed in Table \ref{tab:SatSNRsubA}.
-The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the DHS noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration and binned to a resolution of 100.
+The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the DHS noise at 1.1 to 1.9 $\mu$m for a G2V type star at this brightness observing a 1 hour long transit and 1 hour on a star out of transit, binned to the native resolution of R $\sim$ \DHSresApprox.
 We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} and we consider 80\% well depth in the second read as saturation.
@@
 \caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes.
-The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4.}\label{tab:SatSNRsubA}
+The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}\label{tab:SatSNRsubA}
 \end{table}
@@
 This only works for sources faint enough that the long-wavelength grisms do not saturate.
+Perhaps future changes to the OSS could allow operating the LW detectors with 4 outputs and the SW ones with 1 output, reducing data volume considerably.
 

### 2016-08-17 ms.tex
Karl's Changes to wording.

@@
 Taking full advantage of JWST spectroscopy of planets from 0.6 $\mu$m to 28$\mu$m, however, will require many observations with a combination of the NIRISS, NIRCam, NIRSpec and MIRI instruments.
-In this white paper, we discuss a new NIRCam mode (not yet approved and implemented) that can reduce the number of observations needed for observations in the 1.0$\mu$m to 5.0$\mu$m wavelength range.
+In this white paper, we discuss a new NIRCam mode (not yet approved or implemented) that can reduce the number of observations needed to cover the 1.0$\mu$m to 5.0$\mu$m wavelength range.
 The NIRCam instrument was primarily designed as an imager, but includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments.
-NIRCam's long-wavelength channel includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R = 1200 - 1550$ and it has already been approved for wide field and single object (time series) slitless spectroscopy.
+NIRCam's long-wavelength channel includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with a resolution of $R = 1200 - 1550$ using two separate configurations.
+The long-wavelength grisms have already been approved for wide field and single object (time series) slitless spectroscopy in science operations.
 We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength channel.
 This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spatially separated spectra per source source at $R \sim \DHSresApprox$.
-The DHS can observe the brightest host stars of any JWST mode.
+%% The DHS can observe the brightest host stars of any JWST mode. [WITHOUT EXPLANATION OF MODES AND NO CONTEXT, THIS WAS A BIT JARRING WHEN I READ IT - FEEL FREE TO ADD IT BACK IN! -KAM]
 We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres.
-The DHS essentially comes for free with any NIRCam long-wavelength grism observation, but the detector integration parameters have to be selected to ensure that the long-wavelength grism observations do not saturate and that the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
+The DHS essentially comes for free with any NIRCam long-wavelength grism observation, but the detector integration parameters have to be selected to ensure that the long-wavelength grism observations do not saturate and that JWST data volume downlink constraints are not violated.
+%the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
 Combining both of NIRCam's channels will maximize the science potential of JWST, which is a limited life observatory.
@@
 The wavelength coverage from 0.6$\mu$m to 28$\mu$m adds significantly to the wavelengths covered by the Hubble Space Telescope (HST) (currently 0.09$\mu$m to 1.7$\mu$m).
-Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent observatory for characterizing the atmospheres of planets that transit their host stars with time series observations.
+Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent platform for time series observations to characterize the atmospheres of planets that transit their host stars.
 Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
@@
 
-No single JWST instrument may measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum.
+No single JWST instrument can measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum.
 The largest bandwidths possible are NIRSpec's low resolution double prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m.
-Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
-For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (\SOSSrange), two with NIRCam's long-wavelength channel (2.44$\mu$m to 4.98$\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7~$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
-With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours.
-This was calculated with the Astronomer's Proposal Tools software\footnote{http://www.stsci.edu/hst/proposing/apt} with the NIRISS SOSS mode, NIRCam's F322W2 and F444W grism time series and the MIRI Low Resolution spectrograph (LRS).
+Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planetary systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
+For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (SOSS, \SOSSrange), two with NIRCam's long-wavelength channel (F322W2 and F444W + grisms, 2.44$\mu$m to 4.98$\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7~$\mu$ to 5.0$\mu$m.} and one with MIRI (LRS, 5$\mu$m to 12$\mu$m).
+Using the Astronomer's Proposal Tool software\footnote{http://www.stsci.edu/hst/proposing/apt}, each transit observation (pre-ingress, transit, and post-ingress) requires $\sim$9 hr and incurs overheads of $\sim$2 hr, resulting in a total of $\sim$11 hours per transit and hence $\sim$44 hours total to cover
+the full wavelength range.
 
@@
 The long-wavelength grisms are used in concert with broadband filters.
-The F322W2 filter encompasses 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter encompasses 3.88$\mu$m to 4.98$\mu$m at half maximum throughput.
+The F322W2 filter covers 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter covers 3.88$\mu$m to 4.98$\mu$m at half maximum throughput.
 These filters and grism are enabled and supported JWST science modes.
 The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput.
-The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the first order of the spectrum begins to overlap at at 2.0$\mu$m.\footnote{The prism that spatially separate the 10 DHS spectra separate the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
+The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the first order of the spectrum begins to overlap at 2.0$\mu$m.\footnote{The prism that spatially separate the 10 DHS spectra separate the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
 
@@
 
-The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5$\mu$m.
+The NIRCam instrument can reduce the number of transits needed to build up a 1$\mu$m to 5$\mu$m transmission or emission spectrum of a planet.
 This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength channel and long-wavelength channel, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
@@
 Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
-For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0$\mu$m to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
+%% Changed this to not read 11 hours per TRANSIT, but 11 hours per PLANET - i.e. removes 1 single transit from the run to get the same coverage
+For the example above of HD 209458b, simultaneous DHS data would reduce the required transits from four to three, saving about 11 JWST hours 
+if the wavelengths from 2.0$\mu$m to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
 The DHS is expected to collect similar photon levels as HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.
 
-Since the DHS was not originally designed for science observations, it is not yet an approved mode for the James Webb Space Telescope.
+Since the DHS was not originally designed for science observations, it is not yet an approved mode for the James Webb Space Telescope science operations.
 In this white paper, we explain the value of the DHS mode to fully take advantage of two NIRCam channels to maximize JWST's science potential for transiting planets as well as discuss the specifics of its implementation.
@@
 
-The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST.
+The DHS has the best [** Is 'best' the best word here? Highest? Lowest? **] brightness limits of any spectroscopic mode on JWST because it
+spreads light over many pixels and reduces the effective aperture of JWST.
 Figure \ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
 Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
-The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
+%The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
 
@@
 We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
-In other words, there is one DHS measurement per grism filter (F444W and F322W2).
-This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra.
+%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
+This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
 The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
@@
 
-We use CHIMERA and a Markov Chain Monte Carlo (MCMC) retrieval to recover the individual atmospheric abundances of the simulated spectrum.
+We use CHIMERA and a MCMC retrieval to recover the individual atmospheric abundances of the simulated spectrum.
 The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile; 2) the altitude of the 10-bar pressure surface where the model begins; 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths; 4) through 11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively; 12) an amplitude of a Raleigh-like haze; and 13) a power law index for the Raleigh-type haze.

### 2016-08-17 ms.tex
I incorporated Mike Line's updates to the modeling section.

@@
 
-We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to show the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
+We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to illustrate the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
 We first simulate a forward model of a transmission spectrum for two planets, HD 209458b and HAT-P-12b.
@@
 Finally, we run a Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
-We combine the individual gases' posterior distributions for the C/O ratio and metallicity.
+We combine the individual gases' posterior distributions to derive the C/O ratio and metallicity (\citet{greene2016jwst_trans}) .
 
@@
 
-For the initial model of HD 209458b, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the settling out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}.
-For HAT-P-12b, we scale the atomic abundances of all elements except Hydrogen and Helium by a factor of 22 using the mass-metallicity relation of \citep{kreidberg2014wasp43} and \citep{line2016hd209wfc3}.
-The atomic abundances are converted to molecular mixing ratios using the Chemical Equilibrium code with Applications (CEA)\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} to calculate the fractions of molecules at the given pressure and temperature.
-For HD209458b and HAT-P-12b, this is at a reference pressure of 0.01 bars and a reference temperature of 1440K and 960 K respectively.
-We assume that the abundances and temperature are constant with altitude.
-We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as sources of opacity, but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
-For the HAT-P-12b model, we include an opaque cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
-For HD 209458b, this cloud deck is placed at a pressure level of 1 bar which is too low in altitude to affect the spectrum, as shown in Figure \ref{fig:209spec}.
+%For the underlying ``true" model of HD 209458b, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}.
+%For HAT-P-12b, we scale the atomic abundances of all elements except Hydrogen and Helium by a factor of 22 using the mass-metallicity relation of \citep{kreidberg2014wasp43} and \citep{line2016hd209wfc3}.
+%The atomic abundances are converted to molecular mixing ratios using the Chemical Equilibrium code with Applications (CEA)\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} to calculate the fractions of molecules at the given pressure and temperature.
+
+To construct the model atmospheres and generate a spectrum we require a thermal profile and molecular abundances.
+For simplicity, we assume isothermal atmospheres at the planetary equilibrium temperatures.
+Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code \footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea}) at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances (Asphlund reference).
+
+For HD209458b and HAT-P-12b we assume isothermal temperature's of 1440K and 960 K respectively.
+Molecular abundances are assumed constant with altitude at the 0.01 bar thermochemical values.
+While this ``0D" model is likely unrealistic, more sophisticated 1D models in general may be unrealistic given the uncertainties due to the impact of 3-dimensional effects (e.g., Line \& Parmentier 2016; Feng et al.
+2016).
+We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as the sources of opacity (with absorption cross-section derived from Freedman et al.
+2014 and references therein), but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
+For the HAT-P-12b model, we include an opaque gray cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
+For HD 209458b, this cloud deck is placed at a pressure level of 1 bar which is too deep to affect the spectrum, as shown in Figure \ref{fig:209spec}.
 % if we run the simulations later, also mention emission spectra
@@
 
-We use CHIMERA and a MCMC retrieval to recover the individual atmospheric abundances of the simulated spectrum.
-The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile; 2) the altitude of the 10-bar pressure surface where the model begins; 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths; 4) through 11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively; 12) an amplitude of a Raleigh-like haze; and 13) a power law index for the Raleigh-type haze.
-We assume flat priors in log space for all abundances from volume mixing ratios of 10$^{-12}$ to 1.
-The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 to allow for burn-in.
+We use the \tt{emcee} version of CHIMERA (Greene et al.
+2016) to recover the individual atmospheric abundances of the simulated spectrum.
+The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile; 2) the altitude of the 10-bar pressure surface where the model begins; 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths; 4) through 11) the constant-with-altitude mixing ratios of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively; 12) an amplitude of a Raleigh-like haze; and 13) a power law index for the Raleigh-type haze.
+We assume uniform-in-log priors from 10$^{-12}$ to 1 for all volume mixing ratios.
+The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 (times $\sim$100 walkers) to allow for burn-in.
 
@@
 
-\subsection{CHIMERA Retreivals}\label{sec:retrievals}
+\subsection{Parameter Estimation Rresults}\label{sec:retrievals}
 
@@
 The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
-If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels, though the grism blaze function drops off above 2.0$\mu$m, shown in Section \ref{sec:layout}.
+If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels, though the grism transmission is lower above 2.0$\mu$m, shown in Figure \ref{fig:DHSthrough}.
 

### 2016-08-17 ms.tex
Corrected some of Mike Line's edits - Everett
I removed the line about the software requirements that the subarray locations be identical.
I cleaned up Mike and Karls' changes as well as put in the citep reference.

@@
 This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spatially separated spectra per source source at $R \sim \DHSresApprox$.
-%% The DHS can observe the brightest host stars of any JWST mode. [WITHOUT EXPLANATION OF MODES AND NO CONTEXT, THIS WAS A BIT JARRING WHEN I READ IT - FEEL FREE TO ADD IT BACK IN! -KAM]
-We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres.
+We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres as well as its ability to observe the brightest systems.
 The DHS essentially comes for free with any NIRCam long-wavelength grism observation, but the detector integration parameters have to be selected to ensure that the long-wavelength grism observations do not saturate and that JWST data volume downlink constraints are not violated.
@@
 Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
-%% Changed this to not read 11 hours per TRANSIT, but 11 hours per PLANET - i.e. removes 1 single transit from the run to get the same coverage
 For the example above of HD 209458b, simultaneous DHS data would reduce the required transits from four to three, saving about 11 JWST hours 
@@
 
-The DHS has the best [** Is 'best' the best word here? Highest? Lowest? **] brightness limits of any spectroscopic mode on JWST because it
+The DHS has the brightest saturation limits of any spectroscopic mode on JWST because it
 spreads light over many pixels and reduces the effective aperture of JWST.
@@
 For simplicity, we assume isothermal atmospheres at the planetary equilibrium temperatures.
-Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code \footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea}) at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances (Asphlund reference).
+Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code \footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea}) at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
 
@@
 Molecular abundances are assumed constant with altitude at the 0.01 bar thermochemical values.
-While this ``0D" model is likely unrealistic, more sophisticated 1D models in general may be unrealistic given the uncertainties due to the impact of 3-dimensional effects (e.g., Line \& Parmentier 2016; Feng et al.
-2016).
-We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as the sources of opacity (with absorption cross-section derived from Freedman et al.
-2014 and references therein), but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
+While this ``0D" model is likely unrealistic, more sophisticated 1D models in general may be unrealistic given the uncertainties due to the impact of 3-dimensional effects \citep[e.g.][]{line2016nonUclouds,feng2016nonUniform}.
+We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as the sources of opacity (with absorption cross-section derived from \citet{freedman2014opacities} and references therein), but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
 For the HAT-P-12b model, we include an opaque gray cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
@@
 
-We use the \tt{emcee} version of CHIMERA (Greene et al.
-2016) to recover the individual atmospheric abundances of the simulated spectrum.
+We use the \texttt{emcee} version of CHIMERA \citep{greene2016jwst_trans} to recover the individual atmospheric abundances of the simulated spectrum.
 The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile; 2) the altitude of the 10-bar pressure surface where the model begins; 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths; 4) through 11) the constant-with-altitude mixing ratios of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively; 12) an amplitude of a Raleigh-like haze; and 13) a power law index for the Raleigh-type haze.
 We assume uniform-in-log priors from 10$^{-12}$ to 1 for all volume mixing ratios.
-The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 (times $\sim$100 walkers) to allow for burn-in.
+The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 (times 160 walkers) to allow for burn-in.
 
@@
 
-\subsection{Parameter Estimation Rresults}\label{sec:retrievals}
+\subsection{Parameter Estimation Results}\label{sec:retrievals}
 
@@
 This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
-The current software requires that the sub-array locations must be identical for NIRCam's short wavelength arrays and long wavelength arrays.
 We recommend  the sub-array locations to be adjustable so that the short wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long wavelength array can be centered on a single grism spectrum.

### 2016-08-17 ms.tex
I added a few more clarifications to the abundances section and put in references to HAT-P-12b and HD 209458b's discoveries.

@@
 We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to illustrate the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
-We first simulate a forward model of a transmission spectrum for two planets, HD 209458b and HAT-P-12b.
+We first simulate a forward model of a transmission spectrum for two planets, HD 209458b \citep{henry00,charbonneau00} and HAT-P-12b \citep{hartman2009hatp12}.
 We then add Gaussian noise using the SNR estimated on the target to create a simulated spectrum.
@@
 For simplicity, we assume isothermal atmospheres at the planetary equilibrium temperatures.
-Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code \footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea}) at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
+Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea}) at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
+For HD 209458b (0.7 M$_{Jup}$), we prescribe solar metallicity since it is close to one Jupiter mass.
+For HAT-P-12b (0.2 M$_{Jup}$), we prescribe a planet metallicity of 22 $\times$ solar using the relation from \citet{kreidberg2014wasp43}.
+In both cases, we reduce the oxygen volume mixing ratio to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}, but this only results in a $\sim$ 20\% change in Oxygen.
 
-For HD209458b and HAT-P-12b we assume isothermal temperature's of 1440K and 960 K respectively.
+We assume isothermal temperature's of 1440K and 960 K for for HD209458b and HAT-P-12b respectively.
 Molecular abundances are assumed constant with altitude at the 0.01 bar thermochemical values.

### 2016-08-17 ms.tex
Tiny word change to clarify the Silicate rainout change to the Oxygen abundance.

@@
 For HAT-P-12b (0.2 M$_{Jup}$), we prescribe a planet metallicity of 22 $\times$ solar using the relation from \citet{kreidberg2014wasp43}.
-In both cases, we reduce the oxygen volume mixing ratio to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}, but this only results in a $\sim$ 20\% change in Oxygen.
+In both cases, we reduce the oxygen volume mixing ratio to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}, but this only results in a $\sim$ 20\% change in the Oxygen abundance.
 

### 2016-08-18 ms.tex
Adjusted the figure locations and added space before the acknowledgement to fix up formatting.

@@
 \subsubsection{Simulated Observations and Retrieval Methods}
-For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
-We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
-%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
-This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
-The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
-The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrange\ can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
-
 \begin{figure}[t]
@@
 \end{figure*}
+
+For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
+We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
+%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
+This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
+The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
+The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrange\ can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
 
@@
 
-\subsubsection{Specific Changes Needed for Implementation}
+\subsection{Specific Changes Needed for Implementation}
 We summarize the specific changes to the existing operations needed for the DHS here:
@@
 
+\vspace{0.1in}
 \section*{Acknowledgements}

### 2016-08-22 ms.tex
I changed out the old saturation plot for a new one that shows all the known systems and simulated TESS targets with the DHS and grism brightness limits. Also started a section on spot monitoring.

@@
 \begin{figure}[!b]
-\includegraphics[width=1.0\columnwidth]{sat_limits.jpg}
-\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
-The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
-The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:saturationLim}
+\includegraphics[width=1.0\columnwidth]{brightness_scape.pdf}
+\caption{Saturation limits of the DHS mode (blue line), and long-wavelength grism's F322W2 filter (green line) and F444W filter (dark red line) as a function of effective temperature.
+The magnitudes are Vega $K_S$ magnitudes where 80\% of the well depth is filled in the standard CDS readout mode (described in Figure \ref{fig:readout}) for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
+The blue points are known transiting systems from \texttt{exoplanets.org} and the green points are simulated TESS planets \citep{sullivan2015tess}.}\label{fig:saturationLim}
 \end{figure}
@@
 Figure \ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
-Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
-%The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
+The saturation limits are found using \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
+Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
+The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
+We plot the expected yield of TESS \citep{sullivan2015tess} in Figure \ref{fig:saturationLim} and still none of these targets saturate the DHS.
+
+\subsection{Short Wavelength Monitoring of Starspots}
+The fact that the DHS can be operated simultaneously with long wavelength grism observations of transits means that one can monitor for star spots during a transit.
 
@@
 Thanks to Michael Bruck at the High Performance Computing center at the University of Arizona for assisting with setting up the CHIMERA runs to utilize the HPC hardware.
+This research has made use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at exoplanets.org.
 %If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

### 2016-08-22 ms.tex
I re-arranged some figures in an attempt to keep the figures closer to the text. Also, I fixed up the citation to pysynphot.

@@
 
-\begin{figure}[!b]
+\section{Science Benefits with the DHS}\label{sec:addedScience}
+
+\subsection{Brightness limits}\label{sec:brightness}
+
+\begin{figure}[!bhtp]
 \includegraphics[width=1.0\columnwidth]{brightness_scape.pdf}
@@
 
-\section{Science Benefits with the DHS}\label{sec:addedScience}
-
-\subsection{Brightness limits}\label{sec:brightness}
-
 The DHS has the brightest saturation limits of any spectroscopic mode on JWST because it
@@
 Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
+Figure \ref{fig:saturationLim} shows the known transiting systems from \texttt{exoplanets.org} \citep{han2014exopDorg}.
 The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
-We plot the expected yield of TESS \citep{sullivan2015tess} in Figure \ref{fig:saturationLim} and still none of these targets saturate the DHS.
+We plot the expected yield of TESS \citep{sullivan2015tess} in Figure \ref{fig:saturationLim} and none of the simulated targets saturate the DHS.
 
-\subsection{Short Wavelength Monitoring of Starspots}
-The fact that the DHS can be operated simultaneously with long wavelength grism observations of transits means that one can monitor for star spots during a transit.
+%\subsection{Short Wavelength Monitoring of Starspots}
+%The fact that the DHS can be operated simultaneously with long wavelength grism observations of transits means that one can monitor for star spots during a transit.
 
 \subsection{CHIMERA Models}\label{sec:models}
+
+\begin{figure}[!tbhp]
+\centering
+\includegraphics[width=1.0\columnwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
+\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
+Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
+A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
+\end{figure}
 
@@
 We combine the individual gases' posterior distributions to derive the C/O ratio and metallicity (\citet{greene2016jwst_trans}) .
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=1.0\columnwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
-\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
-Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
-A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
-\end{figure}
 
@@
 
+\begin{figure}[!tbhp]
+\centering
+\includegraphics[width=1.0\columnwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
+\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
+Similar wavelength coverage can be achieved in just 3 different transits or $\sim$33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
+\end{figure}
+
 We assume isothermal temperature's of 1440K and 960 K for for HD209458b and HAT-P-12b respectively.
@@
 \subsubsection{Simulated Observations and Retrieval Methods}
-\begin{figure}[t]
-\centering
-\includegraphics[width=1.0\columnwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
-\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
-Similar wavelength coverage can be achieved in just 3 different transits or $\sim$33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
-\end{figure}
 
-\begin{figure*}[t]
+For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
+We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
+%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
+This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
+The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
+The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrange\ can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
+
+\begin{figure*}[!bthp]
 \centering
@@
 \end{figure*}
-
-For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
-We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
-%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
-This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
-The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
-The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrange\ can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
 

### 2016-08-22 ms.tex
I clarified the planet systems and stellar effective temperatures in the brightness limits section.

@@
 \includegraphics[width=1.0\columnwidth]{brightness_scape.pdf}
-\caption{Saturation limits of the DHS mode (blue line), and long-wavelength grism's F322W2 filter (green line) and F444W filter (dark red line) as a function of effective temperature.
+\caption{Saturation limits of the DHS mode (blue line), and long-wavelength grism's F322W2 filter (green line) and F444W filter (dark red line) as a function of stellar effective temperature.
 The magnitudes are Vega $K_S$ magnitudes where 80\% of the well depth is filled in the standard CDS readout mode (described in Figure \ref{fig:readout}) for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
@@
 The saturation limits are found using \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
-Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
+Any known transiting planet system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
 Figure \ref{fig:saturationLim} shows the known transiting systems from \texttt{exoplanets.org} \citep{han2014exopDorg}.

### 2016-08-23 ms.tex
inserted a 'the' before James Webb ST

@@
 
-In normal operations, science and telemetry data from James Webb Space Telescope are downlinked in a 4 hour contact time with an antenna in the Deep Space Network (SDN)  \citep{dashevsky2008groundflight}.
+In normal operations, science and telemetry data from the James Webb Space Telescope are downlinked in a 4 hour contact time with an antenna in the Deep Space Network (SDN)  \citep{dashevsky2008groundflight}.
 There will be two downlinks per day so on average the total data rate can no more than $\sim$458 Gbits per 12 hours.

### 2016-08-23 copy_to_mips.sh
I added a one-line script to copy to MIPS.

@@ -1,0 +1,1 @@
+scp ms.pdf schlawin@mips.as.arizona.edu:public_html/dhs_white_paper.pdf

### 2016-08-23 copy_to_mips.sh
I changed from scp to rsync -u in the MIPS update script.

@@ -1,1 +1,1 @@
-scp ms.pdf schlawin@mips.as.arizona.edu:public_html/dhs_white_paper.pdf
+rsync -uv ms.pdf schlawin@mips.as.arizona.edu:public_html/dhs_white_paper.pdf

### 2016-08-23 ms.tex
I incorporated Doug's fixes and clarifications.

@@
 We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres as well as its ability to observe the brightest systems.
-The DHS essentially comes for free with any NIRCam long-wavelength grism observation, but the detector integration parameters have to be selected to ensure that the long-wavelength grism observations do not saturate and that JWST data volume downlink constraints are not violated.
+The DHS essentially comes for free (at no time cost) with any NIRCam long-wavelength grism observation, but the detector integration parameters have to be selected to ensure that the long-wavelength grism observations do not saturate and that JWST data volume downlink constraints are not violated.
 %the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
@@
 Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
-JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to it host star.
+JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to its host star.
 Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes.
@@
 The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput.
-The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the first order of the spectrum begins to overlap at 2.0$\mu$m.\footnote{The prism that spatially separate the 10 DHS spectra separate the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
+The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the second order of the spectrum begins to overlap at 2.0$\mu$m.\footnote{The prism that spatially separate the 10 DHS spectra separate the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
 
@@
 
-The DHS has the brightest saturation limits of any spectroscopic mode on JWST because it
-spreads light over many pixels and reduces the effective aperture of JWST.
+The DHS has the brightest saturation limits of any spectroscopic mode on JWST because each of the 10 DHS elements samples only 1 to 4\% of the pupil and the light is dispersed over over two short wavelength detectors.
 Figure \ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
@@
 \includegraphics[width=1.0\columnwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
-\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
+\caption{Model spectra separated by molecule for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
 Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
@@
 
-Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure \ref{fig:DHSvsPupilOverlay}.
+Each DHS spectrum covers roughly 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure \ref{fig:DHSvsPupilOverlay}.
 We elected to clock the pupil wheel by 1.9$^\circ$ in order to align the spectra with rows on the short wavelength detector.

### 2016-08-24 ms.tex
I incorporated most of Lisa May's comments but need to still fix the figure ordering and ask about the one comment I couldn't understand.

@@
 The wavelength coverage from 0.6$\mu$m to 28$\mu$m adds significantly to the wavelengths covered by the Hubble Space Telescope (HST) (currently 0.09$\mu$m to 1.7$\mu$m).
-Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent platform for time series observations to characterize the atmospheres of planets that transit their host stars.
+Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent platform for time series observations to characterize the atmospheres of planets that transit their host stars \citep{beichman2014pasp,stevenson2016ers}.
 Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
@@
 The DHS can be used in tandem with either the F322W2 or F444W filter for the long wavelength grism observations.
-The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
+The properties of the DHS as compared to the grisms are listed in Table \ref{tab:DHSgprop}.
 If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels, though the grism transmission is lower above 2.0$\mu$m, shown in Figure \ref{fig:DHSthrough}.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
+\caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission.
+The total throughput is the multiple of the filter curve, ``DHS'' grism and the pupil area fraction from Table \ref{tab:pupfrac}..}\label{fig:DHSthrough}
+\end{figure}
 
@@
 
-\begin{figure*}
+A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure \ref{fig:DHSwaveWGrism}.
+The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
+The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
+Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
+
+\begin{figure*}[!hbtp]
 \centering
@@
 
-A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure \ref{fig:DHSwaveWGrism}.
-The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
-The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
-Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
-
 Each DHS spectrum covers roughly 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure \ref{fig:DHSvsPupilOverlay}.
-We elected to clock the pupil wheel by 1.9$^\circ$ in order to align the spectra with rows on the short wavelength detector.
+We elect to clock the pupil wheel by 1.9$^\circ$ in order to align the spectra with rows on the short wavelength detector.
 Aligning spectra along the rows enables small stripe mode readouts (such as 2048 $\times$ 64) to read one DHS spectra simultaneously with long wavelength grism spectra.
@@
 
-The throughput for DHS spectroscopy is the multiple of the DHS grating efficiency, telescope and instrument throughput for a given filter (both shown in Figure \ref{fig:DHSthrough}) and the pupil coverage by the DHS elements listed in Table \ref{tab:pupfrac}.
+The throughput for DHS spectroscopy is the product of the DHS grating efficiency, telescope and instrument throughput for a given filter (both shown in Figure \ref{fig:DHSthrough}) and the pupil coverage by the DHS elements listed in Table \ref{tab:pupfrac}.
 A fractional pupil 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
 For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure~\ref{fig:DHSvsPupilOverlay}.
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
-\caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission.
-The total throughput is the multiple of the filter curve, ``DHS'' grism and the pupil area fraction from Table \ref{tab:pupfrac}..}\label{fig:DHSthrough}
-\end{figure}
+We discuss only module A (of the two redundant modules A and B) because the long wavelength grisms are anti-reflective coated for module A.
 
@@
 We recommend  the sub-array locations to be adjustable so that the short wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long wavelength array can be centered on a single grism spectrum.
-The current time series observing templates is limited subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure \ref{fig:DHSaps}.
+The current time series observing templates is limited to subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure \ref{fig:DHSaps}.
 
@@
 In normal operations, science and telemetry data from the James Webb Space Telescope are downlinked in a 4 hour contact time with an antenna in the Deep Space Network (SDN)  \citep{dashevsky2008groundflight}.
-There will be two downlinks per day so on average the total data rate can no more than $\sim$458 Gbits per 12 hours.
+There will be two downlinks per day so on average the total data rate can be no more than $\sim$458 Gbits per 12 hours.
 Science operations can continue during the 4 hour contact time, but re-pointing the high gain antenna can cause $<$0.07 \arcsec\ disturbances \citep{beichman2014pasp}.
@@
 We introduced a new science mode using the Dispersed Hartmann Sensors on the NIRCam instrument which enable simultaneous measurements of spectra at R $\sim$ \DHSres\ from 1.0 to 2.0$\mu$m while using the NIRCam long-wavelength grisms covering either 2.4$\mu$m to 4.0$\mu$m or 3.9$\mu$m to 5.0$\mu$m.
+The fact that the two sets of grisms operate simultaneously allows more science to be done in the same amount of time.
 The readout mode and subarray size must be chosen carefully on the DHS so as to not saturate the long-wavelength grisms.

### 2016-08-24 ms.tex
I clarified the explanation of the gap between detectors.
Karl corrected a typo (where word was repeated).

@@
 We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength channel.
-This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spatially separated spectra per source source at $R \sim \DHSresApprox$.
+This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spatially separated spectra per source at $R \sim \DHSresApprox$.
 We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres as well as its ability to observe the brightest systems.
@@
 Figure \ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
-There will be about a \DHSgap$\mu$m gap in the spectrum due to the gap between short wavelength detectors.
+There is a spatial gap between short wavelength detectors which corresponds to about \DHSgap$\mu$m in wavelength.
 The center of this gap depends on source position.

### 2016-08-24 ms.tex
Jarron fixed up the ordering and placement of the figures. He also fixed up the figure references to they don't get split to multiple lines.

@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=1.0\columnwidth]{molecules_DHS_HD209.pdf}
-\caption{Model spectra separated by molecule for HD 209458b.
-The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel.
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=1.0\columnwidth]{molecules_DHS_HD209.pdf}
+%\caption{Model spectra separated by molecule for HD 209458b.
+%The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel.
 The simulated data are for one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
 The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:209spec}
-\end{figure}
+%\end{figure}
 
@@
 
-\begin{figure}[!bhtp]
+The DHS has the brightest saturation limits of any spectroscopic mode on JWST because each of the 10 DHS elements samples only 1 to 4\% of the pupil and the light is dispersed over over two short wavelength detectors.
+Figure~\ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
+The saturation limits are found using \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
+Any known transiting planet system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
+Figure~\ref{fig:saturationLim} shows the known transiting systems from \texttt{exoplanets.org} \citep{han2014exopDorg}.
+The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
+We plot the expected yield of TESS \citep{sullivan2015tess} in Figure~\ref{fig:saturationLim} and none of the simulated targets saturate the DHS.
+
+\begin{figure}[!h]
 \includegraphics[width=1.0\columnwidth]{brightness_scape.pdf}
 \caption{Saturation limits of the DHS mode (blue line), and long-wavelength grism's F322W2 filter (green line) and F444W filter (dark red line) as a function of stellar effective temperature.
-The magnitudes are Vega $K_S$ magnitudes where 80\% of the well depth is filled in the standard CDS readout mode (described in Figure \ref{fig:readout}) for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
+The magnitudes are Vega $K_S$ magnitudes where 80\% of the well depth is filled in the standard CDS readout mode (described in Figure~\ref{fig:readout}) for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
 The blue points are known transiting systems from \texttt{exoplanets.org} and the green points are simulated TESS planets \citep{sullivan2015tess}.}\label{fig:saturationLim}
 \end{figure}
-
-The DHS has the brightest saturation limits of any spectroscopic mode on JWST because each of the 10 DHS elements samples only 1 to 4\% of the pupil and the light is dispersed over over two short wavelength detectors.
-Figure \ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
-The saturation limits are found using \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
-Any known transiting planet system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
-Figure \ref{fig:saturationLim} shows the known transiting systems from \texttt{exoplanets.org} \citep{han2014exopDorg}.
-The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
-We plot the expected yield of TESS \citep{sullivan2015tess} in Figure \ref{fig:saturationLim} and none of the simulated targets saturate the DHS.
 
@@
 
-\subsection{CHIMERA Models}\label{sec:models}
+\begin{figure*}[!thb]
+\centering
+\subfloat[HD 209458b]{
+	\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
+	%\caption{HD209458b}
+	\label{fig:209spec}
+	}
+\subfloat[HAT-P-12b]{
+	\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
+	%\caption{HAT-P-12b}
+	\label{fig:HATp12spec}
+	}
+	\caption{Model spectra separated by molecule for HD~209458b and the inflated warm Saturn HAT-P-12b.The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel.
+a) The simulated data for HD~209458b consists of one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
+The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.
+b) HAT-P-12b is an inflated warm Saturn with an opaque cloud deck at 1 mbar.
+Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, consisting of a total of 2 transits or about 17 hours of JWST time.
+A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}}
+	\label{fig:spec}
+\end{figure*}
 
-\begin{figure}[!tbhp]
-\centering
-\includegraphics[width=1.0\columnwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
-\caption{Model spectra separated by molecule for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
+%\begin{figure}[!tbhp]
+%\centering
+%\includegraphics[width=1.0\columnwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
+%\caption{Model spectra separated by molecule for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
 Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
 A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
-\end{figure}
+%\end{figure}
+
+\subsection{CHIMERA Models}\label{sec:models}
 
@@
 
-\begin{figure}[!tbhp]
-\centering
-\includegraphics[width=1.0\columnwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
-\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
-Similar wavelength coverage can be achieved in just 3 different transits or $\sim$33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
-\end{figure}
-
-We assume isothermal temperature's of 1440K and 960 K for for HD209458b and HAT-P-12b respectively.
-Molecular abundances are assumed constant with altitude at the 0.01 bar thermochemical values.
-While this ``0D" model is likely unrealistic, more sophisticated 1D models in general may be unrealistic given the uncertainties due to the impact of 3-dimensional effects \citep[e.g.][]{line2016nonUclouds,feng2016nonUniform}.
-We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as the sources of opacity (with absorption cross-section derived from \citet{freedman2014opacities} and references therein), but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
-For the HAT-P-12b model, we include an opaque gray cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
-For HD 209458b, this cloud deck is placed at a pressure level of 1 bar which is too deep to affect the spectrum, as shown in Figure \ref{fig:209spec}.
-% if we run the simulations later, also mention emission spectra
-
-\subsubsection{Simulated Observations and Retrieval Methods}
-
-For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
-We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
-%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
-This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
-The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
-The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrange\ can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
-
-\begin{figure*}[!bthp]
+\begin{figure*}[!t]
 \centering
@@
 
+\begin{figure}[!b]
+\centering
+\includegraphics[width=1.0\columnwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
+\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
+Similar wavelength coverage can be achieved in just 3 different transits or $\sim$33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
+\end{figure}
+
+We assume isothermal temperature's of 1440K and 960 K for for HD209458b and HAT-P-12b respectively.
+Molecular abundances are assumed constant with altitude at the 0.01 bar thermochemical values.
+While this ``0D" model is likely unrealistic, more sophisticated 1D models in general may be unrealistic given the uncertainties due to the impact of 3-dimensional effects \citep[e.g.][]{line2016nonUclouds,feng2016nonUniform}.
+We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as the sources of opacity (with absorption cross-section derived from \citet{freedman2014opacities} and references therein), but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
+For the HAT-P-12b model, we include an opaque gray cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
+For HD 209458b, this cloud deck is placed at a pressure level of 1 bar which is too deep to affect the spectrum, as shown in Figure~\ref{fig:209spec}.
+% if we run the simulations later, also mention emission spectra
+
+\subsubsection{Simulated Observations and Retrieval Methods}
+
+For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
+We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
+%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
+This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
+The noise models for the hot Jupiter HD 209458b are shown in Figure~\ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
+The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrange\ can take advantage of NIRISS (also shown in Figure~\ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
+
 We use the \texttt{emcee} version of CHIMERA \citep{greene2016jwst_trans} to recover the individual atmospheric abundances of the simulated spectrum.
@@
 %\end{figure}
+
+\begin{table*}[!t]
+\centering
+\caption{Simultaneous DHS and Grism Observations (Module A)}\label{tab:DHSgprop}
+\begin{tabular}{lcc}
+\hline \hline
+ & DHS & Grism \\
+\hline \hline		
+Resolution: &  \DHSres & 1200 - 1550 \\
+Dispersion: & 0.29 nm / px & 1.0 nm / px \\
+Wavelengths: & 1.05 - 2.00$\mu$m (F150W2)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
+			 & 1.75 - 2.23$\mu$m (F200W)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
+			& 	1.01 - 1.94$\mu$m (F150W2) \footnote{For a field point matched to the F444W filter and long wavelength grism.
+There is a \DHSgap$\mu$m gap between detectors that depends on field position.}	& 3.88 - 4.98$\mu$m (F444W) \\
+Plate Scale: & 32 mas / px  &  65 mas / px\\
+Undeviated Wavelength: & 1.36$\mu$m & 3.94$\mu$m   \\
+\hline
+\end{tabular}
+%%%
+%\caption{Properties of DHS and simultaneous long-wavelength grism spectra. The parameters are for the A-side grism in the direction aligned with detector rows (R).}\label{tab:DHSgprop}
+%\vspace{0.1in}
+\end{table*}
 
@@
 
-One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:corner209} and Figure \ref{fig:cornerHATp12}.
+One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure~\ref{fig:corner209} and Figure~\ref{fig:cornerHATp12}.
 A quick glance at the contributions of individual molecules to the spectrum shown in Figures \ref{fig:209spec} and \ref{fig:HATp12spec} would indicate that the DHS is mainly important for water vapor.
-However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:corner209}.
+However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure~\ref{fig:corner209}.
 Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.
 
-\begin{table*}[!t]
+\begin{figure}[!b]
 \centering
-\begin{tabular}{lcc}
-\hline \hline
- & DHS & Grism \\
-\hline \hline		
-Resolution: &  \DHSres & 1200 - 1550 \\
-Dispersion: & 0.29 nm / px & 1.0 nm / px \\
-Wavelengths: & 1.05 - 2.00$\mu$m (F150W2)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
-			 & 1.75 - 2.23$\mu$m (F200W)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
-			& 	1.01 - 1.94$\mu$m (F150W2) \footnote{For a field point matched to the F444W filter and long wavelength grism.
-There is a \DHSgap$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
-Plate Scale: & 32 mas / px  &  65 mas / px\\
-Undeviated Wavelength: & 1.36$\mu$m & 3.94$\mu$m   \\
-\hline
-\end{tabular}
-\caption{Properties of DHS and simultaneous long-wavelength grism spectra. The parameters are for the A-side grism in the direction aligned with detector rows (R).}\label{tab:DHSgprop}
-\vspace{0.1in}
-\end{table*}
+\includegraphics[width=1.0\columnwidth]{dhs_res.pdf}
+\caption{Resolution as a function of wavelength for the DHS.}\label{fig:DHSRes}
+\end{figure}
+
+\begin{figure}[!b]
+\centering
+\includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
+\caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission.
+The total throughput is the multiple of the filter curve, ``DHS'' grism and the pupil area fraction from Table~\ref{tab:pupfrac}..}\label{fig:DHSthrough}
+\end{figure}
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=0.85\textwidth]{grism_pos_for_max_wcoverage.pdf}
+\caption{DHS wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength channel for the same input source.
+The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.
+The circles plotted for each grism are the shortest usable wavelength, undispersed wavelength and longest usable wavelength.}\label{fig:DHSwaveWGrism}
+\end{figure*}
 
@@
 The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width in the dispersion direction.
-Figure \ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
+Figure~\ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
 There is a spatial gap between short wavelength detectors which corresponds to about \DHSgap$\mu$m in wavelength.
@@
 The DHS can be used in tandem with either the F322W2 or F444W filter for the long wavelength grism observations.
-The properties of the DHS as compared to the grisms are listed in Table \ref{tab:DHSgprop}.
-If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels, though the grism transmission is lower above 2.0$\mu$m, shown in Figure \ref{fig:DHSthrough}.
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
-\caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission.
-The total throughput is the multiple of the filter curve, ``DHS'' grism and the pupil area fraction from Table \ref{tab:pupfrac}..}\label{fig:DHSthrough}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.0\columnwidth]{dhs_res.pdf}
-\caption{Resolution as a function of wavelength for the DHS.}\label{fig:DHSRes}
-\end{figure}
+The properties of the DHS as compared to the grisms are listed in Table~\ref{tab:DHSgprop}.
+If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure~\ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels, though the grism transmission is lower above 2.0$\mu$m, shown in Figure~\ref{fig:DHSthrough}.
 
@@
 
-\begin{figure}[b]
-\centering
-\includegraphics[width=1.0\columnwidth]{dhs_pupil_labels_modA.pdf}
-\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}. 
-The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted "Y" shaped feature).
-The pupil wheel is clocked to make the DHS spectra straight along rows.
-This moves the DHS elements off-center from JWST's pupil and thus decreases the throughput for elements 1 and 6, but the overall combined throughput for all 10 elements is only reduced from 32\% to 29\%.}\label{fig:DHSvsPupilOverlay}
-\end{figure}
-
-A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure \ref{fig:DHSwaveWGrism}.
+A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure~\ref{fig:DHSwaveWGrism}.
 The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
@@
 
-\begin{figure*}[!hbtp]
-\centering
-\includegraphics[width=0.7\textwidth]{grism_pos_for_max_wcoverage.pdf}
-\caption{DHS wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength channel for the same input source.
-The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.
-The circles plotted for each grism are the shortest usable wavelength, undispersed wavelength and longest usable wavelength.}\label{fig:DHSwaveWGrism}
-\end{figure*}
-
-Each DHS spectrum covers roughly 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure \ref{fig:DHSvsPupilOverlay}.
+Each DHS spectrum covers roughly 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure~\ref{fig:DHSvsPupilOverlay}.
 We elect to clock the pupil wheel by 1.9$^\circ$ in order to align the spectra with rows on the short wavelength detector.
@@
 
-The throughput for DHS spectroscopy is the product of the DHS grating efficiency, telescope and instrument throughput for a given filter (both shown in Figure \ref{fig:DHSthrough}) and the pupil coverage by the DHS elements listed in Table \ref{tab:pupfrac}.
-A fractional pupil 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
-For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure~\ref{fig:DHSvsPupilOverlay}.
-We discuss only module A (of the two redundant modules A and B) because the long wavelength grisms are anti-reflective coated for module A.
-
-\begin{table}[!ht]
+\begin{table}[!b]
 \centering
+\caption{DHS Pupil Coverage}\label{tab:pupfrac}
 \begin{tabular}{cc}
 \hline \hline
-DHS \# & Pupil Fraction \\
+Aperture \# & Pupil Fraction \\
 \hline \hline
@@
 \hline
-\\
-\multicolumn{2}{c}{\textbf{DHS Pupil Coverage} }
 \end{tabular}
-\caption{The pupil coverage of the 10 DHS grisms compared to the total primary collecting area for the pupil wheel position that aligns DHS spectra with detector rows.}
-\label{tab:pupfrac}
-%\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}
+%\caption{The pupil coverage of the 10 DHS grisms compared to the total primary collecting area for the pupil wheel position that aligns DHS spectra with detector rows.}\label{tab:pupfrac}
+%\tablecomments{The pupil coverage of the 10 DHS grisms compared to the total primary collecting area for the pupil wheel position that aligns DHS spectra with detector rows.}
+\tablenotetext{0}{The pupil coverage of the 10 DHS grisms compared to the total primary collecting area for the pupil wheel position that aligns DHS spectra with detector rows.}
 \end{table}
 
+\begin{figure}[!t]
+\centering
+\includegraphics[width=1.0\columnwidth]{dhs_pupil_labels_modA.pdf}
+\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table~\ref{tab:pupfrac}. 
+The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted "Y" shaped feature).
+The pupil wheel is clocked to make the DHS spectra straight along rows.
+This moves the DHS elements off-center from JWST's pupil and thus decreases the throughput for elements 1 and 6, but the overall combined throughput for all 10 elements is only reduced from 32\% to 29\%.}\label{fig:DHSvsPupilOverlay}
+\end{figure}
+
+The throughput for DHS spectroscopy is the product of the DHS grating efficiency, telescope and instrument throughput for a given filter (both shown in Figure~\ref{fig:DHSthrough}) and the pupil coverage by the DHS elements listed in Table~\ref{tab:pupfrac}.
+A fractional pupil 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
+For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure~\ref{fig:DHSvsPupilOverlay}.
+Only the long-wavelength grisms if Module A are considered, because those in Module B lack an anti-reflective coating.
+%We discuss only module A (of the two redundant modules A and B) because the long wavelength grisms are anti-reflective coated for module A.
+
 %The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs.
-%The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m.
+%The resulting image, shown in Figure~\ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m.
 %If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
@@
 We adopt the following naming convention for the readout: an observation may consist of one of more exposures which are typically combined into a single \texttt{FITS} file per exposure.
-Within an exposure, there are 1 or more integrations, which consist of a reset frame followed by 1 or more groups of non-destructive reads up a ramp.
-This is illustrated in Fig \ref{fig:readout} for three example readout modes.
+Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp.
+This is illustrated in Figure~\ref{fig:readout} for three example readout modes.
 
@@
 A single FITS file is saved for the exposure, consisting of 1 or more groups per integration.
-No reset frames or dropped frames are saved.``1 Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
+No reset frames or dropped frames are saved.``1~Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
 The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but has a longer minimum integration time, resulting in fainter saturation limits.}\label{fig:readout}
@@
 
-Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS).
-%The window sizes could theoretically be different between the long-wavelength and short-wavelength detectors with only software changes, but would require large changes to the existing software.
-This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
-We recommend  the sub-array locations to be adjustable so that the short wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long wavelength array can be centered on a single grism spectrum.
-The current time series observing templates is limited to subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure \ref{fig:DHSaps}.
-
-\begin{figure}[!t]
-\includegraphics[width=1.0\columnwidth]{example_ap_sizes.pdf}
-\caption{Example DHS image on the A1 short wavelength detector taken during cryogenic vacuum testing of the flight hardware -- see Figure \ref{fig:DHSwaveWGrism} for the detector's position.
-Each element is labeled corresponding to the DHS apertures shown in Figure \ref{fig:DHSvsPupilOverlay} and pupil fraction in Table \ref{tab:pupfrac}.
-The sub-array size options currently available (all 2048 pixels wide) are shown with selections for the brightest spectra available - elements 7 and 8.}\label{fig:DHSaps}
-\end{figure}
-
-The balance between saturating the long-wavelength grism and getting enough SNR in the DHS is listed in Table \ref{tab:SatSNRsubA}.
-The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the DHS noise at 1.1 to 1.9 $\mu$m for a G2V type star at this brightness observing a 1 hour long transit and 1 hour on a star out of transit, binned to the native resolution of R $\sim$ \DHSresApprox.
-We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} and we consider 80\% well depth in the second read as saturation.
-If the bias level after each reset remains stable over the course of observations, it may be possible to use ``1 Group Readout'', illustrated in Figure \ref{fig:readout}.
-The 1 Group Readout method can push the brightness limits by a factor of 2 over CDS because it reduces the integration time by a factor of 2.
-The sub-array sizes and order of DHS elements is shown in Figure \ref{fig:DHSaps}.
-For the brightest sources, which require the 2048 $\times$ 64 pixel subarray, the DHS throughput loss is significant, because only 1 DHS spectrum out of 10 is used, meaning only 4.2\% of JWST's 25 m$^2$ collecting area is used.
-
-\begin{table}[!hb]
+\begin{table}[!b]
 \centering
+\caption{Grism \& DHS Performance}\label{tab:SatSNRsubA}
 \begin{tabular}{llrr}
@@
 \end{tabular}
-\caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes.
+%\caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes.
 The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}\label{tab:SatSNRsubA}
+\tablenotetext{0}{G2V-type star saturation K band limits are shown for suggested sub-array sizes.
+The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1-hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}
 \end{table}
+
+Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS).
+%The window sizes could theoretically be different between the long-wavelength and short-wavelength detectors with only software changes, but would require large changes to the existing software.
+This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
+We recommend  the sub-array locations to be adjustable so that the short wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long wavelength array can be centered on a single grism spectrum.
+The current time series observing templates is limited to subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure~\ref{fig:DHSaps}.
+
+\begin{figure}[!t]
+\includegraphics[width=1.0\columnwidth]{example_ap_sizes.pdf}
+\caption{Example DHS image on the A1 short wavelength detector taken during cryogenic vacuum testing of the flight hardware -- see Figure~\ref{fig:DHSwaveWGrism} for the detector's position.
+Each element is labeled corresponding to the DHS apertures shown in Figure~\ref{fig:DHSvsPupilOverlay} and pupil fraction in Table~\ref{tab:pupfrac}.
+The sub-array size options currently available (all 2048 pixels wide) are shown with selections for the brightest spectra available - elements 7 and 8.}\label{fig:DHSaps}
+\end{figure}
+
+The balance between saturating the long-wavelength grism and getting enough SNR in the DHS is listed in Table~\ref{tab:SatSNRsubA}.
+The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the DHS noise at 1.1 to 1.9 $\mu$m for a G2V type star at this brightness observing a 1 hour long transit and 1 hour on a star out of transit, binned to the native resolution of R $\sim$ \DHSresApprox.
+We use the standard correlated double sampling (CDS) readout mode shown in Figure~\ref{fig:readout} and we consider 80\% well depth in the second read as saturation.
+If the bias level after each reset remains stable over the course of observations, it may be possible to use ``1~Group Readout'', illustrated in Figure~\ref{fig:readout}.
+The 1~Group Readout method can push the brightness limits by a factor of 2 over CDS because it reduces the integration time by a factor of two.
+The sub-array sizes and order of DHS elements is shown in Figure~\ref{fig:DHSaps}.
+For the brightest sources, which require the 2048 $\times$ 64 pixel subarray, the DHS throughput loss is significant, because only 1 DHS spectrum out of 10 is used, meaning only 4.2\% of JWST's 25 m$^2$ collecting area is used.
 
@@
 We consider the use of 458 Gbits of space for science data as the maximum the SSR can handle at once.
-This overload can happen in as few as 10.3 hours if three NIRCam detectors are used simultaneously and all are read out with four amplifiers in CDS mode (meaning no samples are co-added or dropped) -- see Figure \ref{fig:DataVolume}.
+This overload can happen in as few as 10.3 hours if three NIRCam detectors are used simultaneously and all are read out with four amplifiers in CDS mode (meaning no samples are co-added or dropped) -- see Figure~\ref{fig:DataVolume}.
 
@@
 \caption{The maximum time JWST NIRCam can expose three detectors (e.g.
-A1, A3 and A5 in Figure \ref{fig:DHSwaveWGrism}) before filling up JWST's Solid State Recorder (SSR).
+A1, A3 and A5 in Figure~\ref{fig:DHSwaveWGrism}) before filling up JWST's Solid State Recorder (SSR).
 The readout modes shown are for Rapid readouts (no skipped frames as in CDS) and Bright1 for both 1 amplifier and 4 amplifiers.
@@
 The lower frame rate, however, means that the detector saturates at 1/4 the flux as four amplifiers.
-Second, the detector can be read out in BRIGHT1 mode, seen in Figure \ref{fig:readout}.
+Second, the detector can be read out in BRIGHT1 mode, seen in Figure~\ref{fig:readout}.
 This is where a frame is dropped between read 2 and read 1 to increase the integration time and efficiency while reducing data volume.

### 2016-08-25 ms.tex
I updated the plural/singular info for all the cases of the word 'data' I could find, as Marcia caught me using 'data' as a singular.

@@
 In principle, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
-Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
+Thus, the DHS data come ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
 For the example above of HD 209458b, simultaneous DHS data would reduce the required transits from four to three, saving about 11 JWST hours 
@@
 	\caption{Model spectra separated by molecule for HD~209458b and the inflated warm Saturn HAT-P-12b.The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel.
-a) The simulated data for HD~209458b consists of one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
+a) The simulated data for HD~209458b consist of one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
 The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.

### 2016-08-25 ms.tex
An anonymous person clarified the wavelength ranges for each instrument and I made further adjustments to the wavelength descriptions.

@@
 
-\newcommand{\SOSSrange}{0.6 to 2.5 $\mu$m}
+\newcommand{\SOSSrange}{0.6 - 2.5~$\mu$m}
+\newcommand{\SOSSrangeto}{0.6 to 2.5~$\mu$m}
 
@@
 \begin{abstract}
-James Webb Space Telescope (JWST) offers unprecedented sensitivity, stability and wavelength coverage for transiting exoplanet studies, opening up new avenues for measuring atmospheric abundances, structure and temperature profiles.
-Taking full advantage of JWST spectroscopy of planets from 0.6 $\mu$m to 28$\mu$m, however, will require many observations with a combination of the NIRISS, NIRCam, NIRSpec and MIRI instruments.
-In this white paper, we discuss a new NIRCam mode (not yet approved or implemented) that can reduce the number of observations needed to cover the 1.0$\mu$m to 5.0$\mu$m wavelength range.
-The NIRCam instrument was primarily designed as an imager, but includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments.
+The James Webb Space Telescope (JWST) offers unprecedented sensitivity, stability, and wavelength coverage for transiting exoplanet studies, opening up new avenues for measuring atmospheric abundances, structure, and temperature profiles.
+Taking full advantage of JWST spectroscopy of planets from 0.6$\mu$m to 28$\mu$m, however, will require many observations with a combination of the NIRISS, NIRCam, NIRSpec, and MIRI instruments.
+In this white paper, we discuss a new NIRCam mode (not yet approved or implemented) that can reduce the number of necessary observations to cover the 1.0$\mu$m to 5.0$\mu$m wavelength range.
+Even though NIRCam was designed primarily as an imager, it also includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments.
 NIRCam's long-wavelength channel includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with a resolution of $R = 1200 - 1550$ using two separate configurations.
-The long-wavelength grisms have already been approved for wide field and single object (time series) slitless spectroscopy in science operations.
+The long-wavelength grisms have already been approved for science operations, including wide field and single object (time series) slitless spectroscopy.
 We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength channel.
@@
 Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
-JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to its host star.
+JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO, and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to its host star.
 Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes.
@@
 No single JWST instrument can measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum.
-The largest bandwidths possible are NIRSpec's low resolution double prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m.
-Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planetary systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
-For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (SOSS, \SOSSrange), two with NIRCam's long-wavelength channel (F322W2 and F444W + grisms, 2.44$\mu$m to 4.98$\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7~$\mu$ to 5.0$\mu$m.} and one with MIRI (LRS, 5$\mu$m to 12$\mu$m).
-Using the Astronomer's Proposal Tool software\footnote{http://www.stsci.edu/hst/proposing/apt}, each transit observation (pre-ingress, transit, and post-ingress) requires $\sim$9 hr and incurs overheads of $\sim$2 hr, resulting in a total of $\sim$11 hours per transit and hence $\sim$44 hours total to cover
+The largest bandwidths possible are NIRSpec's low resolution double prism ($0.7-5.0~\mu$m) and MIRI's low resolution prism (LRS; $5-12~\mu$m).
+Unfortunately, NIRSpec's low resolution prism mode is so sensitive that it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planetary systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
+For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits:\ one with NIRISS SOSS (\SOSSrange), two with NIRCam's long-wavelength channel grisms (F322W2 and F444W + grisms; $2.44-4.98~\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H modes ($1.7-5.0~\mu$m.} and one with MIRI LRS ($5-12~\mu$m).
+Using the Astronomer's Proposal Tool software\footnote{http://www.stsci.edu/hst/proposing/apt}, each transit observation (pre-ingress, transit, and post-ingress) requires $\sim$9~hours and incurs overheads of $\sim$2~hours, resulting in a total of $\sim$11~hours per transit and hence $\sim$44~hours total to cover
 the full wavelength range.
@@
 The noise models for the hot Jupiter HD 209458b are shown in Figure~\ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
-The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrange\ can take advantage of NIRISS (also shown in Figure~\ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
+The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrangeto\ can take advantage of NIRISS (also shown in Figure~\ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
 

### 2016-08-25 ms.tex
I put in a note that the NIRCam team funded is provided by Goddard.
I clarified the descriptions of the known transiting planets in the saturation plot.

@@
 The DHS has the brightest saturation limits of any spectroscopic mode on JWST because each of the 10 DHS elements samples only 1 to 4\% of the pupil and the light is dispersed over over two short wavelength detectors.
-Figure~\ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
+Figure~\ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms and the known transiting systems from \texttt{exoplanets.org} \citep{han2014exopDorg}, plus \citet{motalebi2015hd219134b}.
 The saturation limits are found using \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
-Any known transiting planet system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
-Figure~\ref{fig:saturationLim} shows the known transiting systems from \texttt{exoplanets.org} \citep{han2014exopDorg}.
+Any known transiting planet system can be observed with the DHS, including the super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
 The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
@@
 CHIMERA retrieval makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
+Funding for the NIRCam team is provided by NASA Goddard Spaceflight Center.
 For use of the El Gato computing system, this material is based upon work supported by the National Science Foundation under Grant No. 1228509.

### 2016-09-21 ms.tex
I moved the technical section to before the science benefits section and added the references the asked for.

@@
 Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent platform for time series observations to characterize the atmospheres of planets that transit their host stars \citep{beichman2014pasp,stevenson2016ers}.
-Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
-JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO, and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to its host star.
+Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O and CO in a variety of hot Jupiter and hot Neptune planets \cite[e.g.][]{charbNa,redfield2008sodium,snellen2008Na209,brogi2012tauB,rodler2012taub,birkby2013water,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
+JWST has the capability of characterizing carbon-bearing and oxygen-bearing molecules such as CH$_4$, CO, CO$_2$ and H$_2$O at unprecedented precision to improve measurements of planet metallicity and C/O in comparison to its host star.
 Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes.
@@
 In this white paper, we explain the value of the DHS mode to fully take advantage of two NIRCam channels to maximize JWST's science potential for transiting planets as well as discuss the specifics of its implementation.
+In section \ref{sec:implementation}, we discuss how the DHS would work for time-series observations and the implications of reading out several detectors simultaneously at a high frame rate.
 In section \ref{sec:addedScience} we discuss the added science that can be achieved with the DHS, including the brightness limits and improved precision in retrieved parameters for a representative system.
-In section \ref{sec:implementation}, we discuss how the DHS would work for time-series observations and the implications of reading out several detectors simultaneously at a high frame rate.
 
-\section{Science Benefits with the DHS}\label{sec:addedScience}
+\section{DHS Implementation}\label{sec:implementation}
 
-\subsection{Brightness limits}\label{sec:brightness}
-
-The DHS has the brightest saturation limits of any spectroscopic mode on JWST because each of the 10 DHS elements samples only 1 to 4\% of the pupil and the light is dispersed over over two short wavelength detectors.
-Figure~\ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms and the known transiting systems from \texttt{exoplanets.org} \citep{han2014exopDorg}, plus \citet{motalebi2015hd219134b}.
-The saturation limits are found using \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
-Any known transiting planet system can be observed with the DHS, including the super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
-The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
-We plot the expected yield of TESS \citep{sullivan2015tess} in Figure~\ref{fig:saturationLim} and none of the simulated targets saturate the DHS.
-
-\begin{figure}[!h]
-\includegraphics[width=1.0\columnwidth]{brightness_scape.pdf}
-\caption{Saturation limits of the DHS mode (blue line), and long-wavelength grism's F322W2 filter (green line) and F444W filter (dark red line) as a function of stellar effective temperature.
-The magnitudes are Vega $K_S$ magnitudes where 80\% of the well depth is filled in the standard CDS readout mode (described in Figure~\ref{fig:readout}) for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
-The blue points are known transiting systems from \texttt{exoplanets.org} and the green points are simulated TESS planets \citep{sullivan2015tess}.}\label{fig:saturationLim}
-\end{figure}
-
-%\subsection{Short Wavelength Monitoring of Starspots}
-%The fact that the DHS can be operated simultaneously with long wavelength grism observations of transits means that one can monitor for star spots during a transit.
-
-\begin{figure*}[!thb]
-\centering
-\subfloat[HD 209458b]{
-	\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
-	%\caption{HD209458b}
-	\label{fig:209spec}
-	}
-\subfloat[HAT-P-12b]{
-	\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
-	%\caption{HAT-P-12b}
-	\label{fig:HATp12spec}
-	}
-	\caption{Model spectra separated by molecule for HD~209458b and the inflated warm Saturn HAT-P-12b.The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel.
-a) The simulated data for HD~209458b consist of one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
-The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.
-b) HAT-P-12b is an inflated warm Saturn with an opaque cloud deck at 1 mbar.
-Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, consisting of a total of 2 transits or about 17 hours of JWST time.
-A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}}
-	\label{fig:spec}
-\end{figure*}
-
-%\begin{figure}[!tbhp]
-%\centering
-%\includegraphics[width=1.0\columnwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
-%\caption{Model spectra separated by molecule for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
-Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
-A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
-%\end{figure}
-
-\subsection{CHIMERA Models}\label{sec:models}
-
-We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to illustrate the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
-We first simulate a forward model of a transmission spectrum for two planets, HD 209458b \citep{henry00,charbonneau00} and HAT-P-12b \citep{hartman2009hatp12}.
-We then add Gaussian noise using the SNR estimated on the target to create a simulated spectrum.
-Finally, we run a Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
-We combine the individual gases' posterior distributions to derive the C/O ratio and metallicity (\citet{greene2016jwst_trans}) .
-
-%For the underlying ``true" model of HD 209458b, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}.
-%For HAT-P-12b, we scale the atomic abundances of all elements except Hydrogen and Helium by a factor of 22 using the mass-metallicity relation of \citep{kreidberg2014wasp43} and \citep{line2016hd209wfc3}.
-%The atomic abundances are converted to molecular mixing ratios using the Chemical Equilibrium code with Applications (CEA)\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} to calculate the fractions of molecules at the given pressure and temperature.
-
-To construct the model atmospheres and generate a spectrum we require a thermal profile and molecular abundances.
-For simplicity, we assume isothermal atmospheres at the planetary equilibrium temperatures.
-Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea}) at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
-For HD 209458b (0.7 M$_{Jup}$), we prescribe solar metallicity since it is close to one Jupiter mass.
-For HAT-P-12b (0.2 M$_{Jup}$), we prescribe a planet metallicity of 22 $\times$ solar using the relation from \citet{kreidberg2014wasp43}.
-In both cases, we reduce the oxygen volume mixing ratio to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}, but this only results in a $\sim$ 20\% change in the Oxygen abundance.
-
-\begin{figure*}[!t]
-\centering
-\subfloat[HD 209458b]{
-	\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_1trans_corner.png}
-	%\caption{HD209458b}
-	\label{fig:corner209}
-	}
-\subfloat[HAT-P-12b]{
-	\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
-	%\caption{HAT-P-12b}
-	\label{fig:cornerHATp12}
-	}
-	\caption{Posterior distributions for MCMC runs of HD209458b and HAT-P-12b with the DHS (blue) and without the DHS (green).
-The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.
-Abundances are given in $\log_{10}$~(ppm).
-Cloud pressure is in $\log_{10}$~(bar).}
-	\label{fig:corner}
-\end{figure*}
-
-\begin{figure}[!b]
-\centering
-\includegraphics[width=1.0\columnwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
-\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
-Similar wavelength coverage can be achieved in just 3 different transits or $\sim$33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
-\end{figure}
-
-We assume isothermal temperature's of 1440K and 960 K for for HD209458b and HAT-P-12b respectively.
-Molecular abundances are assumed constant with altitude at the 0.01 bar thermochemical values.
-While this ``0D" model is likely unrealistic, more sophisticated 1D models in general may be unrealistic given the uncertainties due to the impact of 3-dimensional effects \citep[e.g.][]{line2016nonUclouds,feng2016nonUniform}.
-We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as the sources of opacity (with absorption cross-section derived from \citet{freedman2014opacities} and references therein), but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
-For the HAT-P-12b model, we include an opaque gray cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
-For HD 209458b, this cloud deck is placed at a pressure level of 1 bar which is too deep to affect the spectrum, as shown in Figure~\ref{fig:209spec}.
-% if we run the simulations later, also mention emission spectra
-
-\subsubsection{Simulated Observations and Retrieval Methods}
-
-For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
-We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
-%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
-This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
-The noise models for the hot Jupiter HD 209458b are shown in Figure~\ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
-The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrangeto\ can take advantage of NIRISS (also shown in Figure~\ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
-
-We use the \texttt{emcee} version of CHIMERA \citep{greene2016jwst_trans} to recover the individual atmospheric abundances of the simulated spectrum.
-The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile; 2) the altitude of the 10-bar pressure surface where the model begins; 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths; 4) through 11) the constant-with-altitude mixing ratios of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively; 12) an amplitude of a Raleigh-like haze; and 13) a power law index for the Raleigh-type haze.
-We assume uniform-in-log priors from 10$^{-12}$ to 1 for all volume mixing ratios.
-The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 (times 160 walkers) to allow for burn-in.
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_DHS.pdf}
-%\caption{Posterior distributions of the retrieved abundances, showing improvements of the constraints on temperature, cloud pressure upper limit and H$_2$O, CO$_2$ and CO abundances with the DHS.
-%Vertical dashed bars show the input abundances for the initial forward model that was used to generate the simulated spectru.}\label{fig:DHSposterios}
-%\end{figure}
+\subsection{DHS properties}
+The DHS expands the wavelength range that NIRCam can achieve on a single observation by simultaneously obtaining spectroscopy with NIRCam's short wavelength channel and long wavelength channel.
+The maximum wavelength range for the F150W2 filter in the short wavelength channel is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
+The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width in the dispersion direction.
+Figure~\ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
+There is a spatial gap between short wavelength detectors which corresponds to about \DHSgap$\mu$m in wavelength.
+The center of this gap depends on source position.
+The DHS can be used in tandem with either the F322W2 or F444W filter for the long wavelength grism observations.
+The properties of the DHS as compared to the grisms are listed in Table~\ref{tab:DHSgprop}.
+If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure~\ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels, though the grism transmission is lower above 2.0$\mu$m, shown in Figure~\ref{fig:DHSthrough}.
 
@@
 
-\subsection{Parameter Estimation Results}\label{sec:retrievals}
-
-The posterior distributions for retrieved parameters for the most important abundances are shown in Figure~\ref{fig:corner}.
-We show the posterior distributions for two cases:
-\begin{enumerate}
-\item \label{it:DHSgr} An observation with the long wavelength grisms alone (2.4-5.0$\mu$m), shown in green.
-\item \label{it:grAlone} An observation with the long wavelength grisms (2.4-5.0$\mu$m) with simultaneous DHS spectra (1.0-2.0$\mu$m), shown in blue.
-\end{enumerate}
-For the spectral data they have in common (2.4$\mu$m to 5.0$\mu$m), we use the same noise instance to make direct comparison easier.
-
-The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used with the long wavelength grisms (Case~\ref{it:DHSgr}) as compared to the long wavelength grisms alone (Case~\ref{it:grAlone}).
-These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.
-
-%\begin{figure*}
-%\centering
-%\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
-%\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) and without the DHS (green).
-%The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.
-Abundances are given in Log$_{10}$(ppm).
-Cloud pressure is in Log$_{10}$(bar).}\label{fig:corner209}
-%\end{figure*}
-
-The warm Saturn HAT-P-12b model shows improvements to the temperature constraints, but the cloud pressure measurements have similar uncertainties with and without the DHS.
-This is because the 1mbar cloud layer begins to affect the opacity near 4.0$\mu$m, which is measured by the long wavelength grisms.
-As with HD 209458b, the DHS improves constraints on the H$_2$O and CO$_2$ abundances, but since the planet is at a cooler temperatures, chemical equilibrium favors CH$_4$ over CO, so the constraints are much better on CH$_4$.
-
-%\begin{figure*}
-%\centering
-%\includegraphics[width=1.0\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
-%\caption{Posterior distributions an MCMC retrieval of parameters for HAT-P-12b with the DHS (blue) and without the DHS (gray).}\label{fig:cornerHATp12}
-%\end{figure*}
-
-One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure~\ref{fig:corner209} and Figure~\ref{fig:cornerHATp12}.
-A quick glance at the contributions of individual molecules to the spectrum shown in Figures \ref{fig:209spec} and \ref{fig:HATp12spec} would indicate that the DHS is mainly important for water vapor.
-However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure~\ref{fig:corner209}.
-Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.
-
 \begin{figure}[!b]
@@
 
+\subsection{DHS Layout}\label{sec:layout}
+
+A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure~\ref{fig:DHSwaveWGrism}.
+The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
+The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
+Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
+
 \begin{figure*}[!t]
@@
 \end{figure*}
-
-\section{DHS Implementation}\label{sec:implementation}
-
-\subsection{DHS properties}
-The DHS expands the wavelength range that NIRCam can achieve on a single observation by simultaneously obtaining spectroscopy with NIRCam's short wavelength channel and long wavelength channel.
-The maximum wavelength range for the F150W2 filter in the short wavelength channel is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
-The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width in the dispersion direction.
-Figure~\ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
-There is a spatial gap between short wavelength detectors which corresponds to about \DHSgap$\mu$m in wavelength.
-The center of this gap depends on source position.
-The DHS can be used in tandem with either the F322W2 or F444W filter for the long wavelength grism observations.
-The properties of the DHS as compared to the grisms are listed in Table~\ref{tab:DHSgprop}.
-If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure~\ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels, though the grism transmission is lower above 2.0$\mu$m, shown in Figure~\ref{fig:DHSthrough}.
-
-\subsection{DHS Layout}\label{sec:layout}
-
-A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure~\ref{fig:DHSwaveWGrism}.
-The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
-The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
-Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
 
@@
 Perhaps future changes to the OSS could allow operating the LW detectors with 4 outputs and the SW ones with 1 output, reducing data volume considerably.
+
+\section{Science Benefits with the DHS}\label{sec:addedScience}
+
+\subsection{Brightness limits}\label{sec:brightness}
+
+The DHS has the brightest saturation limits of any spectroscopic mode on JWST because each of the 10 DHS elements samples only 1 to 4\% of the pupil and the light is dispersed over over two short wavelength detectors.
+Figure~\ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms and the known transiting systems from \texttt{exoplanets.org} \citep{han2014exopDorg}, plus \citet{motalebi2015hd219134b}.
+The saturation limits are found using \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
+Any known transiting planet system can be observed with the DHS, including the super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which saturates the long-wavelength grism with the F322W2 filter and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
+The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.
+We plot the expected yield of TESS \citep{sullivan2015tess} in Figure~\ref{fig:saturationLim} and none of the simulated targets saturate the DHS.
+
+\begin{figure}[!h]
+\includegraphics[width=1.0\columnwidth]{brightness_scape.pdf}
+\caption{Saturation limits of the DHS mode (blue line), and long-wavelength grism's F322W2 filter (green line) and F444W filter (dark red line) as a function of stellar effective temperature.
+The magnitudes are Vega $K_S$ magnitudes where 80\% of the well depth is filled in the standard CDS readout mode (described in Figure~\ref{fig:readout}) for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
+The blue points are known transiting systems from \texttt{exoplanets.org} and the green points are simulated TESS planets \citep{sullivan2015tess}.}\label{fig:saturationLim}
+\end{figure}
+
+%\subsection{Short Wavelength Monitoring of Starspots}
+%The fact that the DHS can be operated simultaneously with long wavelength grism observations of transits means that one can monitor for star spots during a transit.
+
+\begin{figure*}[!thb]
+\centering
+\subfloat[HD 209458b]{
+	\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
+	%\caption{HD209458b}
+	\label{fig:209spec}
+	}
+\subfloat[HAT-P-12b]{
+	\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
+	%\caption{HAT-P-12b}
+	\label{fig:HATp12spec}
+	}
+	\caption{Model spectra separated by molecule for HD~209458b and the inflated warm Saturn HAT-P-12b.The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel.
+a) The simulated data for HD~209458b consist of one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
+The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.
+b) HAT-P-12b is an inflated warm Saturn with an opaque cloud deck at 1 mbar.
+Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, consisting of a total of 2 transits or about 17 hours of JWST time.
+A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}}
+	\label{fig:spec}
+\end{figure*}
+
+%\begin{figure}[!tbhp]
+%\centering
+%\includegraphics[width=1.0\columnwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
+%\caption{Model spectra separated by molecule for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
+Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time.
+A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
+%\end{figure}
+
+\subsection{CHIMERA Models}\label{sec:models}
+
+We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to illustrate the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
+We first simulate a forward model of a transmission spectrum for two planets, HD 209458b \citep{henry00,charbonneau00} and HAT-P-12b \citep{hartman2009hatp12}.
+We then add Gaussian noise using the SNR estimated on the target to create a simulated spectrum.
+Finally, we run a Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
+We combine the individual gases' posterior distributions to derive the C/O ratio and metallicity (\citet{greene2016jwst_trans}) .
+
+%For the underlying ``true" model of HD 209458b, we use solar abundances of \citet{asplund} and reduce the oxygen by a factor of 24\% to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}.
+%For HAT-P-12b, we scale the atomic abundances of all elements except Hydrogen and Helium by a factor of 22 using the mass-metallicity relation of \citep{kreidberg2014wasp43} and \citep{line2016hd209wfc3}.
+%The atomic abundances are converted to molecular mixing ratios using the Chemical Equilibrium code with Applications (CEA)\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} to calculate the fractions of molecules at the given pressure and temperature.
+
+To construct the model atmospheres and generate a spectrum we require a thermal profile and molecular abundances.
+For simplicity, we assume isothermal atmospheres at the planetary equilibrium temperatures.
+Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea}) at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
+For HD 209458b (0.7 M$_{Jup}$), we prescribe solar metallicity since it is close to one Jupiter mass.
+For HAT-P-12b (0.2 M$_{Jup}$), we prescribe a planet metallicity of 22 $\times$ solar using the relation from \citet{kreidberg2014wasp43}.
+In both cases, we reduce the oxygen volume mixing ratio to account for the rainout out of MgSiO$_3$ and MgSiO$_4$ which are below their condensation temperatures \citep{sing2016continuum}, but this only results in a $\sim$ 20\% change in the Oxygen abundance.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[HD 209458b]{
+	\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_1trans_corner.png}
+	%\caption{HD209458b}
+	\label{fig:corner209}
+	}
+\subfloat[HAT-P-12b]{
+	\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
+	%\caption{HAT-P-12b}
+	\label{fig:cornerHATp12}
+	}
+	\caption{Posterior distributions for MCMC runs of HD209458b and HAT-P-12b with the DHS (blue) and without the DHS (green).
+The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.
+Abundances are given in $\log_{10}$~(ppm).
+Cloud pressure is in $\log_{10}$~(bar).}
+	\label{fig:corner}
+\end{figure*}
+
+\begin{figure}[!b]
+\centering
+\includegraphics[width=1.0\columnwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
+\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
+Similar wavelength coverage can be achieved in just 3 different transits or $\sim$33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
+\end{figure}
+
+We assume isothermal temperature's of 1440K and 960 K for for HD209458b and HAT-P-12b respectively.
+Molecular abundances are assumed constant with altitude at the 0.01 bar thermochemical values.
+While this ``0D" model is likely unrealistic, more sophisticated 1D models in general may be unrealistic given the uncertainties due to the impact of 3-dimensional effects \citep[e.g.][]{line2016nonUclouds,feng2016nonUniform}.
+We include H$_2$O, CO, CO$_2$, CH$_4$, NH$_3$, C$_2$H$_2$, HCN and collision-induced absorption (CIA) of hydrogen as the sources of opacity (with absorption cross-section derived from \citet{freedman2014opacities} and references therein), but only H$_2$O, CH$_4$, CO and CO$_2$ contribute significantly to the opacity, as seen in Figures \ref{fig:209spec} and \ref{fig:HATp12spec}.
+For the HAT-P-12b model, we include an opaque gray cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
+For HD 209458b, this cloud deck is placed at a pressure level of 1 bar which is too deep to affect the spectrum, as shown in Figure~\ref{fig:209spec}.
+% if we run the simulations later, also mention emission spectra
+
+\subsubsection{Simulated Observations and Retrieval Methods}
+
+For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
+We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
+%In other words, there is one DHS measurement per grism filter (F444W and F322W2).
+This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
+The noise models for the hot Jupiter HD 209458b are shown in Figure~\ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
+The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrangeto\ can take advantage of NIRISS (also shown in Figure~\ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
+
+We use the \texttt{emcee} version of CHIMERA \citep{greene2016jwst_trans} to recover the individual atmospheric abundances of the simulated spectrum.
+The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile; 2) the altitude of the 10-bar pressure surface where the model begins; 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths; 4) through 11) the constant-with-altitude mixing ratios of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively; 12) an amplitude of a Raleigh-like haze; and 13) a power law index for the Raleigh-type haze.
+We assume uniform-in-log priors from 10$^{-12}$ to 1 for all volume mixing ratios.
+The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 (times 160 walkers) to allow for burn-in.
+
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_DHS.pdf}
+%\caption{Posterior distributions of the retrieved abundances, showing improvements of the constraints on temperature, cloud pressure upper limit and H$_2$O, CO$_2$ and CO abundances with the DHS.
+%Vertical dashed bars show the input abundances for the initial forward model that was used to generate the simulated spectru.}\label{fig:DHSposterios}
+%\end{figure}
+
+\subsection{Parameter Estimation Results}\label{sec:retrievals}
+
+The posterior distributions for retrieved parameters for the most important abundances are shown in Figure~\ref{fig:corner}.
+We show the posterior distributions for two cases:
+\begin{enumerate}
+\item \label{it:DHSgr} An observation with the long wavelength grisms alone (2.4-5.0$\mu$m), shown in green.
+\item \label{it:grAlone} An observation with the long wavelength grisms (2.4-5.0$\mu$m) with simultaneous DHS spectra (1.0-2.0$\mu$m), shown in blue.
+\end{enumerate}
+For the spectral data they have in common (2.4$\mu$m to 5.0$\mu$m), we use the same noise instance to make direct comparison easier.
+
+The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used with the long wavelength grisms (Case~\ref{it:DHSgr}) as compared to the long wavelength grisms alone (Case~\ref{it:grAlone}).
+These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.
+
+%\begin{figure*}
+%\centering
+%\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
+%\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) and without the DHS (green).
+%The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.
+Abundances are given in Log$_{10}$(ppm).
+Cloud pressure is in Log$_{10}$(bar).}\label{fig:corner209}
+%\end{figure*}
+
+The warm Saturn HAT-P-12b model shows improvements to the temperature constraints, but the cloud pressure measurements have similar uncertainties with and without the DHS.
+This is because the 1mbar cloud layer begins to affect the opacity near 4.0$\mu$m, which is measured by the long wavelength grisms.
+As with HD 209458b, the DHS improves constraints on the H$_2$O and CO$_2$ abundances, but since the planet is at a cooler temperatures, chemical equilibrium favors CH$_4$ over CO, so the constraints are much better on CH$_4$.
+
+%\begin{figure*}
+%\centering
+%\includegraphics[width=1.0\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
+%\caption{Posterior distributions an MCMC retrieval of parameters for HAT-P-12b with the DHS (blue) and without the DHS (gray).}\label{fig:cornerHATp12}
+%\end{figure*}
+
+One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure~\ref{fig:corner209} and Figure~\ref{fig:cornerHATp12}.
+A quick glance at the contributions of individual molecules to the spectrum shown in Figures \ref{fig:209spec} and \ref{fig:HATp12spec} would indicate that the DHS is mainly important for water vapor.
+However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure~\ref{fig:corner209}.
+Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.
 

### 2016-09-25 ms.tex
I added some changes to the text from the reviewers comments 1-11, including a reference to Morley et al., quantified the sensitivity differences between the DHS and other modes, clarified the spectra simulations.

@@
 Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O and CO in a variety of hot Jupiter and hot Neptune planets \cite[e.g.][]{charbNa,redfield2008sodium,snellen2008Na209,brogi2012tauB,rodler2012taub,birkby2013water,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
-JWST has the capability of characterizing carbon-bearing and oxygen-bearing molecules such as CH$_4$, CO, CO$_2$ and H$_2$O at unprecedented precision to improve measurements of planet metallicity and C/O in comparison to its host star.
-Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes.
+JWST has the capability of characterizing carbon-bearing and oxygen-bearing molecules such as CH$_4$, CO, CO$_2$ and H$_2$O at high precision to improve measurements of planet metallicity and C/O in comparison to its host star.
+Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes \citep[e.g.][]{morley2015superEclouds}.
 
@@
 The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput.
-The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the second order of the spectrum begins to overlap at 2.0$\mu$m.\footnote{The prism that spatially separate the 10 DHS spectra separate the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
+The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the second order of the spectrum begins to overlap at 2.0$\mu$m.\footnote{The prisms that spatially separate the 10 DHS spectra cross-disperse the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
+When using the DHS with the F150W2 filter and pairing it with the long wavelength grisms (F322W2 and F444W), the wavelength coverage will therefore be 1.0 to 5.0$\mu$m with a gap from 2.00$\mu$m to 2.44$\mu$m.
+This wavelength gap can include a CH$_4$ feature for cool planets, but other CH$_4$ bands are also visible at 1.7$\mu$m and 3.5$\mu$m.
 
@@
 if the wavelengths from 2.0$\mu$m to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
-The DHS is expected to collect similar photon levels as HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.
+The DHS is expected to collect similar photon levels as HST's WFC3 grisms because the DHS pupil coverage ($\sim$30\%) and relative throughput ($\sim$30\% versus $\sim$40\% with WFC3 \texttt{http://etc.stsci.edu}) are together similar to the ratio between telescope collecting areas.
+Therefore, the DHS is like a free coordinated HST observation for every long-wavelength NIRCam grism transit but without the interruptions or thermal consequences of HST's low earth orbit.
 
@@
 b) HAT-P-12b is an inflated warm Saturn with an opaque cloud deck at 1 mbar.
-Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, consisting of a total of 2 transits or about 17 hours of JWST time.
+Error bars shown are for simulated observations of 2 total transits: one transit with the DHS and F322W2+grism together and one transit with the DHS and F444W+grism together for a total of about 17 hours of JWST time.
 A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}}
@@
 The noise models for the hot Jupiter HD 209458b are shown in Figure~\ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
-The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher SNR and full wavelength coverage from \SOSSrangeto\ can take advantage of NIRISS (also shown in Figure~\ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
+The DHS has lower total throughput ($\sim$8\% including pupil coverage factor) and a smaller wavelength coverage than the NIRISS instrument in SOSS mode ($\sim$30\% throughput\footnote{\texttt{http://maestria.astro.umontreal.ca/niriss/simu1D/simu1D.php}}), so observations which require higher SNR and full wavelength coverage from \SOSSrangeto\ can take advantage of NIRISS (also shown in Figure~\ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
 

### 2016-09-28 ms.tex
I added a lot more description of the subarray sizes, locations, DHS elements and description of the readout modes availabl including references all of this to address the reviewer comments 11-20.

@@
 
-A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure~\ref{fig:DHSwaveWGrism}.
-The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
-The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
-Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
-
 \begin{figure*}[!t]
@@
 
+A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure~\ref{fig:DHSwaveWGrism}.
+The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
+The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
+Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
+
 Each DHS spectrum covers roughly 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure~\ref{fig:DHSvsPupilOverlay}.
@@
 This is needed for bright targets that will saturate the long wavelength detector with longer frame times, as discussed in Section \ref{sec:readout}.
-There is a price for clocking the DHS pupil wheel to align spectra with rows: all DHS grisms are partially obscured by either the secondary supports or the outer edges of the primary, save element 7.
+There is a price for clocking the DHS pupil wheel to align spectra with rows: all DHS grisms are partially obscured by either the secondary supports or the outer edges of the primary, save elements 7 and 10.
 Fortunately, the relative obscuration for all 10 DHS spectra is small, going from 32\% total throughput when the pupil wheel is centered (which produces tilted spectra), versus 29\% if the pupil wheel is clocked to align the spectra along rows.
@@
 \subsection{Readout Considerations}\label{sec:readout}
-JWST's NIRCam has many different possible readout patterns per pixel and array that all factor in to the SNRs and saturation limits for an observation.
-We adopt the following naming convention for the readout: an observation may consist of one of more exposures which are typically combined into a single \texttt{FITS} file per exposure.
+JWST's NIRCam instrument has many different possible readout patterns per pixel and array that all factor in to the SNRs and saturation limits for an observation.
+We adopt the following naming convention for the readout: an observation may consist of one of more exposures which are combined into a single \texttt{FITS} file per exposure.
 Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp.
 This is illustrated in Figure~\ref{fig:readout} for three example readout modes.
+
+We consider a simplified example of a time series using a standard correlated double sampling (CDS) illustrated in Figure~\ref{fig:readout} and assume a round frame time of 10.0 seconds, close to the actual 10.74 seconds full frame read time.
+The raw data delivered to observers for use in a pipeline would consist of a single FITS file containing a data cube.
+If the data is in full frame mode, cube would have dimensions of 2048 $\times$ 2048 $\times$ 8, which can be thought of 8 image planes.
+In this example there are 4 integrations consisting of a reset followed by two reads, which are saved as two image planes per integration.	
+For simplicity in this example, we ignore many of the corrections that are applied in a pipeline such as non-linearity correction, reference pixel correction, intrapixel capacitance, flat fielding etc.
+Under these assumptions, the flux (in DN/s) in any integration is the difference between the two reads divided by the frame time.
+This reduces the 8 image planes, to 4 flux planes, one per integration.
+Spectral extraction on the flux planes \citep[e.g.][]{horne1986optimalE} produces 1 flux per wavelength bin.
+The time series for a given wavelength would consist of the 4 fluxes with 4 time coordinates centered at 15 sec, 45 sec, 75 sec and 105 sec if we use the mid-points of the two reads.
 
@@
 \end{figure}
+
+There are several variations of readout patterns available to NIRCam with the Astronomers Proposal Tool (APT)\footnote{http://www.stsci.edu/hst/proposing/apt}.
+For exoplanets time series observations, the readout patterns most commonly used will likely be ``RAPID'', meaning every sample is saved up the ramp individually and ``BRIGHT1'' where a single frame is dropped between reads.
+These modes give high time resolution and allow one to detect and flag cosmic ray hits without having to discard large amounts of data.
+The number of groups per integration is a variable set in the APT.
+When the number of groups is 1 (``1~Group Readout''), there is no ability to subtract out the bias frame so it relies on the bias level being constant through the whole time series.
+When the number of groups is 2, the slope can be calculated from the difference between the frames divided by the frame time.
+It is the same as the CDS mode described above when using RAPID readout.
+For a higher number groups, a line is fit to the the ramp to calculate a slope image for every integration.
+In exoplanet time series, the high signal to noise ratios required generally mean that bright sources will be observed so these will generally not benefit from skipped frames or co-added frames of other JWST readout modes, which come at the expense of lower time resolution, reduced ability for cosmic ray rejection and fainter saturation limits.
+For more general discussion of HAWAII-2RG detector readout, we refer to \citet{rauscher2007detectors} and for specific readout patterns we refer to \citet{roberto2009optimalR1} and \citet{roberto2010optimalR2}.
 
@@
 This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
-We recommend  the sub-array locations to be adjustable so that the short wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long wavelength array can be centered on a single grism spectrum.
-The current time series observing templates is limited to subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure~\ref{fig:DHSaps}.
+The current time series observing templates available in APT are limited to subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure~\ref{fig:DHSaps}.
+These are the subarrays that will be available to Cycle 1 science programs and likely stay this way for continuity through the mission in order to stick to detector ``sweet spots'' that are well characterized and calibrated.
+In principle, the short wavelength detectors can be read out with different sizes and read patterns from long wavelength array or even what is available in APT, but we realize there are operational costs to implementing and testing new modes in the OSS software and data handling.
+
+We recommend that the sub-array locations to be adjusted so that the short wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long wavelength array can be centered on a single grism spectrum.
+For the 2048~$\times$~64 and 2048~$\times$~128 subarrays, which can only encompass one spectrum with more than 10 pixels of background, they should be centered on the spectrum from element 7, since it has the maximum possible throughput listed in Table~\ref{tab:pupfrac}.
+For the 2048~$\times$~256 subarray, the location should be centered of the the middle of the spectra from elements 7 and 8 since they have the highest throughput of any adjacent pairs from Table~\ref{tab:pupfrac}.
+This is illustrated in Figure \ref{fig:DHSaps}.
 
@@
 This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
+The readout mode in all cases simulated is RAPID readout (all reads saved without skips up the ramp discussed in Section \ref{sec:readout}) with 10 reads up the ramp for HD 209458 and 25 reads up the ramp for HAT-P-12b.
+
 The noise models for the hot Jupiter HD 209458b are shown in Figure~\ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
@@
 \begin{enumerate}
-\item \label{it:DHSgr} An observation with the long wavelength grisms alone (2.4-5.0$\mu$m), shown in green.
-\item \label{it:grAlone} An observation with the long wavelength grisms (2.4-5.0$\mu$m) with simultaneous DHS spectra (1.0-2.0$\mu$m), shown in blue.
+\item \label{it:grAlone} An observation with the long wavelength grisms alone (2.4-5.0$\mu$m), shown in green.
+\item \label{it:DHSgr} An observation with the long wavelength grisms (2.4-5.0$\mu$m) with simultaneous DHS spectra (1.0-2.0$\mu$m), shown in blue.
 \end{enumerate}
@@
 The brightest known systems and similarly bright future TESS targets will be accessible with NIRCam's DHS mode.
-We present example usage of the DHS mode on example systems and show that the temperature, cloud pressure level and water vapor constraints are improved with the DHS.
+We present example usage of the DHS mode on two systems and show that the temperature, cloud pressure level and water vapor constraints are improved with the DHS.
 Furthermore, the improved water vapor constraints also feed back to higher precision CO and CO$_2$ abundances because of the correlation of these derived parameters.
@@
 \item Allow the NIRCam pupil wheel to be used for science at the DHS element position with spectra parallel with detector rows
-\item Allow subarray locations to be different for the short wavelength arrays and the long wavelength arrays in order to capture the spectrum for Element numbers 7 and 8 for subarrays
-\item Choose field points from NIRCam's long wavelength grism to allow simultaneous DHS spectroscopy with all 10 DHS elements
+\item Allow subarray locations to be different for the short wavelength arrays and the long wavelength arrays in order to capture the spectrum for element number 7 for 2048~$\times$~64 and 2048~$\times$~128 subarrays and both element numbers 7 and 8 for the 2048~$\times$~256 subarray
+\item Choose field points from NIRCam's long wavelength grism to allow simultaneous DHS spectroscopy with all 10 DHS elements when reading out in full frame (2048~$\times$~2408) mode
 \item Change the OSS software and timing so that large subarrays may used with the DHS simultaneously with small 2048$\times$64 subarrays with the long wavelength grisms

### 2016-09-28 ms.tex
re-arranged placement of the resolution and throughput figures and updated some clarifying text.

@@
 \subsection{DHS properties}
+
+\begin{figure}
+\centering
+\includegraphics[width=1.0\columnwidth]{dhs_res.pdf}
+\caption{Resolution as a function of wavelength for the DHS.}\label{fig:DHSRes}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
+\caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission.
+The total throughput is the multiple of the filter curve, ``DHS'' grism and the pupil area fraction from Table~\ref{tab:pupfrac}..}\label{fig:DHSthrough}
+\end{figure}
+
 The DHS expands the wavelength range that NIRCam can achieve on a single observation by simultaneously obtaining spectroscopy with NIRCam's short wavelength channel and long wavelength channel.
 The maximum wavelength range for the F150W2 filter in the short wavelength channel is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
-The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width in the dispersion direction.
+The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width as each other in the dispersion direction.
 Figure~\ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
@@
 The properties of the DHS as compared to the grisms are listed in Table~\ref{tab:DHSgprop}.
-If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure~\ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength channels, though the grism transmission is lower above 2.0$\mu$m, shown in Figure~\ref{fig:DHSthrough}.
+If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure~\ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the DHS+F150W2 spectrum and Grism+F322W2 spectra, though the grism transmission is lower above 2.0$\mu$m, shown in Figure~\ref{fig:DHSthrough}.
 
-\begin{table*}[!t]
+\begin{table*}
 \centering
-\caption{Simultaneous DHS and Grism Observations (Module A)}\label{tab:DHSgprop}
+\caption{Simultaneous DHS and Grism Properties (Module A)}\label{tab:DHSgprop}
 \begin{tabular}{lcc}
@@
 
-\begin{figure}[!b]
-\centering
-\includegraphics[width=1.0\columnwidth]{dhs_res.pdf}
-\caption{Resolution as a function of wavelength for the DHS.}\label{fig:DHSRes}
-\end{figure}
-
-\begin{figure}[!b]
-\centering
-\includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
-\caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission.
-The total throughput is the multiple of the filter curve, ``DHS'' grism and the pupil area fraction from Table~\ref{tab:pupfrac}..}\label{fig:DHSthrough}
-\end{figure}
-
 \subsection{DHS Layout}\label{sec:layout}
 
-\begin{figure*}[!t]
+\begin{figure*}
 \centering
@@
 \includegraphics[width=1.0\columnwidth]{dhs_pupil_labels_modA.pdf}
-\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table~\ref{tab:pupfrac}. 
-The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted "Y" shaped feature).
+\caption{DHS pupil coverage by each of the 10 DHS grisms, with the fractional throughput given in Table~\ref{tab:pupfrac}. 
+The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted ``Y'' shaped feature).
 The pupil wheel is clocked to make the DHS spectra straight along rows.
@@
 The throughput for DHS spectroscopy is the product of the DHS grating efficiency, telescope and instrument throughput for a given filter (both shown in Figure~\ref{fig:DHSthrough}) and the pupil coverage by the DHS elements listed in Table~\ref{tab:pupfrac}.
-A fractional pupil 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
+A fractional pupil of 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
 For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure~\ref{fig:DHSvsPupilOverlay}.
-Only the long-wavelength grisms if Module A are considered, because those in Module B lack an anti-reflective coating.
+Only the long-wavelength grisms of Module A are considered, because those in Module B lack an anti-reflective coating.
 %We discuss only module A (of the two redundant modules A and B) because the long wavelength grisms are anti-reflective coated for module A.
@@
 Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp.
+In all of our examples, there is one read per group.
 This is illustrated in Figure~\ref{fig:readout} for three example readout modes.
@@
 We consider a simplified example of a time series using a standard correlated double sampling (CDS) illustrated in Figure~\ref{fig:readout} and assume a round frame time of 10.0 seconds, close to the actual 10.74 seconds full frame read time.
+CDS is equivalent to RAPID mode with 2 reads up the ramp.
 The raw data delivered to observers for use in a pipeline would consist of a single FITS file containing a data cube.
@@
 
-There are several variations of readout patterns available to NIRCam with the Astronomers Proposal Tool (APT)\footnote{http://www.stsci.edu/hst/proposing/apt}.
+There are several variations of readout patterns available to NIRCam with APT.
 For exoplanets time series observations, the readout patterns most commonly used will likely be ``RAPID'', meaning every sample is saved up the ramp individually and ``BRIGHT1'' where a single frame is dropped between reads.
@@
 The magnitudes are Vega $K_S$ magnitudes where 80\% of the well depth is filled in the standard CDS readout mode (described in Figure~\ref{fig:readout}) for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
-The blue points are known transiting systems from \texttt{exoplanets.org} and the green points are simulated TESS planets \citep{sullivan2015tess}.}\label{fig:saturationLim}
+The blue points are known transiting systems from and the green points are simulated TESS planets \citep{sullivan2015tess}.}\label{fig:saturationLim}
 \end{figure}
@@
 
-The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used with the long wavelength grisms (Case~\ref{it:DHSgr}) as compared to the long wavelength grisms alone (Case~\ref{it:grAlone}).
+The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the long wavelength grisms are used alone (Case~\ref{it:grAlone}) as compared to when the DHS is used simultaneously with the long wavelength grisms (Case~\ref{it:DHSgr}).
 These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.

### 2016-09-28 ms.tex
I explained more about the groups versus reads and how many integrations are in the example shown in the diagrams.

@@
 Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp.
-In all of our examples, there is one read per group.
 This is illustrated in Figure~\ref{fig:readout} for three example readout modes.
+In all of our examples, there is one read per group, meaning that no images are co-added.
 
-We consider a simplified example of a time series using a standard correlated double sampling (CDS) illustrated in Figure~\ref{fig:readout} and assume a round frame time of 10.0 seconds, close to the actual 10.74 seconds full frame read time.
+We consider a simplified example of a time series of 4 integrations using a standard correlated double sampling (CDS) illustrated in Figure~\ref{fig:readout} and assume a round frame time of 10.0 seconds, close to the actual 10.74 seconds full frame read time.
 CDS is equivalent to RAPID mode with 2 reads up the ramp.
@@
 The number of groups per integration is a variable set in the APT.
-When the number of groups is 1 (``1~Group Readout''), there is no ability to subtract out the bias frame so it relies on the bias level being constant through the whole time series.
-When the number of groups is 2, the slope can be calculated from the difference between the frames divided by the frame time.
+When the number of groups is 1 (``1~Group Readout''), there is no ability to subtract out the current bias frame so it relies on the bias level being constant through the whole time series.
+When the number of groups is 2, the slope can be calculated from the difference between the two reads divided by the frame time.
 It is the same as the CDS mode described above when using RAPID readout.

### 2016-09-28 ms.tex
I did some minor word changes and commented out the line on C/O ratios and metallicities since they aren't in the stairstep plots.

@@
 \caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission.
-The total throughput is the multiple of the filter curve, ``DHS'' grism and the pupil area fraction from Table~\ref{tab:pupfrac}..}\label{fig:DHSthrough}
+The total throughput is the product of the filter curve, ``DHS'' grism and the pupil area fraction from Table~\ref{tab:pupfrac}..}\label{fig:DHSthrough}
 \end{figure}
@@
 The pupil wheel is clocked to make the DHS spectra straight along rows.
-This moves the DHS elements off-center from JWST's pupil and thus decreases the throughput for elements 1 and 6, but the overall combined throughput for all 10 elements is only reduced from 32\% to 29\%.}\label{fig:DHSvsPupilOverlay}
+This moves the DHS elements off-center from JWST's pupil and thus decreases the throughput for elements 1 and 6 substantially, but the overall combined throughput for all 10 elements is only reduced from 32\% to 29\%.}\label{fig:DHSvsPupilOverlay}
 \end{figure}
@@
 These modes give high time resolution and allow one to detect and flag cosmic ray hits without having to discard large amounts of data.
-The number of groups per integration is a variable set in the APT.
+The number of groups per integration is a variable set in a proposal with APT.
 When the number of groups is 1 (``1~Group Readout''), there is no ability to subtract out the current bias frame so it relies on the bias level being constant through the whole time series.
@@
 The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}\label{tab:SatSNRsubA}
-\tablenotetext{0}{G2V-type star saturation K band limits are shown for suggested sub-array sizes.
-The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1-hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}
+\tablenotetext{0}{G2V-type star saturation K band limits are shown for the current available array sizes in APT, which determine the number of spectra from DHS elements that can be included.
+The noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1-hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}
 \end{table}
@@
 These are the subarrays that will be available to Cycle 1 science programs and likely stay this way for continuity through the mission in order to stick to detector ``sweet spots'' that are well characterized and calibrated.
-In principle, the short wavelength detectors can be read out with different sizes and read patterns from long wavelength array or even what is available in APT, but we realize there are operational costs to implementing and testing new modes in the OSS software and data handling.
+In principle, the short wavelength detectors can be read out with different sizes and read patterns from long wavelength array or even what is available in APT, but there are operational costs to implementing and testing new modes in the OSS software and data handling.
 
@@
 For the 2048~$\times$~64 and 2048~$\times$~128 subarrays, which can only encompass one spectrum with more than 10 pixels of background, they should be centered on the spectrum from element 7, since it has the maximum possible throughput listed in Table~\ref{tab:pupfrac}.
-For the 2048~$\times$~256 subarray, the location should be centered of the the middle of the spectra from elements 7 and 8 since they have the highest throughput of any adjacent pairs from Table~\ref{tab:pupfrac}.
+For the 2048~$\times$~256 subarray, the location should be centered between the spectra from elements 7 and 8 since they have the highest throughput of any adjacent pairs from Table~\ref{tab:pupfrac}.
 This is illustrated in Figure \ref{fig:DHSaps}.
@@
 The amount of data streaming from the detectors can overload the Solid State Recorder (SSR), which has a capacity of 540 Gbits \citep{johns2008L2comm}.
-We consider the use of 458 Gbits of space for science data as the maximum the SSR can handle at once.
+We consider the use of 458 Gbits of space for science data as the maximum the SSR can handle at once to allow for storage of telemetry.
 This overload can happen in as few as 10.3 hours if three NIRCam detectors are used simultaneously and all are read out with four amplifiers in CDS mode (meaning no samples are co-added or dropped) -- see Figure~\ref{fig:DataVolume}.
@@
 Finally, we run a Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
-We combine the individual gases' posterior distributions to derive the C/O ratio and metallicity (\citet{greene2016jwst_trans}) .
+%We combine the individual gases' posterior distributions to derive the C/O ratio and metallicity (\citet{greene2016jwst_trans}) .
 

### 2016-09-28 ms.tex
Some more minor wording changes but also corrected the order of the Case 1 and Case 2 which was still written incorrectly.

@@
 These are the subarrays that will be available to Cycle 1 science programs and likely stay this way for continuity through the mission in order to stick to detector ``sweet spots'' that are well characterized and calibrated.
-In principle, the short wavelength detectors can be read out with different sizes and read patterns from long wavelength array or even what is available in APT, but there are operational costs to implementing and testing new modes in the OSS software and data handling.
+In principle, the short wavelength detectors can be read out with different sizes and read patterns from long wavelength array or even what is available in APT, but the science benefits must be traded off with operational costs to implementing and testing new modes in the OSS software and data handling.
 
@@
 For simplicity, we assume isothermal atmospheres at the planetary equilibrium temperatures.
-Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea}) at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
+Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
 For HD 209458b (0.7 M$_{Jup}$), we prescribe solar metallicity since it is close to one Jupiter mass.
@@
 This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
-The readout mode in all cases simulated is RAPID readout (all reads saved without skips up the ramp discussed in Section \ref{sec:readout}) with 10 reads up the ramp for HD 209458 and 25 reads up the ramp for HAT-P-12b.
+The readout mode in all cases simulated is RAPID readout (all reads saved up the ramp without skips, discussed in Section \ref{sec:readout}) with 10 reads up the ramp for HD 209458 and 25 reads up the ramp for HAT-P-12b.
 
@@
 
-The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the long wavelength grisms are used alone (Case~\ref{it:grAlone}) as compared to when the DHS is used simultaneously with the long wavelength grisms (Case~\ref{it:DHSgr}).
+The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used simultaneously with the long wavelength grisms (Case~\ref{it:DHSgr}) as compared to when the long wavelength grisms are used alone (Case~\ref{it:grAlone}).
 These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.

### 2016-09-29 ms.tex
I replaced all instances of resolution (spectra) with resolving power because Tom points out that resolution is technically in wavelength units.

@@
 Even though NIRCam was designed primarily as an imager, it also includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments.
-NIRCam's long-wavelength channel includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with a resolution of $R = 1200 - 1550$ using two separate configurations.
+NIRCam's long-wavelength channel includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with a resolving power of $R = 1200 - 1550$ using two separate configurations.
 The long-wavelength grisms have already been approved for science operations, including wide field and single object (time series) slitless spectroscopy.
@@
 \includegraphics[width=1.0\columnwidth]{dhs_res.pdf}
-\caption{Resolution as a function of wavelength for the DHS.}\label{fig:DHSRes}
+\caption{Resolving power as a function of wavelength for the DHS.}\label{fig:DHSRes}
 \end{figure}
@@
 The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width as each other in the dispersion direction.
-Figure~\ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
+Figure~\ref{fig:DHSRes} shows the resolving power as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
 There is a spatial gap between short wavelength detectors which corresponds to about \DHSgap$\mu$m in wavelength.
@@
 \hline \hline		
-Resolution: &  \DHSres & 1200 - 1550 \\
+Resolving Power: &  \DHSres & 1200 - 1550 \\
 Dispersion: & 0.29 nm / px & 1.0 nm / px \\
@@
 \tablenotetext{0}{G2V-type star saturation K band limits are shown for the current available array sizes in APT, which determine the number of spectra from DHS elements that can be included.
-The noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1-hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}
+The noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1-hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolving power.}
 \end{table}
@@
 The balance between saturating the long-wavelength grism and getting enough SNR in the DHS is listed in Table~\ref{tab:SatSNRsubA}.
-The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the DHS noise at 1.1 to 1.9 $\mu$m for a G2V type star at this brightness observing a 1 hour long transit and 1 hour on a star out of transit, binned to the native resolution of R $\sim$ \DHSresApprox.
+The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the DHS noise at 1.1 to 1.9 $\mu$m for a G2V type star at this brightness observing a 1 hour long transit and 1 hour on a star out of transit, binned to the native resolving power of R $\sim$ \DHSresApprox.
 We use the standard correlated double sampling (CDS) readout mode shown in Figure~\ref{fig:readout} and we consider 80\% well depth in the second read as saturation.

### 2016-10-04 ms.tex
Thanks to Karl's suggestions, I adjusted the detector readout section to more clearly explain the general readout procedure before diving into specific readout modes like BRIGHT1 and RAPID.

@@
 We adopt the following naming convention for the readout: an observation may consist of one of more exposures which are combined into a single \texttt{FITS} file per exposure.
-Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp.
-This is illustrated in Figure~\ref{fig:readout} for three example readout modes.
-In all of our examples, there is one read per group, meaning that no images are co-added.
+Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp illustrated in Figure~\ref{fig:readout}.
+
+The NIRCam instrument supports 9 dedicated readout modes, each with a set number of reads up the ramp co-added on board (collectively called a group) and a set number of reads dropped between the groups to reduce data volume.
+As the exoplanet transit science case will be focused on bright targets, we consider only two of the allowed modes: RAPID (all reads up the ramp saved and downlinked) and BRIGHT1
+(alternating reads up the ramp dropped, i.e. read-drop-read-drop-...). 
+In these cases, the number of coadded frames is 1, so the number of groups is the same as the number of reads.
+A general discussion of HAWAII-2RG detector readouts can be found in  \citet{rauscher2007detectors} and
+a detailed description of the 9 readout patterns implemented for NIRCam can be found
+in  \citet{roberto2009optimalR1,roberto2010optimalR2}.
 
@@
 The raw data delivered to observers for use in a pipeline would consist of a single FITS file containing a data cube.
-If the data is in full frame mode, cube would have dimensions of 2048 $\times$ 2048 $\times$ 8, which can be thought of 8 image planes.
+If the data is in full frame mode, the cube would have dimensions of 2048 $\times$ 2048 $\times$ 8, which can be thought of 8 image planes.
 In this example there are 4 integrations consisting of a reset followed by two reads, which are saved as two image planes per integration.	
@@
 
-There are several variations of readout patterns available to NIRCam with APT.
-For exoplanets time series observations, the readout patterns most commonly used will likely be ``RAPID'', meaning every sample is saved up the ramp individually and ``BRIGHT1'' where a single frame is dropped between reads.
-These modes give high time resolution and allow one to detect and flag cosmic ray hits without having to discard large amounts of data.
+The BRIGHT1 and RAPID modes give high time resolution and allow one to detect and flag cosmic ray hits without having to discard large amounts of data.
 The number of groups per integration is a variable set in a proposal with APT.
@@
 In exoplanet time series, the high signal to noise ratios required generally mean that bright sources will be observed so these will generally not benefit from skipped frames or co-added frames of other JWST readout modes, which come at the expense of lower time resolution, reduced ability for cosmic ray rejection and fainter saturation limits.
-For more general discussion of HAWAII-2RG detector readout, we refer to \citet{rauscher2007detectors} and for specific readout patterns we refer to \citet{roberto2009optimalR1} and \citet{roberto2010optimalR2}.
 

### 2016-10-04 ms.tex
I corrected the second order overlap range to 2.0 to 2.02 as well as introduced the APT acroynm.

@@
 For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits:\ one with NIRISS SOSS (\SOSSrange), two with NIRCam's long-wavelength channel grisms (F322W2 and F444W + grisms; $2.44-4.98~\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H modes ($1.7-5.0~\mu$m.} and one with MIRI LRS ($5-12~\mu$m).
-Using the Astronomer's Proposal Tool software\footnote{http://www.stsci.edu/hst/proposing/apt}, each transit observation (pre-ingress, transit, and post-ingress) requires $\sim$9~hours and incurs overheads of $\sim$2~hours, resulting in a total of $\sim$11~hours per transit and hence $\sim$44~hours total to cover
+Using the Astronomer's Proposal Tool (APT) software\footnote{http://www.stsci.edu/hst/proposing/apt}, each transit observation (pre-ingress, transit, and post-ingress) requires $\sim$9~hours and incurs overheads of $\sim$2~hours, resulting in a total of $\sim$11~hours per transit and hence $\sim$44~hours total to cover
 the full wavelength range.
@@
 The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput.
-The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the second order of the spectrum begins to overlap at 2.0$\mu$m.\footnote{The prisms that spatially separate the 10 DHS spectra cross-disperse the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
+The range from 2.02$\mu$m to 2.35$\mu$m will probably be discarded because the second order of the spectrum begins to overlap at 2.0$\mu$m.\footnote{The prisms that spatially separate the 10 DHS spectra cross-disperse the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
 When using the DHS with the F150W2 filter and pairing it with the long wavelength grisms (F322W2 and F444W), the wavelength coverage will therefore be 1.0 to 5.0$\mu$m with a gap from 2.00$\mu$m to 2.44$\mu$m.

### 2016-10-04 ms.tex
Jarron made a set of changes to clarify the readout modes and terminology.

@@
 \subsection{Readout Considerations}\label{sec:readout}
-JWST's NIRCam instrument has many different possible readout patterns per pixel and array that all factor in to the SNRs and saturation limits for an observation.
-We adopt the following naming convention for the readout: an observation may consist of one of more exposures which are combined into a single \texttt{FITS} file per exposure.
-Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp illustrated in Figure~\ref{fig:readout}.
 
-The NIRCam instrument supports 9 dedicated readout modes, each with a set number of reads up the ramp co-added on board (collectively called a group) and a set number of reads dropped between the groups to reduce data volume.
-As the exoplanet transit science case will be focused on bright targets, we consider only two of the allowed modes: RAPID (all reads up the ramp saved and downlinked) and BRIGHT1
-(alternating reads up the ramp dropped, i.e. read-drop-read-drop-...). 
+NIRCam's detectors have numerous pixel readout schemes that factor into saturation limits and SNR calculations for a given observation.
+%JWST's NIRCam instrument has many different possible readout patterns per pixel and array that all factor in to the SNRs and saturation limits for an observation.
+We adopt the following nomenclature for the readout (Figure~\ref{fig:readout}):\ an \emph{integration} (also commonly refered to as a ``ramp'') consists of a pixel-reset frame followed by one or more groups of non-destructive reads to sample the pixels' charge accumulation.
+An \emph{exposure} is considered to be a collection of multiple integrations of the same type and length.
+Finally, an \emph{observation} consists of many exposures.
+
+%an \emph{observation} consists of one of more exposures which are combined into a single \texttt{FITS} file per exposure.
+%Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp illustrated in Figure~\ref{fig:readout}.
+
+The NIRCam instrument supports 9 dedicated readout modes, each with a set number of reads up the ramp co-added on board (collectively called a group) and a set number of reads dropped between the groups, both of which reduce data volume.
+As the exoplanet transit science case will be focused on bright targets, we consider only two of the allowed modes: RAPID (all read frames up the ramp are saved and downlinked) and BRIGHT1
+(alternating reads up the ramp dropped, i.e. reset-read-drop-read-drop-...). 
 In these cases, the number of coadded frames is 1, so the number of groups is the same as the number of reads.
@@
 
-We consider a simplified example of a time series of 4 integrations using a standard correlated double sampling (CDS) illustrated in Figure~\ref{fig:readout} and assume a round frame time of 10.0 seconds, close to the actual 10.74 seconds full frame read time.
+We consider a simplified example of a time series of 4 integrations using a standard correlated double sampling (CDS) illustrated in Figure~\ref{fig:readout} and assume an approximate frame time of 10.0 seconds, close to the actual 10.74 seconds full frame read time.
 CDS is equivalent to RAPID mode with 2 reads up the ramp.
@@
 If the data is in full frame mode, the cube would have dimensions of 2048 $\times$ 2048 $\times$ 8, which can be thought of 8 image planes.
-In this example there are 4 integrations consisting of a reset followed by two reads, which are saved as two image planes per integration.	
+In this example there are 4 integrations, each consisting of a reset followed by two read frames, which are saved as two image planes per integration.	
 For simplicity in this example, we ignore many of the corrections that are applied in a pipeline such as non-linearity correction, reference pixel correction, intrapixel capacitance, flat fielding etc.
@@
 This reduces the 8 image planes, to 4 flux planes, one per integration.
-Spectral extraction on the flux planes \citep[e.g.][]{horne1986optimalE} produces 1 flux per wavelength bin.
-The time series for a given wavelength would consist of the 4 fluxes with 4 time coordinates centered at 15 sec, 45 sec, 75 sec and 105 sec if we use the mid-points of the two reads.
+Spectral extraction on the flux planes \citep[e.g.][]{horne1986optimalE} then produces the flux per wavelength bin.
+A final reduced time series would consist of flux values at each given wavelength for each of the 4 time coordinates centered on 15 sec, 45 sec, 75 sec and 105 sec relative to the beginning of the observation sequence.%, taking the mid-points between read frames.
 
@@
 \caption{Schematic of example readout modes for an exposure that is 12 frame times in duration.
-A single FITS file is saved for the exposure, consisting of 1 or more groups per integration.
+A single exposure consists of 1 or more groups per integration.
 No reset frames or dropped frames are saved.``1~Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
@@
 This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).
-The current time series observing templates available in APT are limited to subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would cover 1, 1, 2 and 10 DHS spectra as shown in Figure~\ref{fig:DHSaps}.
+The current time series observing templates available in APT are limited to subarray sizes of 2048 $\times$ 64, 2048 $\times$ 128, 2048 $\times$ 256 and 2048 $\times$ 2048 (full frame), which would respectively cover 1, 1, 2 and 10 DHS spectra as shown in Figure~\ref{fig:DHSaps}.
 These are the subarrays that will be available to Cycle 1 science programs and likely stay this way for continuity through the mission in order to stick to detector ``sweet spots'' that are well characterized and calibrated.
@@
 
-We recommend that the sub-array locations to be adjusted so that the short wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long wavelength array can be centered on a single grism spectrum.
+We recommend that the sub-array locations be adjusted such that the short-wavelength sub-array can be centered on one DHS spectrum or a subset of the 10 and the long-wavelength array can be centered on a single grism spectrum.
 For the 2048~$\times$~64 and 2048~$\times$~128 subarrays, which can only encompass one spectrum with more than 10 pixels of background, they should be centered on the spectrum from element 7, since it has the maximum possible throughput listed in Table~\ref{tab:pupfrac}.
@@
 
-In normal operations, science and telemetry data from the James Webb Space Telescope are downlinked in a 4 hour contact time with an antenna in the Deep Space Network (SDN)  \citep{dashevsky2008groundflight}.
+In normal operations, science and telemetry data from the James Webb Space Telescope are downlinked in a 4 hour contact time with an antenna in the Deep Space Network \citep{dashevsky2008groundflight}.
 There will be two downlinks per day so on average the total data rate can be no more than $\sim$458 Gbits per 12 hours.

### 2016-10-04 ms.tex
I made a few small wording changes and also made the wavelength range of the F150W2 filter consistently 1.01 to 2.02 um.

--- 2016-10-04 ms.tex
@@
 The properties of the DHS as compared to the grisms are listed in Table~\ref{tab:DHSgprop}.
-If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure~\ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the DHS+F150W2 spectrum and Grism+F322W2 spectra, though the grism transmission is lower above 2.0$\mu$m, shown in Figure~\ref{fig:DHSthrough}.
+If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure~\ref{fig:HATp12spec}, the DHS can be used with the F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the DHS+F150W2 spectrum and the long wavelength channel (grism+F322W2 spectrum), though the DHS grism transmission is lower above 2.0$\mu$m, shown in Figure~\ref{fig:DHSthrough}.
 
@@
 Dispersion: & 0.29 nm / px & 1.0 nm / px \\
-Wavelengths: & 1.05 - 2.00$\mu$m (F150W2)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
+Wavelengths: & 1.05 - 2.02$\mu$m (F150W2)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
 			 & 1.75 - 2.23$\mu$m (F200W)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
@@
 \includegraphics[width=0.85\textwidth]{grism_pos_for_max_wcoverage.pdf}
-\caption{DHS wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength channel for the same input source.
+\caption{DHS wavelength coverage (when using the F150W2 filter) for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength channel for the same input source.
 The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes.
@@
 A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength channel and one spectrum on the long-wavelength channel -- see Figure~\ref{fig:DHSwaveWGrism}.
-The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
+The DHS spectra span two of NIRCam's short-wavelength detectors (covering 1.02$\mu$m to 2.02$\mu$m when using the F150W2 filter) with a \DHSgap$\mu$m gap due to the separation between detectors.
 The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
@@
 A fractional pupil of 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
-For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure~\ref{fig:DHSvsPupilOverlay}.
-Only the long-wavelength grisms of Module A are considered, because those in Module B lack an anti-reflective coating.
+For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS element should be used - number 7 in Figure~\ref{fig:DHSvsPupilOverlay}.
+Only the long-wavelength grisms of Module A are considered here, because those in Module B lack an anti-reflective coating.
 %We discuss only module A (of the two redundant modules A and B) because the long wavelength grisms are anti-reflective coated for module A.
@@
 \subsection{Readout Considerations}\label{sec:readout}
-JWST's NIRCam instrument has many different possible readout patterns per pixel and array that all factor in to the SNRs and saturation limits for an observation.
+JWST's NIRCam instrument has many different possible readout patterns per pixel and array that all factor into the SNRs and saturation limits for an observation.
 We adopt the following naming convention for the readout: an observation may consist of one of more exposures which are combined into a single \texttt{FITS} file per exposure.

### 2016-10-04 ms.tex

--- 2016-10-04 ms.tex
@@
 \subsection{Readout Considerations}\label{sec:readout}
-
 NIRCam's detectors have numerous pixel readout schemes that factor into saturation limits and SNR calculations for a given observation.
-%JWST's NIRCam instrument has many different possible readout patterns per pixel and array that all factor in to the SNRs and saturation limits for an observation.
 We adopt the following nomenclature for the readout (Figure~\ref{fig:readout}):\ an \emph{integration} (also commonly refered to as a ``ramp'') consists of a pixel-reset frame followed by one or more groups of non-destructive reads to sample the pixels' charge accumulation.
@@
 Finally, an \emph{observation} consists of many exposures.
-
-%an \emph{observation} consists of one of more exposures which are combined into a single \texttt{FITS} file per exposure.
-%Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp illustrated in Figure~\ref{fig:readout}.
 

### 2016-10-04 ms.tex
I decided to describe the readout modes as RAPID and BRIGHT1 and number of coadded or skipped frames and discuss CDS later.

@@
 The NIRCam instrument supports 9 dedicated readout modes, each with a set number of reads up the ramp co-added on board (collectively called a group) and a set number of reads dropped between the groups, both of which reduce data volume.
-As the exoplanet transit science case will be focused on bright targets, we consider only two of the allowed modes: RAPID (all read frames up the ramp are saved and downlinked) and BRIGHT1
+As the exoplanet transit science case will be focused on bright targets, we consider two of the allowed modes in this paper: RAPID (all read frames up the ramp are saved and downlinked) and BRIGHT1
 (alternating reads up the ramp dropped, i.e. reset-read-drop-read-drop-...). 
@@
 
-We consider a simplified example of a time series of 4 integrations using a standard correlated double sampling (CDS) illustrated in Figure~\ref{fig:readout} and assume an approximate frame time of 10.0 seconds, close to the actual 10.74 seconds full frame read time.
+We consider a simplified example of a time series of 4 integrations using 2 Groups in RAPID mode (a standard correlated double sampling, CDS pattern) illustrated in Figure~\ref{fig:readout} and assume an approximate frame time of 10.0 seconds, close to the actual 10.74 seconds full frame read time.
 CDS is equivalent to RAPID mode with 2 reads up the ramp.
-The raw data delivered to observers for use in a pipeline would consist of a single FITS file containing a data cube.
-If the data is in full frame mode, the cube would have dimensions of 2048 $\times$ 2048 $\times$ 8, which can be thought of 8 image planes.
+The raw data delivered to observers for use in a pipeline would contain a data cube.
+If the data is in full frame mode, the cube would have dimensions of 2048 $\times$ 2048 $\times$ 8, which can be thought of as 8 image planes.
 In this example there are 4 integrations, each consisting of a reset followed by two read frames, which are saved as two image planes per integration.	
@@
 Spectral extraction on the flux planes \citep[e.g.][]{horne1986optimalE} then produces the flux per wavelength bin.
-A final reduced time series would consist of flux values at each given wavelength for each of the 4 time coordinates centered on 15 sec, 45 sec, 75 sec and 105 sec relative to the beginning of the observation sequence.%, taking the mid-points between read frames.
+A final reduced time series would consist of flux values at each given wavelength bin for each of the 4 time coordinates centered on 15 sec, 45 sec, 75 sec and 105 sec relative to the beginning of the observation sequence.%, taking the mid-points between read frames.
 
@@
 A single exposure consists of 1 or more groups per integration.
-No reset frames or dropped frames are saved.``1~Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
+No reset frames or dropped frames are saved. 1~Group, RAPID readout can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
 The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but has a longer minimum integration time, resulting in fainter saturation limits.}\label{fig:readout}
@@
 When the number of groups is 1 (``1~Group Readout''), there is no ability to subtract out the current bias frame so it relies on the bias level being constant through the whole time series.
-When the number of groups is 2, the slope can be calculated from the difference between the two reads divided by the frame time.
+When the number of groups is 2, the slope can be calculated from the difference between the two reads divided by the group time.
 It is the same as the CDS mode described above when using RAPID readout.
@@
 For the 2048~$\times$~256 subarray, the location should be centered between the spectra from elements 7 and 8 since they have the highest throughput of any adjacent pairs from Table~\ref{tab:pupfrac}.
-This is illustrated in Figure \ref{fig:DHSaps}.
+These recommended subarray positions are illustrated in Figure \ref{fig:DHSaps}.
 
@@
 \subsubsection{Data Volume}
-For most transiting planet science, the targets are bright and so the pixels will continuously be read out quickly without any co-added reads.
+For most transiting planet science, the targets are bright so the pixels will be read out with very few or zero co-added and dropped frames.
 The amount of data streaming from the detectors can overload the Solid State Recorder (SSR), which has a capacity of 540 Gbits \citep{johns2008L2comm}.
@@
 A1, A3 and A5 in Figure~\ref{fig:DHSwaveWGrism}) before filling up JWST's Solid State Recorder (SSR).
-The readout modes shown are for Rapid readouts (no skipped frames as in CDS) and Bright1 for both 1 amplifier and 4 amplifiers.
+The readout modes shown are for RAPID readout and BRIGHT1 readout for both 1 amplifier and 4 amplifiers.
 The number of pixels read out affects the integration time and thus the data rate.
@@
 The lower frame rate, however, means that the detector saturates at 1/4 the flux as four amplifiers.
-Second, the detector can be read out in BRIGHT1 mode, seen in Figure~\ref{fig:readout}.
-This is where a frame is dropped between read 2 and read 1 to increase the integration time and efficiency while reducing data volume.
+Second, the detector reads can be skipped or co-added such as in BRIGHT1 mode, seen in Figure~\ref{fig:readout}.
+In BRIGHT1 mode, a frame is dropped between read 2 and read 1 to increase the integration time and efficiency while reducing data volume.
 This only works for sources faint enough that the long-wavelength grisms do not saturate.

### 2016-10-05 ms.tex
More tiny word changes like adding a space after a period and inserting a tilde between HD and 209458b.

@@
 Unfortunately, NIRSpec's low resolution prism mode is so sensitive that it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planetary systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
-For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits:\ one with NIRISS SOSS (\SOSSrange), two with NIRCam's long-wavelength channel grisms (F322W2 and F444W + grisms; $2.44-4.98~\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H modes ($1.7-5.0~\mu$m.} and one with MIRI LRS ($5-12~\mu$m).
+For example, to create a transmission spectrum for HD~209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits:\ one with NIRISS SOSS (\SOSSrange), two with NIRCam's long-wavelength channel grisms (F322W2 and F444W + grisms; $2.44-4.98~\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H modes ($1.7-5.0~\mu$m.} and one with MIRI LRS ($5-12~\mu$m).
 Using the Astronomer's Proposal Tool (APT) software\footnote{http://www.stsci.edu/hst/proposing/apt}, each transit observation (pre-ingress, transit, and post-ingress) requires $\sim$9~hours and incurs overheads of $\sim$2~hours, resulting in a total of $\sim$11~hours per transit and hence $\sim$44~hours total to cover
@@
 Thus, the DHS data come ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
-For the example above of HD 209458b, simultaneous DHS data would reduce the required transits from four to three, saving about 11 JWST hours 
+For the example above of HD~209458b, simultaneous DHS data would reduce the required transits from four to three, saving about 11 JWST hours 
 if the wavelengths from 2.0$\mu$m to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
@@
 
-The DHS has the brightest saturation limits of any spectroscopic mode on JWST because each of the 10 DHS elements samples only 1 to 4\% of the pupil and the light is dispersed over over two short wavelength detectors.
+The DHS has the brightest saturation limits of any spectroscopic mode on JWST because each of the 10 DHS elements samples only 1\% to 4\% of the pupil and the light is dispersed over two short wavelength detectors.
 Figure~\ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms and the known transiting systems from \texttt{exoplanets.org} \citep{han2014exopDorg}, plus \citet{motalebi2015hd219134b}.
@@
 \includegraphics[width=1.0\columnwidth]{brightness_scape.pdf}
-\caption{Saturation limits of the DHS mode (blue line), and long-wavelength grism's F322W2 filter (green line) and F444W filter (dark red line) as a function of stellar effective temperature.
+\caption{Saturation limits of the DHS mode (blue line), the long-wavelength grism + F322W2 filter combination (green line) and the long-wavelength grism + F444W filter (dark red line) as a function of stellar effective temperature.
 The magnitudes are Vega $K_S$ magnitudes where 80\% of the well depth is filled in the standard CDS readout mode (described in Figure~\ref{fig:readout}) for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
-The blue points are known transiting systems from and the green points are simulated TESS planets \citep{sullivan2015tess}.}\label{fig:saturationLim}
+The blue points are known transiting systems and the green points are simulated TESS planets \citep{sullivan2015tess}.}\label{fig:saturationLim}
 \end{figure}
@@
 	}
-	\caption{Model spectra separated by molecule for HD~209458b and the inflated warm Saturn HAT-P-12b.The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel.
+	\caption{Model spectra separated by molecule for HD~209458b and the inflated warm Saturn HAT-P-12b.
+The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel.
 a) The simulated data for HD~209458b consist of one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
@@
 We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to illustrate the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms.
-We first simulate a forward model of a transmission spectrum for two planets, HD 209458b \citep{henry00,charbonneau00} and HAT-P-12b \citep{hartman2009hatp12}.
+We first simulate a forward model of a transmission spectrum for two planets, HD~209458b \citep{henry00,charbonneau00} and HAT-P-12b \citep{hartman2009hatp12}.
 We then add Gaussian noise using the SNR estimated on the target to create a simulated spectrum.
-Finally, we run a Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
+Finally, we run a Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for the simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}.
 %We combine the individual gases' posterior distributions to derive the C/O ratio and metallicity (\citet{greene2016jwst_trans}) .
@@
 Molecular volume mixing ratios are assumed to be in thermochemical equilibrium at a represenatitive pressure (0.01 bars) and temperature using the NASA CEA code\footnote{http://www.grc.nasa.gov/WWW/CEAWeb/ceaHome.htm}\citep{gordon1996cea} at the prescribed planetary metallicity, derived by rescaling the solar elemental abundances \citep{asplund}.
-For HD 209458b (0.7 M$_{Jup}$), we prescribe solar metallicity since it is close to one Jupiter mass.
+For HD~209458b (0.7 M$_{Jup}$), we prescribe solar metallicity since it is close to one Jupiter mass.
 For HAT-P-12b (0.2 M$_{Jup}$), we prescribe a planet metallicity of 22 $\times$ solar using the relation from \citet{kreidberg2014wasp43}.
@@
 	}
-	\caption{Posterior distributions for MCMC runs of HD209458b and HAT-P-12b with the DHS (blue) and without the DHS (green).
+	\caption{Posterior distributions for MCMC runs of HD~209458b and HAT-P-12b with the DHS (blue) and without the DHS (green).
 The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.
@@
 \centering
-\includegraphics[width=1.0\columnwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
-\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
+\includegraphics[width=0.5 \textwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
+\caption{Calculated SNR for one transit of the hot Jupiter HD~209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
 Similar wavelength coverage can be achieved in just 3 different transits or $\sim$33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
@@
 
-We assume isothermal temperature's of 1440K and 960 K for for HD209458b and HAT-P-12b respectively.
+We assume isothermal temperatures of 1440K and 960 K for HD~209458b and HAT-P-12b respectively.
 Molecular abundances are assumed constant with altitude at the 0.01 bar thermochemical values.
@@
 For the HAT-P-12b model, we include an opaque gray cloud deck at 1 mbar to simulate the effect of clouds on reducing spectral features in a planet spectrum.
-For HD 209458b, this cloud deck is placed at a pressure level of 1 bar which is too deep to affect the spectrum, as shown in Figure~\ref{fig:209spec}.
+For HD~209458b, this cloud deck is placed at a pressure level of 1 bar which is too deep to affect the spectrum, as shown in Figure~\ref{fig:209spec}.
 % if we run the simulations later, also mention emission spectra
@@
 
-For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m.
+For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.98$\mu$m.
 We assume that each of these was accompanied by a DHS observation for the 1.0$\mu$m to 2.0$\mu$m wavelength range, which benefits in SNR by $\sqrt{2}$ for the two separate observations.
@@
 This observing scenario is compared to a scenario that does not include the DHS to show the added scientific value of using the DHS spectra.
-The readout mode in all cases simulated is RAPID readout (all reads saved up the ramp without skips, discussed in Section \ref{sec:readout}) with 10 reads up the ramp for HD 209458 and 25 reads up the ramp for HAT-P-12b.
+The readout mode in all cases simulated is RAPID readout (all reads saved up the ramp without skips, discussed in Section \ref{sec:readout}) with 10 reads up the ramp for HD~209458 and 25 reads up the ramp for HAT-P-12b.
 
-The noise models for the hot Jupiter HD 209458b are shown in Figure~\ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
+The noise models for the hot Jupiter HD~209458b are shown in Figure~\ref{fig:DHSvsNIRISS209}, which is dominated by the residual systematic noise floor (set to 30 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations.
 The DHS has lower total throughput ($\sim$8\% including pupil coverage factor) and a smaller wavelength coverage than the NIRISS instrument in SOSS mode ($\sim$30\% throughput\footnote{\texttt{http://maestria.astro.umontreal.ca/niriss/simu1D/simu1D.php}}), so observations which require higher SNR and full wavelength coverage from \SOSSrangeto\ can take advantage of NIRISS (also shown in Figure~\ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.
@@
 
-The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used simultaneously with the long wavelength grisms (Case~\ref{it:DHSgr}) as compared to when the long wavelength grisms are used alone (Case~\ref{it:grAlone}).
+The posterior distributions for HD~209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used simultaneously with the long wavelength grisms (Case~\ref{it:DHSgr}) as compared to when the long wavelength grisms are used alone (Case~\ref{it:grAlone}).
 These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.
@@
 This is because the 1mbar cloud layer begins to affect the opacity near 4.0$\mu$m, which is measured by the long wavelength grisms.
-As with HD 209458b, the DHS improves constraints on the H$_2$O and CO$_2$ abundances, but since the planet is at a cooler temperatures, chemical equilibrium favors CH$_4$ over CO, so the constraints are much better on CH$_4$.
+As with HD~209458b, the DHS improves constraints on the H$_2$O and CO$_2$ abundances, but since the planet is at a cooler temperatures, chemical equilibrium favors CH$_4$ over CO, so the constraints are much better on CH$_4$.
 

### 2016-10-05 ms.tex
This is the version I will submit after the first referee report. I got rid of the bibliographystyle astroads that I originally had in there since it doesn't seem to be used nor is recognized by PASP's system.
I renamed the NIRCam+OTE file name because the PASP submission system doesn't like the plus sign in the file name.
Got rid of all of Mike's bazillion affiliations since he's now at ASU.

@@
 \usepackage{natbib}
-\bibliographystyle{astroads}
 
@@
 
-\author{M. Line\altaffilmark{1,2,3,4}}
-\affil{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 95064}
+\author{M. Line}
+\affil{School of Earth and Space Exploration, Arizona State University, Tempe, AZ 85281}
 
@@
 %% affiliation.
-
-\altaffiltext{1}{Hubble Postdoctoral Fellow}
-\altaffiltext{2}{NASA Ames Research Center, Moffett Field, CA 94035}
-\altaffiltext{3}{Bay Area Environmental Research Institute, Petaluma, CA}
-\altaffiltext{4}{School of Earth and Space Exploration, Arizona State University, Tempe, AZ}
 
@@
 \centering
-\includegraphics[width=1.0\columnwidth]{NIRCam+OTE_SWA_DHS_and_F150W2_efficiency.pdf}
+\includegraphics[width=1.0\columnwidth]{NIRCam_OTE_SWA_DHS_and_F150W2_efficiency.pdf}
 \caption{Throughput as a function of wavelength for the DHS grism, F150W2 filter and F200W filter that includes the telescope and instrument transmission.
